### 2018-05-23 Paper/first_diff_method.tex
Added first difference method document

%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is a template file for the LaTeX package SVJour2 for the
% Springer journal
%  The 20th European Conference on Few-Body Problems in Physics,
%  9-13 September 2013, Cracow, Poland
%
% Copy it to a new file with a new name and use it as the basis
% for your article. Delete % as needed.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% First comes an example EPS file -- just ignore it and
% proceed on the \documentclass line
% your LaTeX will extract the file if required
\begin{filecontents*}{example.eps}
%!PS-Adobe-3.0 EPSF-3.0
%%BoundingBox: 19 19 221 221
%%CreationDate: Mon Sep 29 1997
%%Creator: programmed by hand (JK)
%%EndComments
gsave
newpath
  20 20 moveto
  20 220 lineto
  220 220 lineto
  220 20 lineto
closepath
2 setlinewidth
gsave
  .4 setgray fill
grestore
stroke
grestore
\end{filecontents*}
%
\documentclass[onecolumn, 12pt, draft]{revtex4-1}
\bibpunct{[}{]}{;}{n}{}{,} % to get "[numbered]" references from natbib
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
\usepackage{amsmath, amssymb}
\usepackage{color}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
\journalname{Few-Body Systems}
%

\begin{document}

\title{Impenetrability in Floquet scattering in one dimension}
\author{A.~G.~Volosniev \and D.~H.~Smith}

%\authorrunning{Short form of author list} % if too long for running head

\institute{A.~G.~Volosniev  \at
              Institut f{\"u}r Kernphysik, Technische Universit{\"a}t Darmstadt, 64289 Darmstadt, Germany   
  \newline
 \email{volosniev@theorie.ikp.physik.tu-darmstadt.de}    %  \\
%             \emph{Present address:} of F. Author  %  if needed
           \and
           D.~H.~Smith \at Department of Physics, The Ohio State University, Columbus, OH 43210, USA  
}

%\institute{ Department of Physics and Astronomy, Aarhus University, DK-8000 Aarhus C, Denmark \\
 %             \email{artem@phys.au.dk}           %  \\    
%}

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
\keywords{one spatial dimension}
\end{abstract}

\section{Introduction}

\section{Scattering off a time-periodic zero-range potential in one dimension}
\label{sec:zero}
\begin{figure}
\centering
\includegraphics[scale=0.7]{fig1new.eps}
\caption{Panel {\textbf a)}: The reflection probability $|B_0|^2$ as a function of $p/\sqrt{\omega}$ for $g_1/\sqrt{\omega}=0.2$ -- black solid curve, $g_1/\sqrt{\omega}=0.4$ -- red dashed curve,  $g_1/\sqrt{\omega}=0.8$ -- green dot-dashed curve, and $g_1/\sqrt{\omega}=1.0$ -- blue dotted curve. For all curves $g_0/\sqrt{\omega}=-1$. Panel {\textbf b)}: $|B_0|^2$ for $g_1/\sqrt{\omega}=1.5$ -- black solid curve, $g_1/\sqrt{\omega}=2.5$ -- red dashed curve, $g_1/\sqrt{\omega}=3.5$ -- green dot-dashed curve, and $g_1/\sqrt{\omega}=4.5$ -- blue dotted curve. For all curves $g_0=0$. Panel {\textbf c)}: $|B_0|^2$ for $g_0/\sqrt{\omega}=0.1$ -- black solid curve, $g_0/\sqrt{\omega}=0.5$ -- red dashed curve,  $g_0/\sqrt{\omega}=1$ -- green dot-dashed curve, and $g_0/\sqrt{\omega}=1.5$ -- blue dotted curve. For all curves $g_1/\sqrt{\omega}=1.5$. Panel {\textbf d)}:  $|B_0|^2$ for $g_0/\sqrt{\omega}=-0.1$ -- black solid curve, $g_0/\sqrt{\omega}=-0.8$ -- red dashed curve,  $g_0/\sqrt{\omega}=-1.4$ -- green dot-dashed curve, and $g_0/\sqrt{\omega}=-2$ -- blue dotted curve. For all curves $g_1/\sqrt{\omega}=1.5$.}
\label{fig:fig1new}
\end{figure}

\section{Conclusions}
\label{sec:concl}

{\small {\bf Acknowledgments} A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation.}

\appendix

\section{Appendix}
\label{sec:formalism}

\subsection{Floquet Formalism}

{\bf Scattering in time-dependent picture}. Here, for convenience of the reader, we discuss the time-dependent Schr{\"o}dinger equation with a general short-range time-periodic potential
\begin{equation}
i\frac{\partial}{\partial t}\Psi(x,t)=H(t)\Psi(x,t),\qquad H(t)=H_0+W(x,t),
\label{eq:schr}
\end{equation}
where the operators in the coordinate representation are $H_0=-\frac{\partial^2}{\partial x^2}$, and $W(x,t)=\sum_n  e^{-\frac{2 i \pi n t}{T}} W_n(x)$. We assume that the incoming square-integrable wave packet is $\Psi_0(x,t)$, i.e., $\Psi(x,t\to-\infty)=\Psi_0(x,t)$. Obviously, if $g_n=0, \forall n$ then the time propagation is $\Psi_0(x,t)=e^{-i H_0 t}\Psi_0$, where $\Psi_0\equiv\Psi_0(x,0)$. Therefore, the effect of scattering is deduced by comparing $\Psi(x,t)$ with $\Psi_0(x,t)$.

To proceed we note that there is a unitary operator $U(t,s)$ that determines the time evolution
\begin{equation}
\Psi(t)=U(t,s)\Psi(s).
\end{equation}
The formal properties of $U(t,s)$ are discussed in Ref. \cite{yajima1977}.
From now on we reserve the letters $t$ and $s$ for time, also when it does not cause confusion we omit the coordinate variables. For convenience, we set $t=0$ to be a reference time and introduce $\Psi\equiv\Psi(x,0)$ such that $\Psi(t)=U(t)\Psi$, where $U(t)\equiv U(t,0)$. To compare $\Psi(t)$ and $\Psi_0(t)$ one can introduce the wave operator $\Omega(s)$, such that $\Psi=\Omega \Psi_0$, $\Omega=\Omega(0)$. This operator is defined as the limit
\begin{equation}
\Omega(s) \equiv \lim_{t\to-\infty}U^{-1}(t,s)e^{-i(t-s) H_0}.
\end{equation}
In scattering theory for time-independent potentials $\Omega$ is often called the M{\o}ller operator \cite{taylorbook}. This operator exists also for time-periodic short-range potentials as discussed in Refs.~\cite{yajima1977, howland1979}. One important property of $\Omega$ is called the intertwining relation:
\begin{equation}
U(t)\Omega=\Omega(t)e^{-i H_0 t}.
\end{equation}
We use this relation upon decomposing $\Psi_0$ in the eigenbasis of $H_0$. For convenience we refrain from using coordinate representation and use Dirac's notation for vectors instead: $|\Psi_0\rangle=\int_{-\infty}^{\infty} \mathrm{d}p \phi(p) |p\rangle$. Now if we apply the intertwining relation to this decomposition we obtain
\begin{equation}
\int \mathrm{d}p \phi(p)\left(U(t)\Omega |p\rangle -e^{-i p^2 t}\Omega(t)|p\rangle \right)=0.
\end{equation}
Since it should be valid for all possible initial wave packets described by $\phi(p)$ we  conclude that the integrand should be zero. By differentiating both sides with respect to time, we see that the only way to satisfy this condition is to assume that $|f_p\rangle(t)\equiv \Omega(t)|p\rangle$ obeys
\begin{equation}
\left(H(t)-i\frac{\partial}{\partial t}\right) |f_p\rangle(t) =p^2 |f_p\rangle(t).
\label{eq:floquet}
\end{equation}
%To find $\Omega(t)|p\rangle$ initial conditions are needed.

Let us take a closer look at Eq. (\ref{eq:floquet}). According to the Floquet theorem $U(t+T,s+T)=U(t,s)$; see also Ref. \cite{yajima1977}. Therefore, $\Omega(T)=\Omega$, hence $|f_p\rangle(t+T)=|f_p\rangle(t)$ and $|f_p\rangle(t)=\sum_n e^{-\frac{2 i \pi n  t}{T}} |\tilde f_{pn}\rangle$. By inserting this ansatz function into Eq. (\ref{eq:floquet}) and projecting onto a particular mode we obtain 
\begin{equation}
(p^2+n \omega -H_0)| \tilde  f_{pn}\rangle= \sum_m W_{n-m}|\tilde f_{pm}\rangle,
\label{eq:set}
\end{equation}
where $\omega=2\pi/T$. This is a (infinite-dimensional) matrix equation, and therefore, for each $p^2$ there is an infinite number of solutions, which can be formally written as 
\begin{equation}
|\tilde f_{pn}\rangle = |p_n\rangle \alpha_n + \frac{1}{p^2+n\omega-H_0+ i\epsilon}\sum_{m}W_{n-m}|\tilde f_{pm}\rangle,
\label{eq:tildefpn}
\end{equation}
where $\alpha_n$ and $\epsilon\in\mathbb{R}$ are coefficients, and $p_n^2=p^2+n\omega$. We show below that the solution that satisfies the initial condition $\Psi(x,t\to-\infty)\to \Psi_0(x,t)$ has $\alpha_n=\delta_{n,0}$ and $\epsilon>0$. To this end
we write the formal solution to Eq.~(\ref{eq:schr}) 
%we first note that
%\begin{equation}
%|\Psi\rangle\equiv \Omega|\Psi_0\rangle=\int \mathrm{d}p \phi(p) |f_p\rangle,
%\label{eq:psifromf}
%\end{equation}
%where $|f_p\rangle \equiv |f_p\rangle(0)=\sum_n  |\tilde f_{pn}\rangle$. Then 
\begin{equation}
|\Psi\rangle(t)=e^{-i H_0 t}\int_{-\infty}^{\infty}\mathrm{d}p\phi(p)\left(1-i \int_{-\infty}^t \mathrm{d}t' e^{i H_0 t'}W(t')\Omega(t')e^{-i H_0 t'}\right)|p\rangle.
%\; \to \; |\Psi\rangle=\int \mathrm{d}p\phi(p)(|p\rangle + A|p\rangle),
\label{eq:psi_t}
\end{equation}
%where $A=T\mathrm{exp}\left[-i\int_{-\infty}^0\mathrm{d}t e^{i H_0 t} W(t) e^{-i H_0 t}\right]-1$, with $T$ we denote the usual time-ordering operation.
%Another way to write the operator $A$ is 
%\begin{equation}
%A=-i\int_{-\infty}^0 \mathrm{d}t e^{iH_0 t} W(t) \Omega(t) e^{-iH_0 t}.
%\end{equation}
%By acting with $A$ on $|p\rangle$ we deduce the form of $A|p\rangle=|f_p\rangle-|p\rangle$:
%\begin{equation}
%|f_p\rangle -|p\rangle =  - \sum_{m,n}\frac{1}{H_0-p^2+\omega(m+n)-i\epsilon}W_m|%\tilde f_{pn}\rangle,
%\label{eq:form_f}
%\end{equation}
This equation yields $|\Psi\rangle$
\begin{equation}
|\Psi\rangle=\int_{-\infty}^{\infty}\mathrm{d}p \phi(p)\left(|p\rangle+\sum_{m,n}\frac{1}{p^2+(n+m)\omega-H_0+i\delta}W_{n}|\tilde f_{pm}\rangle\right).
\label{eq:psi_help1}
\end{equation} 
where $\delta$ is a small positive quantity. 	
To obtain $|\Psi\rangle$ we used the prescription $W(t)\to e^{\delta t}W(t)$, which is justified by noticing that for $t\to-\infty$ the square-integrable wave packet cannot be affected by the finite-range potential. Now if we look at Eqs.~(\ref{eq:tildefpn}) and~(\ref{eq:psi_help1}) and notice that
$|\Psi\rangle=\Omega |\Psi_0\rangle=\int \mathrm{d}p \phi(p)\sum_n |\tilde f_{pn}\rangle$ we deduce that $\alpha_n=\delta_{n,0}$ and $\epsilon>0$. At $t$ we have $|\Psi\rangle(t)=\int\mathrm{d}p \phi(p)e^{-ip^2t} \sum_{n}e^{-i\omega n t}|\tilde f_{pn}\rangle$. This provides us with the wave function $\Psi(x,t)$ for $x\to\infty$, which determines characteristics of transmission 
\begin{equation}
\Psi(x,t)=\Psi_0(x,t) -\frac{i}{2}\sum_{m,n}\int\mathrm{d}p\phi(p) \frac{e^{ip_nx - i p_n^2 t }}{p_n} \int\mathrm{d}x' e^{-ip_nx'} W_{n-m}(x')\langle x'|\tilde f_{pm}\rangle,
\label{eq:asymptotics}
\end{equation}
a similar expression can be derived for $x\to-\infty$.
Here we use the coordinate representation of the Green's function
\begin{align}
G(x,x';k^2)\equiv\langle x| \frac{1}{H_0-k^2-i\epsilon}|x'\rangle  = \frac{i}{2k}e^{ik|x-x'|}.
\end{align}

{\bf Scattering in time-independent picture}. In this subsection we consider Eq.~(\ref{eq:tildefpn}) that determines the properties of the scattering in time-independent picture in more detail. In the coordinate representation it reads
\begin{align}
\tilde f_{pn}(x)=\delta_{n,0}e^{i p_n x}- \sum_{m=-\infty}^{\infty} \int\mathrm{d}x' 
 G(x,x';p_n^2)W_{n-m}(x')\tilde f_{pm}(x'),
\label{eq:fpn}
\end{align} 
where $\delta_{m,n}$ is Kronecker's delta. This function at $x\to\infty$ has the form $\delta_{n,0}e^{ip_nx}+B_ne^{ip_nx}$ where 
\begin{align}
B_n=-\frac{i}{2 p_n}\sum_{m=-\infty}^\infty \int\mathrm{d}x' e^{-i p_n x'}W_{n-m}(x')\tilde f_{pm}(x')
\label{eq:an}
\end{align}
whereas at $x\to-\infty$ it has the form $\delta_{n,0}e^{ip_nx}+\tilde B_n e^{-i p_n x}$ with
\begin{align}
\tilde B_n=-\frac{i}{2p_n}\sum_{m=-\infty}^\infty \int\mathrm{d}x' e^{i p_n x'}W_{n-m}(x')\tilde f_{pm}(x'), 
\label{eq:bn}
\end{align}
Apparently, Eqs. (\ref{eq:fpn}), (\ref{eq:an}) and (\ref{eq:bn}) contain all information about the scattering process and can be used to derive Eq.~(\ref{eq:set_zero}) of the main text. It is worthwhile to notice that for a plane wave with a given $p^2$ the total probability to find a particle with the energies $p^2_n, n=0,\pm1,...$ is conserved in the scattering process (see the next subsection). This can be seen as the conservation of the quasi-energy. At the same time the total energy is not conserved and can become larger or smaller, depending on the problem.

\subsection{Conservation of Flux.}
\label{sec:appA}

The Floquet modes, $f_p$, fully describe the scattering process. Since they always contain scattering states, there should be no probability to find a particle close to the potential at $t\to\infty$ (assuming a square-integrable wave function at $t\to-\infty$): the total outgoing flux should be equal to the total incoming flux. Note that since the states with $p^2-\omega(m+n)<0$ do not give any contribution to the fluxes, the particle will leave these modes after some time. Physically it is easily understood, since a particle in these modes can undergo a transition to a scattering state and leave the range of the potential. This appendix 
shows the conservation of flux explicitly in a time-independent picture. Let us start with the scattering off zero-range potential described by Eq.~(\ref{eq:set_zero}), for which the flux is 
\begin{equation}
\vec j = i (\psi \vec \nabla \psi^*-\psi^* \vec \nabla \psi).
\end{equation}
The incoming flux is along the $x$ axis and amounts to $2p$.
The outgoing flux consists of the two parts: the first is along the $x$ direction and equals to $\sum_{p_n\geq0} 2p_n|C_n|^2$. The second piece is along the $(-x)$
 direction and amounts to $\sum_{p_n\geq0} 2 p_n |C_n-\delta_{n,0}|^2$. Let us show that from Eq.~(\ref{eq:set_zero}) it follows that 
\begin{equation}
\sum_{p_n\geq 0}p_n|C_n|^2=p \mathrm{Re} C_0,
\label{eq:fluxzerorange}
\end{equation}
which means that the total flux is conserved. To this end, we multiply
Eq.~(\ref{eq:set_zero}) with~$C_n^{*}$,
\begin{equation}
2 p_n |C_n|^2=2p\delta_{n,0} C_n^*-ig_0 |C_n|^2 - \frac{i g_1}{2}(C_{n+1}+C_{n-1})C_n^*.
\end{equation}
Next we conjugate Eq.~(\ref{eq:set_zero}) and then multiply
with~$C_n$,
\begin{equation}
2 p_n^* |C_n|^2=2p\delta_{n,0} C_n+ig_0 |C_n|^2 + \frac{i g_1}{2}(C^*_{n+1}+C^*_{n-1})C_n.
\end{equation}
Now we add these two equations and sum over all states
\begin{equation}
\sum (p_n+p_n^*)|C_n|^2=2p \mathrm{Re} C_0.
\end{equation}
Since $p_n+p_n^*$ is non-zero only for the scattering states we obtain Eq. (\ref{eq:fluxzerorange}). 
%Note, that if we instead sum up over the scattering states we obtain 
%\begin{equation}
%\sum_{p_n\geq 0} p_n|C_n|^2=2 p \mathrm{Re} C_0 +\frac{i g_1}{4}(C_l C_{l-1}^*-C_l^* C_{l-1}),
%\end{equation}
%where $l$ corresponds to the lowest in energy scattering wave, e.g., if $p^2<\omega$ then $l=0$. This establishes the following identity $\mathrm{Im} (C_{l}^*C_{l-1})=0$. From this identity one can easily derive that $\mathrm{Im} (C_{l-k}^*C_{l-n-1})=0$ for any $n,k\geq 0$. 
Similar steps can be taken to show that the total flux is conserved for any short-range potential. 
%For this we need to show that 
%\begin{equation}
%\sum_{p_n\geq0}p_n(|A_n|^2+|B_n^2|)=-2p\mathrm{Re}A_0,
%\label{eq:appa_cond}
%\end{equation}
%where $A_n$ and $B_n$ are taken from Eqs. (\ref{eq:an}) and (\ref{eq:bn}) respectively.
%Using the definitions of $A_n$ and $B_n$ this expression can be written as
%\begin{align}
%\mathrm{lhs}=-i\sum_{p_n\geq 0,m',m''} \int \mathrm{d}x'\mathrm{d}x'' W_{n-m'}(x')W_{n-m''}(x'') \left[ G(x'',x';p_n^2)-G^*(x'',x';p_n^2)\right]f_{pm'}(x')f^*_{pm''}(x'').
%\end{align}
%To derive Eq. (\ref{eq:appa_cond}) one should use Eq.~(\ref{eq:fpn}) having in mind that for every $n$, such that $p_n^2<0$, the following holds 
%\begin{equation}
%\sum_m \int \mathrm{d}x W_{n-m}(x)\left[f_{pm}^*(x)f_{pn}(x)-f_{pm}(x)f_{pn}^*(x)\right]=0.
%\end{equation}
%which generalizes the previously derived relation $\mathrm{Im}(C_l^*C_{l-1})=0$. 
%This equation can be obtained directly from Eq. (\ref{eq:set}).

\bibliographystyle{unsrt}
\bibliography{bib}

\end{document}
{\bf Appendix -- Limiting cases}

\section{Energy transfer}
\label{sec:transfer}

### 2018-08-01 Paper/skeleton.tex
Added paper to git versioning and modified gitignore for latex files

\documentclass[onecolumn,amsmath,amssymb,nofootinbib,prl]{revtex4-1}

\usepackage{comment}
\usepackage{graphicx} 
\usepackage{xcolor}

\usepackage[%frenchlinks=true,
colorlinks=true,
    linkcolor={red!50!black},
    citecolor={blue!50!black},
    urlcolor={blue!80!black}]{hyperref}

\begin{document}

\title{Engineering momentum profiles of cold-atom beams}

\author{D~Hudson \surname{Smith}}
\affiliation{Clemson University, Clemson, South Carolina 29634, USA}

\author{Artem~G \surname{Volosniev}}
\affiliation{Institut f{\"u}r Kernphysik, Technische Universit{\"a}t Darmstadt, 64289 Darmstadt, Germany}

\begin{abstract}
We ...
\end{abstract}

\maketitle

\section{Introduction}

Scattering is one of the most important observational tools in science. In physics, it is used in almost all subfields to understand internal structure of particles, materials, structures (cite).

In systems of cold atoms scattering might seem obsolete because the energies are so low that usually only a few parameters determine physics, i.e., the system is in a universal regime. However, even at these low temperatures observables can strongly depend on the incoming momentum (see Figure 1a). For example, ...

{\it Figure 1a: examples where observables depend strongly on the incoming momentum: time-dependent one- and two-body scattering, three-body recombination,  polaron. 
Figure 1b: a sketch of the set-up for engineering beams with desirable momentum profiles: two reservoirs and a link between them.}

Here we study how to create fluxes with cold atoms, which can be used to study systems of cold atoms in scattering experiments. We illustrate using the one-dimensional Bose polaron problem.

\section{Design}

Describe the system. The system has three parts: Two reservoirs and a link between them; see Figure 1a. One reservoir is made of a non-interacting (for simplicity) gas of particles at temperature $T$. We call these particles probes or $A$. The reservoir is connected to the link. The link is a potential that acts only on particles $A$ (for simplicity). The second reservoir is made of interacting particles $B$. These particles make a system of interest, which we would like to analyze.

 It is clear that by changing the potential in the link we can change the flux. Let us describe how we compute potentials to create desirable fluxes. In this section we discuss this.  Describe the procedure here: We set the desirable momentum profile, guess a potential, calculate the corresponding transmission coefficient, minimize the parameters.

{\it Figure 2: Examples of a few profiles that can be created: comb, evaporative, anti-evaporative etc. In the insets are the corresponding potentials.}

\section{Illustration}

The Bose polaron problem is very interesting, and many groups are studying it now. It is an open question how to measure the effective mass of the impurity in one-dimensional set-ups. There was one experiment, however the results are unclear. Also it is interesting to understand when the model breaks, i.e., at which momenta. We propose the following experiment: One reservoir -- probes, the link is from Fig. 2 (comb), the second reservoir is an interacting homogeneous Bose gas (for simplicity). Provide some realistic numbers. Probably some simple calculations (in the suppl. material).

{\it Figure 3: Bose polaron set-up. Measurement of the effective mass -- the change of the energy upon interaction change.}

\section{Summary}

We have shown how to create beams of particles to probe systems of cold atoms. We have illustrated the idea using the Bose polaron problem. Other interesting examples include ...

\bibliographystyle{apsrev4-1}
\bibliography{bib}

 \end{document}

### 2018-08-01 Paper/paper.tex
Started writing methods section

--- 2018-08-01 Paper/skeleton.tex
@@
 \usepackage{xcolor}
+\usepackage{bm}
 
@@
 
+\subsection{Physical System}
 Describe the system.
@@
 These particles make a system of interest, which we would like to analyze.
+
+\subsection{Determining the Link Potential}
+We now present a procedure for determining a link potential that produces a generic desirable flux properties.
+This simple procedure performs a global search over a family of possible link potentials in order to minimize the difference between the desired flux properties and the actual flux properties.
+Due to the non-convex nature of this optimization problem, we perform this search using the well-known global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
+Despite its astounding simplicity, this algorithm does an excellent job of balancing the need to search the entire space against the need to learn from subsequent trials in the optimization process in order to speed up convergence.
+
+To start, we must specify the ideal desired flux profile $T(k)$ where $k$ is the incident momentum.
+This could be, for instance, a ``comb'' profile that only allows particle flux near a specified momentum, but our prescription applies to a broad class of flux profiles.
+
+We also must specify the form of the link potential, $V(x, \bm{\theta})$, with unknown parameters $\bm{\theta}$.
+The functional form of the link potential should be chosen to represent the class of physically realizable potentials within the experimental context.
+In our case, we assume a sum of Gaussian potentials:
+\begin{equation}
+V(x,\{\bm{A},\bm{\mu},\bm{\sigma} \}) = \sum_{i=1}^{N}\frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
+\end{equation}
+where $N$ is the number of Gaussian potentials (and the length of the parameter vectors $\bm{A}$, $\bm{\mu}$, and $\bm{\sigma}$).
+
+In addition to specifying the form of the link potential, we may also need to specify a set of constraints on the parameters themselves in order to reflect the limitations in creating the physical potentials.
+In our case, we will enforce the following constraints
+\begin{align}
+  \sum_{i=1}^{N}\mu_i &= 0 & \\
+  \sigma_i &> 0 &\forall i \in\{1,2,\ldots,N\}\\
+  0 &\leq A_i < A^\mathrm{max} &\forall i \in\{1,2,\ldots,N\}             
+\end{align}
+
+In addition there may be generic constraints on the potential itself
 

### 2018-08-30 Paper/version1/paper.tex
Added Version 2

--- 2018-08-01 Paper/paper.tex
@@
 
-\subsection{Determining the Link Potential}
-We now present a procedure for determining a link potential that produces a generic desirable flux properties.
-This simple procedure performs a global search over a family of possible link potentials in order to minimize the difference between the desired flux properties and the actual flux properties.
-Due to the non-convex nature of this optimization problem, we perform this search using the well-known global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
-Despite its astounding simplicity, this algorithm does an excellent job of balancing the need to search the entire space against the need to learn from subsequent trials in the optimization process in order to speed up convergence.
+\subsection{Finding a Link Potential}
+Our simple process for finding an appropriate link potential consists of a global search over a family of possible link potentials in order to minimize the difference (more precisly the ``cost'', defined in Eq.~\eqref{eq:cost} below) between the desired and the actual flux properties.
+We perform this search using the well-known global optimization routine called Differential Evolution (DE) \cite{original DE paper}.This evolutionary-based search is suitable given the non-convex nature of the optimization problem.
+Despite its simplicity, DE does a good job of balancing the need to search the entire space against the need to learn from subsequent trials in the optimization process in order to speed up convergence with minimal complication in terms of choosing the right model settings.
+Emperically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
+
+Before detailing our procedure, we emphasize that our goal is not to the find the ``best'' link potential in terms of a theoretical cost function; one that is ``good enough'' in terms of experimental requirements will do.
+This relaxed goal removes many complications.
+For instance, as long as a discovered potential is {\it good enough} we do not even need to worry about whether or not the DE routine has converged.
+Similarly, if we run the routine twice and arrive at two very different but similarly {\it good enough} solutions, we do not have to worry about which solution is ``right''.
+We can just pick our favorite and proceed.
 

### 2018-08-30 Paper/version2/paper.tex
Added Version 2

--- 2018-08-30 Paper/version1/paper.tex
@@
-\documentclass[onecolumn,amsmath,amssymb,nofootinbib,prl]{revtex4-1}
+\documentclass[twocolumn,amsmath,amssymb,showpacs,prl,superscriptaddress,aps]{revtex4-1}
 
-\usepackage{comment}
+\usepackage{epsfig}
+\usepackage{color}
 \usepackage{graphicx}
-\usepackage{xcolor}
 \usepackage{bm}
-
-\usepackage[%frenchlinks=true,
-colorlinks=true,
-    linkcolor={red!50!black},
-    citecolor={blue!50!black},
-    urlcolor={blue!80!black}]{hyperref}
+\usepackage{epstopdf}
 
@@
 \affiliation{Institut f{\"u}r Kernphysik, Technische Universit{\"a}t Darmstadt, 64289 Darmstadt, Germany}
+
+\date{\today}
 
@@
 
+\begin{acknowledgments}
+We thank Michael Fleischhauer for referring to~\cite{paper}.
+A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation.
+\end{acknowledgments}
+
+\widetext
+
+\section{Supplementary Material}
+
+\section{Polaron}
+
+To model one impurity atom that moves through the one-dimensional environment made of $N$ cold bosonic atoms, we employ the following Hamiltonian
+\begin{equation}
+H=-\frac{\hbar^2}{2m}\sum_{i=1}^N\frac{\partial^2}{\partial x_i^2}-\frac{\hbar^2}{2M}\frac{\partial^2}{\partial y^2}+g\sum_{i>j=1}^N\delta(x_i-x_j)+c\sum_{i=1}^N \delta(x_i-y),
+\end{equation}
+where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are described by the set of coordinates $\{x_i\}$. 
+We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $g$ and $c$ respectively. 
+The reservoir by assumption is large, such that the dynamics can be described by the thermodynamic limit $N\to \infty$ assuming a certain value of the density $\rho$.
+To take the thermodynamic limit we set the periodic boundary conditions: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
+This assumption is not essential for our problem, because we are interested in the limit $N(L)\to \infty$ with $\rho=\frac{N}{L}$.
+
+Every eigenfunction of the Hamiltonian can be written as $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. Because all interactions are pairwise, 
+the total (angular) momentum of the system must be conserved, and we write it as $P=\frac{2\pi\hbar}{L}\left(\sum_{j} n_j+m\right)$.
+Since we have a conserved quantity ($P$), we may exclude the coordinate of the impurity from the consideration. To this end, 
+we write the function $\Psi$ as $\Psi=e^{i \frac{P y}{\hbar}}\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jz_j}{L}}\equiv e^{i \frac{P y}{\hbar}} \psi(z_1,...,z_N)$ 
+with $z_i=L\theta(x_i-y)+x_i-y$, where $\theta(x)$ is the Heavyside step function, i.e., 
+$\theta(x>1) = 1$ and zero otherwise. The variables $z_i$ are defined such that $0\leq z_i \leq L$ and the impurity is placed at $z=0$ and $z=L$. Now if we insert this 
+function into the Schr{\"o}dinger equation, $H\Psi={\cal E}\Psi$, we obtain the following equation for $\psi(0<z_i<L)$
+\begin{equation}
+-\frac{\hbar^2}{2m}\sum_i\frac{\partial^2 \psi}{\partial z_i^2}-\frac{\hbar^2}{2M}\left(\sum_{i}\frac{\partial \psi}{\partial z_i}\right)^2
++ i \frac{\hbar P}{M}\sum_{i}\frac{\partial \psi}{\partial z_i}+g\sum_{i>j}\delta(z_i-z_j)\psi=\left({\cal E}-\frac{P^2}{2M}\right)\psi,
+\end{equation}
+which must be supplemented with the boundary conditions:
+\begin{equation}
+\psi(z_i=0)=\psi(z_i=L); \qquad \frac{\partial \psi}{\partial z_i}\bigg|^{z_i=0^+}_{z_i=L^-}= \frac{2 c \kappa}{\hbar^2} \psi(z_i=0),
+\end{equation}
+where $\kappa=mM/(m+M)$ is the reduced mass.
+
+By assumption the bosons are weakly-interacting, therefore we use the ansatz $\psi=\prod_i \Phi(z_i)$ to approximate the function. 
+To minimize the expectation value of the Hamiltonian the function $\Phi(z)$ must satisfy the following Gross-Pitaevski-type equation
+\begin{equation}
+-\frac{\hbar^2}{2\kappa}\frac{\partial^2\Phi}{\partial z^2}+i\frac{\hbar P}{M}\frac{\partial \Phi}{\partial z}
+-i \frac{\hbar^2 (N-1) A}{M} \frac{\partial\Phi}{\partial z} + g(N-1)|\Phi|^2\Phi=\mu \Phi,
+\end{equation}
+where $A=-i\int \Phi(x)^*\frac{\partial}{\partial x}\Phi(x)\mathrm{d}x$ defines the momentum of a boson, and $\mu$ is the chemical potential (it appears as the Lagrange multiplier). 
+We rewrite this equation as
+\begin{equation}
+-\frac{\partial^2\Phi}{\partial z^2}+i v \frac{\partial \Phi}{\partial z} + \tilde g(N-1)|\Phi|^2\Phi+\tilde c\delta(z)\Phi=\tilde\mu\Phi,
+\label{eq:GPE_resc}
+\end{equation}
+where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde g=\frac{2 \kappa g}{\hbar^2}$, $\tilde c=\frac{2 \kappa c}{\hbar^2}$ and 
+$v\equiv \frac{2 \kappa P_I}{M \hbar}$, where $P_I=P-\hbar A(N-1)$ defines the momentum of the impurity in the thermodynamic limit.
+Note the corresponding boundary conditions 
+\begin{equation}
+\Phi(z=0)=\Phi(z=L); \qquad \frac{\partial \Phi}{\partial z}\bigg|^{z=0^+}_{z=L^-}= \tilde c \Phi(0),
+\end{equation}
+
+This non-linear equation~(\ref{eq:GPE_resc}) has an analytic solution for the soliton-like behavior~\cite{ishikawa1980,hakim1997}, which determines the properties 
+of the polaron in our problem. Let us first consider the case with $c=0$. In this case the solution for $v>0$ is
+\begin{equation}
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde g(N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z+z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\end{equation}
+\begin{equation}
+\phi(z)=-\pi\theta(z+z_0)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
+\end{equation}
+where  $\beta=1- v^2/(2\tilde \mu)$, and $z_0$ is some parameter that should be determined from the boundary conditions.
+It is worthwhile noting that the solution for $v<0$ is $\Phi^*$.
+We plot this solution in Figs.~\ref{fig:Fig1} and~\ref{fig:Fig2}; for simplicity we consider the region $-L/2<z<L/2$, the region $0<z<L$ easily follows.
+Note that the solution is not periodic (see $\phi$), however by combining two solution with $\pm z_0$
+we can construct a periodic solution with a singularity at $z=0$. Therefore, the polaron in this picture is a combination of two moving solitons: The impurity creates a topological defect, which 
+leads to a quasiparticle picture.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centerline{\includegraphics[scale=0.5]{density.pdf}}
+\caption{The density, $|\Phi|^2$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left curve), $z_0=-0.2$, assuming that $\tilde \mu=1.6, v=0.3$ (everything in arbitrary units). 
+Note that the minimum of the density is at $-z_0$.}
+\label{fig:Fig1}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centerline{\includegraphics[scale=0.5]{phase.pdf}}
+\caption{The phase, $\phi$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left curve), $z_0=-0.2$, assuming that $\tilde \mu=1.6, v=0.3$ (everything in arbitrary units).}
+\label{fig:Fig2}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+We write the wave function for the polaron as
+\begin{equation}
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde g(N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z\pm z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\end{equation}
+with 
+\begin{equation}
+\phi(z)=\delta \phi \theta(-z)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z\pm z_0)\right]-2\beta+1}\right),
+\end{equation}
+where the parameter $\delta \phi$ is not important for the further derivations, it reassures that the function is periodic  
+(in the thermodynamic limit it is written as $2\pi - \mathrm{arctan}\left[\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{1-2\beta}\right]$);
+the plus sign in $\pm$ corresponds to $z>0$ and the minus sign to $z<0$. The wave function can be easily visualised from Figs.~\ref{fig:Fig1} and~\ref{fig:Fig2}. 
+The density has a non-analytic derivative at $z=0$. The phase is discontinuous function at $z=0$ (the derivative is continuous).
+
+The corresponding chemical potential is found from the normalization condition $\int \Phi^2=1$, for large values of $N$ and $L$ it reads
+\begin{equation}
+\tilde \mu=\gamma \rho^2 \frac{N-1}{N}\left(1-2\sqrt{2\beta} \frac{ (\mathrm{tanh}(d)-1)}{\sqrt{\gamma}N}\right),
+\end{equation}
+where $\rho=N/L$, $\gamma=\tilde g/\rho$, and $d=\sqrt{\frac{\gamma \beta}{2}}\rho z_0$.
+The condition on $z_0$ is found by using the boundary conditions at $z=\{0,L\}$
+\begin{equation}
+\frac{\tilde c}{\rho \sqrt{2\gamma}}=\frac{\beta^{\frac{3}{2}}\tanh(d)}{-\beta+\cosh^2(d)}.
+\end{equation}
+This equation is cubic (in $\tanh(d)$), hence, the solutions can be found in a closed form.
+Now we can calculate the energy of the polaron in the thermodynamic limit
+\begin{equation}
+E\equiv \lim_{N\to\infty, \frac{N}{L}\to \rho}\left[{\cal E}(c,P)-{\cal E}(c=0,P=0)\right],
+\end{equation}
+where
+\begin{equation}
+{\cal E}(c,P) = \frac{P^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-gN(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
+\end{equation}
+Using these expressions we derive 
+\begin{equation}
+E=\frac{P_I^2}{2M}+\frac{\hbar^2\rho}{2\kappa}\frac{\sqrt{2 \tilde g \rho \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P_I}{M}\lim_{N\to\infty} A N,
+\end{equation}
+where $b=1+\frac{v^2}{4\tilde g\rho}=1+\frac{\kappa P_I^2}{2M^2 g\rho}$. This energy for $v\to 0$ can be written as 
+\begin{equation}
+E\simeq \epsilon+ \frac{P_I^2}{2m_{\mathrm{\mathrm{eff}}}},
+\end{equation}
+where $\epsilon$ is the effective energy of the polaron, and $m_{\mathrm{eff}}$ is the effective mass.
+
+Further Discussions in the supplementary material and in the paper:
+
+Discuss the effective mass.
+
+Discuss the two different solutions.
+
+Discuss the critical momentum.
+
+Discuss the quench dynamics to the polaron.
+
+Discuss the literature.
+
 \bibliographystyle{apsrev4-1}

### 2018-10-17 Paper/version2/paper.tex
Minor progress on methods section.

@@
 \usepackage{color}
+\usepackage{array}
 \usepackage{graphicx}
@@
 \usepackage{epstopdf}
+
+\DeclareMathOperator*{\argmin}{argmin}
 
@@
 
-\subsection{Finding a Link Potential}
-Our simple process for finding an appropriate link potential consists of a global search over a family of possible link potentials in order to minimize the difference (more precisly the ``cost'', defined in Eq.~\eqref{eq:cost} below) between the desired and the actual flux properties.
-We perform this search using the well-known global optimization routine called Differential Evolution (DE) \cite{original DE paper}.This evolutionary-based search is suitable given the non-convex nature of the optimization problem.
-Despite its simplicity, DE does a good job of balancing the need to search the entire space against the need to learn from subsequent trials in the optimization process in order to speed up convergence with minimal complication in terms of choosing the right model settings.
+\subsection{Procedure for Finding a Link Potential}\label{sec:procedure_link}
+We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the difference between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
+Concretely, we minimize the cost $J_{\bm{\theta}}$ which is a function of $T_0(k) - T_{\bm{\theta}}(k)$ but may also explicitly depend upon $V(x,\bm{\theta})$ and $\bm{\theta}$ in order to encode practical, experimental constraints on the solutions for the link potential.
+Given the cost function, the {\it optimal} parameters are $\bm{\theta}^* = \argmin_{\bm{\theta}}J_{\bm\theta}$.
+However, we do not need to find the {\it optimal} link potential; one that is {\it good enough} in terms of experimental requirements will do.
+This relaxed goal alleviates concerns about convergence to the global optimum.
+
+We perform the minimization outlined above using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
+This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
+Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
 Emperically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
 
-Before detailing our procedure, we emphasize that our goal is not to the find the ``best'' link potential in terms of a theoretical cost function; one that is ``good enough'' in terms of experimental requirements will do.
-This relaxed goal removes many complications.
-For instance, as long as a discovered potential is {\it good enough} we do not even need to worry about whether or not the DE routine has converged.
-Similarly, if we run the routine twice and arrive at two very different but similarly {\it good enough} solutions, we do not have to worry about which solution is ``right''.
-We can just pick our favorite and proceed.
+We parametrize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussian potentials:
+\begin{equation}\label{eq:V-param}
+V_N(x,\{\bm{A},\bm{\mu},\bm{\sigma} \}) = \sum_{i=1}^{N}\frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
+\end{equation}
+where $A_j\equiv(\bm{A})_j$, $\mu_j\equiv(\bm{\mu})_j$, and $\sigma_j\equiv(\bm{\sigma})_j$ are the amplitude, mean, and standard deviation for the $j^{\mathrm{th}}$ Gaussian.
+It is necessary to enforce constraints on these parameters to both improve convergence and to ensure that solutions satisfy the experimental requirements.
+Table~\ref{tab:constraints} shows the explicit parameter constraints that we enforce  during minimization.
 
-To start, we must specify the ideal desired flux profile $T(k)$ where $k$ is the incident momentum.
-This could be, for instance, a ``comb'' profile that only allows particle flux near a specified momentum, but our prescription applies to a broad class of flux profiles.
+\begin{table}[t]
+  \renewcommand*{\arraystretch}{1.4}
+  \begin{tabular}{m{3cm}|m{5.5cm}}
+    Constraints & Experimental Rationale \\
+    \hline\hline
+    $\sum_{i=1}^{N}\mu_i = 0$ & The cost function has a continuous degeneracy associated with overall translations of the link potential. \\
+    \hline
+    $\sigma_{\mathrm{min}} \leq \sigma_j \leq \sigma_{\mathrm{max}} $ & Laser beam widths fall between a minimum and maximum value.\\
+    \hline
+    $A_{\mathrm{min}} \leq |A_j| \leq A_{\mathrm{max}}$ & Laser amplitudes fall between a minimum and maximum value.
+  \end{tabular}
+  \caption{The explicit constraints on the potential parameters and the rationale for each constraint.
+The values of $\sigma_{\mathrm{min}}$, $\sigma_{\mathrm{max}}$, $A_{\mathrm{min}}$, and $A_{\mathrm{max}}$ must be determined from the experimental context.}
+  \label{tab:constraints}
+\end{table}
 
-We also must specify the form of the link potential, $V(x, \bm{\theta})$, with unknown parameters $\bm{\theta}$.
-The functional form of the link potential should be chosen to represent the class of physically realizable potentials within the experimental context.
-In our case, we assume a sum of Gaussian potentials:
-\begin{equation}
-V(x,\{\bm{A},\bm{\mu},\bm{\sigma} \}) = \sum_{i=1}^{N}\frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
-\end{equation}
-where $N$ is the number of Gaussian potentials (and the length of the parameter vectors $\bm{A}$, $\bm{\mu}$, and $\bm{\sigma}$).
-
-In addition to specifying the form of the link potential, we may also need to specify a set of constraints on the parameters themselves in order to reflect the limitations in creating the physical potentials.
-In our case, we will enforce the following constraints
-\begin{align}
-  \sum_{i=1}^{N}\mu_i &= 0 & \\
-  \sigma_i &> 0 &\forall i \in\{1,2,\ldots,N\}\\
-  0 &\leq A_i < A^\mathrm{max} &\forall i \in\{1,2,\ldots,N\}             
-\end{align}
-
-In addition there may be generic constraints on the potential itself
+In addition to explicit constraints on the parameters, we inforce an implicit constraint by requireing that the link potential should not extend beyond the region  of potential support $x\in[-x_0,x_0]$.
+This we do by adding to the cost function a term $J_{\mathrm{boundary}}$ that grows with the area of the potential outside the support region.
+The complete definition of the cost function is given in suppl.~material.
 
@@
 
+\subsection{Cost Function}\label{sec:cost_function}
+
+\begin{equation}
+  J'_{\mathbf{\theta}} = J_{\mathbf{\theta}} + \alpha J_{\mathrm{boundary}},
+\end{equation}
+where $\alpha>0$ is the weight given to cost incurred for having the potential extend outside the support region of the potential.
+
 \bibliographystyle{apsrev4-1}

### 2018-10-18 Paper/version2/paper.tex
Update to paper

@@
 \subsection{Procedure for Finding a Link Potential}\label{sec:procedure_link}
-We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the difference between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
-Concretely, we minimize the cost $J_{\bm{\theta}}$ which is a function of $T_0(k) - T_{\bm{\theta}}(k)$ but may also explicitly depend upon $V(x,\bm{\theta})$ and $\bm{\theta}$ in order to encode practical, experimental constraints on the solutions for the link potential.
-Given the cost function, the {\it optimal} parameters are $\bm{\theta}^* = \argmin_{\bm{\theta}}J_{\bm\theta}$.
-However, we do not need to find the {\it optimal} link potential; one that is {\it good enough} in terms of experimental requirements will do.
-This relaxed goal alleviates concerns about convergence to the global optimum.
+We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the $k$-integrated squared error between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
+Concretely, we minimize the cost
+\begin{equation}\label{eq:cost1}
+  J_{\bm{\theta}} = \sum_kw_k\left|T_0(k) - T_{\mathbf{\theta}}(k)\right|^2,
+\end{equation}
+where the $k$-integral has been approximated (up to a constant factor) by a sum over a discrete set of momentum values, and $w_k$ is the weight given to momentum $k$.
+The weights are chosen to emphasize regions of $k$ during the minimization.
+For instance, when trying to create a ``comb'' potential that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$, then it would be appropriate to increase the weights in the region of $k_0$.
+We find that results are sensitive to the choice of $w_k$, and some trial and error was required to get acceptable potentials.
 
-We perform the minimization outlined above using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
+With the goal of discovering experimentally viable solutions, we parameterize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussian potentials each of the form
+\begin{equation}\label{eq:V-param}
+V_i(x; A_i, \mu_i, \sigma_i) = \frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
+\end{equation}
+While minimizing Eq.~\eqref{eq:cost1}, we enforce the parameter constraints listed in Table \ref{tab:constraints}.
+In addition to these explicit constraints on the parameters, we enforce an implicit constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
+To accomplish this, we minimize the augmented cost
+\begin{equation}\label{eq:cost2}
+  J_{\bm{\theta}}^{\mathrm{aug}} = J_{\bm{\theta}} + \alpha \sum_i^N\int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2,
+\end{equation}
+where $\alpha$ is a tuning parameter chosen to make the added term of a similar order to $J_{\mathbf{\theta}}$ in the scenario that the potential extends outside the support region.
+Beyond this, we find that results are not very sensitive to the choice of $\alpha$ probably due to the very short tails of the Gaussian potentials.
+The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
+The full form is given in the suppl.~material.
+
+For a choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating Schr{\"o}dinger's equation across the region of the potential and calculating the ratio of the transmitted to the incident flux.
+In order to do this efficiently, we approximate the integral as a banded linear system of equations solvable in $O(M)$ time where $M$ is the number of $x$-steps.
+Using these techniques we are able to evaluate the transmission coefficient x thousand times per second on a 7th generation Intel Core i7 processor under the conditions used in our tests.
+
+ We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
 This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
@@
 Emperically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
-
-We parametrize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussian potentials:
-\begin{equation}\label{eq:V-param}
-V_N(x,\{\bm{A},\bm{\mu},\bm{\sigma} \}) = \sum_{i=1}^{N}\frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
-\end{equation}
-where $A_j\equiv(\bm{A})_j$, $\mu_j\equiv(\bm{\mu})_j$, and $\sigma_j\equiv(\bm{\sigma})_j$ are the amplitude, mean, and standard deviation for the $j^{\mathrm{th}}$ Gaussian.
-It is necessary to enforce constraints on these parameters to both improve convergence and to ensure that solutions satisfy the experimental requirements.
-Table~\ref{tab:constraints} shows the explicit parameter constraints that we enforce  during minimization.
 
@@
 
-In addition to explicit constraints on the parameters, we inforce an implicit constraint by requireing that the link potential should not extend beyond the region  of potential support $x\in[-x_0,x_0]$.
-This we do by adding to the cost function a term $J_{\mathrm{boundary}}$ that grows with the area of the potential outside the support region.
-The complete definition of the cost function is given in suppl.~material.
-
- It is clear that by changing the potential in the link we can change the flux.
-Let us describe how we compute potentials to create desirable fluxes.
-In this section we discuss this.
-Describe the procedure here: We set the desirable momentum profile, guess a potential, calculate the corresponding transmission coefficient, minimize the parameters.
+Figure \ref{fig:method_examples} demonstrates the application of the procedure described above to three scenarios: the comb potential, evaporative cooling, and anti-evaporative cooling.
+Each figure shows the resulting link potential $V_0(x)$ along with the target and actual momentum-transmission profiles.
 

### 2018-11-06 Paper/version2/paper.tex
First draft of the introduction, summary and application sections

@@
 \begin{abstract}
-We ...
+We propose a scheme for engineering fluxes of cold atoms with given momentum profiles. 
+In our proposal, the flux is created using a link potential that selects desired momenta 
+from the bath. We discuss how to determine the link potential given the required profile 
+of a beam, and present a topical application, in which the beam is used 
+to study Bose polarons. 
 \end{abstract}
@@
 
-\section{Introduction}
+{\it Introduction. --} In systems of cold atoms the typical energies are so 
+low that usually only a few quantities (e.g., the scattering length and the three-body parameter) 
+determine physics~\cite{braaten2006, bloch2008}. 
+When these parameters are known the outcomes of measurements can be predicted. 
+Ultracold beams with a given momentum might be very useful for determining these parameters. 
+For example, the effective mass of a Fermi or Bose `polaron'~\cite{zwierlein2009,hu2016,arlt2016}
+can be obtained by studying a beam of particles with a given momentum inside a degenerate gas.
+Furthermore, ultracold beams can give new 
+insight into the systems where non-universal energy-dependent phenomena have been observed. For instance, it can help 
+to understand the temperature (energy) dependence of the three-body parameter~\cite{naidon2011, huang2015, wacker2018}.
 
-Scattering is one of the most important observational tools in science. In physics, it is used in almost all subfields to understand internal structure of particles, materials, structures (cite).
+In this Letter, we propose an approach for engineering beams of cold atoms. 
+Our proposal is illustrated in Fig.~\ref{fig:Figure1}: The particles in a reservoir scatter off the link potential with 
+some desired transmission coefficient, $T_0(k)$. The function $T_0(k)$ allows only particles with a given momentum to 
+tunnel through the barrier into the `flux region'. In spirit, our scheme is similar to a quantum switch device 
+(`transistor')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' is affected by changing the properties of the `gate'.
+However, the present proposal in addition to completely switching off the flux, allows one to engineer the momentum profile of the flux.
 
-In systems of cold atoms scattering might seem obsolete because the energies are so low that usually only a few parameters determine physics, i.e., the system is in a universal regime.
-However, even at these low temperatures observables can strongly depend on the incoming momentum (see Figure 1a).
-For example, ...
+To confirm that the flux has been created one can use a single-atom momentum resolution to check the momentum profile of the flux~\cite{jochim2018}.
 
-{\it Figure 1a: examples where observables depend strongly on the incoming momentum: time-dependent one- and two-body scattering, three-body recombination,  polaron. 
-Figure 1b: a sketch of the set-up for engineering beams with desirable momentum profiles: two reservoirs and a link between them.}
-
-Here we study how to create fluxes with cold atoms, which can be used to study systems of cold atoms in scattering experiments. We illustrate using the one-dimensional Bose polaron problem.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centerline{\includegraphics[scale=0.3]{figure1new.pdf}}
+\caption{An illustration of the proposal: The reservoir that contains particles of various momenta is connected to the external potential. The design of this potential
+allows only particles with desired momenta to tunnel into the flux region.
+  }
+\label{fig:Figure1}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 
-\section{Illustration}
+{\it Application. --} Consider a flux through a degenerate 
+one-dimensional Bose gas. If the current is low then the system 
+can be described using the concept of the polaron -- an impurity dressed by low-energy excitations 
+of the environment~\cite{landau1948}. Let us briefly describe the properties of this quasiparticle
+within an extension to the mean-field theory developed in Ref.~\cite{volosniev2017}
+for a zero momentum of the impurity~\footnote{See the Supplementary Material}; see also~\cite{kain2016, parisi2017,grusdt2017, pastukhov2017}. 
+According to this theory the lowest energy state of a system with a fixed value of momentum, $P$, 
+is a combination of two solitons which makes a dissipationless defect in the Bose gas, which we call the polaron. The corresponding energy 
+is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, 
+$\epsilon$ is the self-energy of the polaron, and $m_{\mathrm{eff}}$ is its effective mass. The polaron solution is steady only 
+for $P<P_c$, where $P_c$ defines the momentum above which the propagation flux produces grey solitons. 
+Note that quantum fluctuations will lead to some finite dissipation~\cite{astrakharchik2004,sykes2009} even for $P<P_c$, however
+we do no consider this effect in the present study.
 
-The Bose polaron problem is very interesting, and many groups are studying it now.
-It is an open question how to measure the effective mass of the impurity in one-dimensional set-ups.
-There was one experiment, however the results are unclear.
-Also it is interesting to understand when the model breaks, i.e., at which momenta.
-We propose the following experiment: One reservoir -- probes, the link is from Fig.
-2 (comb), the second reservoir is an interacting homogeneous Bose gas (for simplicity).
-Provide some realistic numbers.
-Probably some simple calculations (in the suppl.
-material).
+Ultracold beams can be used to study the properties of Bose polarons. For example, to measure the effective 
+mass one can prepare the flux of particles $B$ in the hyperfine state that does not 
+interact with the Bose gas. Then the particles $B$ can be transferred into a hyperfine state that strongly interacts with the gas.
+This transfer is possible only if one deposits the energy that compensates for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
+There is a non-zero overlap between a free particle and the polaron state; see~\cite{volosniev2017} for $P=0$.
+Therefore, by looking at the radio-frequency responce (e.g., the transferred fraction) at different momenta, the effective mass of the polaron can be extracted. 
+This idea is similar to a recent experiment in a three-dimensional Fermi polaron~\cite{zaccanti2017}. However,
+in our case the initial momentum is known, and therefore not only the effective mass but also the limits of applicability 
+of the polaron model can be determined, in particular, the critical momentum above which there are no steady solutions.
+In Fig.~\ref{fig:Figure3}{\bf b)} we present this momentum for heavy impurities (for which our theory works best), relevant 
+for mixtures of cold atoms with large mass imbalance, e.g., Li-Yb~\cite{takahashi2018}.
+For weak interactions ($g\to 0$) the critical momentum is determined by the speed of sound, $c$, in accordance with the Landau criterion.
+For strong interactions ($g\to \infty$) the critical momentum goes to zero as $1/g$.  
+In this limit the critical momentum is determined by the time needed to exchange two strongly interacting particles.
 
-{\it Figure 3: Bose polaron set-up. Measurement of the effective mass -- the change of the energy upon interaction change.}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centerline{\includegraphics[scale=0.3]{figure3.pdf}}
+\caption{Panel {\bf a)} shows schematically the energies of a free particle and a Bose polaron --
+a particle in a degenerate Bose gas. The possibility to create particles of a given momenta 
+will allow one to establish the effective mass of the polaron
+and the limits of applicability of the polaron model by measuring the energy difference, $\Delta(p)$, using the radio-frequency spectroscopy.
+Note that quasiparticle properties should be absent for high momenta. For one spatial dimension, a typical momentum scale can be estimated  by considering the existence of steady solutions 
+of a suitable non-linear Schr{\"o}dinger equation; see the text for details. Panel {\bf b)} 
+shows the results for a heavy impurity of mass $M$; $c$ is the speed of sound
+and $g$ is the boson-impurity interaction strength.
+  }
+\label{fig:Figure3}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-\section{Summary}
-
-We have shown how to create beams of particles to probe systems of cold atoms. We have illustrated the idea using the Bose polaron problem. Other interesting examples include ...
+{\it Summary. --}  We have shown how to create beams of particles to probe systems of cold atoms. 
+As an application of our proposal we have used the one-dimensional Bose polaron problem. The same concept
+can be used to study two-, three- and mixed-dimensional systems. Other interesting applications.
 
 \begin{acknowledgments}
-We thank Michael Fleischhauer for referring to~\cite{paper}.
+We thank Georg Bruun for referring to~\cite{zaccanti2017}.
 A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation.
@@
 
-To model one impurity atom that moves through the one-dimensional environment made of $N$ cold bosonic atoms, we employ the following Hamiltonian
+To model one impurity atom that moves through a one-dimensional environment made of $N$ cold bosonic atoms, we employ the following Hamiltonian
 \begin{equation}
-H=-\frac{\hbar^2}{2m}\sum_{i=1}^N\frac{\partial^2}{\partial x_i^2}-\frac{\hbar^2}{2M}\frac{\partial^2}{\partial y^2}+g\sum_{i>j=1}^N\delta(x_i-x_j)+c\sum_{i=1}^N \delta(x_i-y),
+H=-\frac{\hbar^2}{2m}\sum_{i=1}^N\frac{\partial^2}{\partial x_i^2}-\frac{\hbar^2}{2M}\frac{\partial^2}{\partial y^2}+\lambda \sum_{i>j=1}^N\delta(x_i-x_j)+g \sum_{i=1}^N \delta(x_i-y),
 \end{equation}
-where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are described by the set of coordinates $\{x_i\}$. 
-We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $g$ and $c$ respectively. 
-The reservoir by assumption is large, such that the dynamics can be described by the thermodynamic limit $N\to \infty$ assuming a certain value of the density $\rho$.
-To take the thermodynamic limit we set the periodic boundary conditions: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
-This assumption is not essential for our problem, because we are interested in the limit $N(L)\to \infty$ with $\rho=\frac{N}{L}$.
+where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are at the coordinates $\{x_i\}$. 
+We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$ respectively. 
+The reservoir by assumption is large, such that the dynamics can be described by the thermodynamic limit $N\to \infty$ with a given density $\rho$.
+To approach this limit, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
+We are interested in the limit $N(L)\to \infty$ with $\rho=\frac{N}{L}$.
 
-Every eigenfunction of the Hamiltonian can be written as $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. Because all interactions are pairwise, 
-the total (angular) momentum of the system must be conserved, and we write it as $P=\frac{2\pi\hbar}{L}\left(\sum_{j} n_j+m\right)$.
-Since we have a conserved quantity ($P$), we may exclude the coordinate of the impurity from the consideration. To this end, 
-we write the function $\Psi$ as $\Psi=e^{i \frac{P y}{\hbar}}\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jz_j}{L}}\equiv e^{i \frac{P y}{\hbar}} \psi(z_1,...,z_N)$ 
-with $z_i=L\theta(x_i-y)+x_i-y$, where $\theta(x)$ is the Heavyside step function, i.e., 
-$\theta(x>1) = 1$ and zero otherwise. The variables $z_i$ are defined such that $0\leq z_i \leq L$ and the impurity is placed at $z=0$ and $z=L$. Now if we insert this 
-function into the Schr{\"o}dinger equation, $H\Psi={\cal E}\Psi$, we obtain the following equation for $\psi(0<z_i<L)$
+For $c=0$ the eigenstates can be written as $e^{2\pi i \frac{n_1x_1+\ldots+n_N x_N+my}{L}}$, where $n_1,\ldots,n_N$ and $m$ are arbitrary integrers. 
+For $c>0$ this basis set can be used to expand an eigenfunction of the Hamiltonian, $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. 
+Because all interactions are pairwise, 
+the total (angular) momentum of the system must be conserved, and we write it as ${\cal P}=\frac{2\pi\hbar}{L}\left(\sum_{j} n_j+m\right)$.
+A conserved quantity (${\cal P}$) allows us to exclude one variable from the consideration. 
+We write the function $\Psi$ as $\Psi=e^{i \frac{{\cal P} y}{\hbar}}\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jz_j}{L}}\equiv e^{i \frac{{\cal P} y}{\hbar}} \psi(z_1,...,z_N)$ 
+with $z_i=L\theta(y-x_i)+x_i-y$, where $\theta(x)$ is the Heaviside step function, i.e., 
+$\theta(x>0) = 1$ and zero otherwise. The variables $z_i$ are defined such that $0\leq z_i \leq L$ and the impurity is placed at $z=0$ ($z=L$). Now if we insert this 
+function into the Schr{\"o}dinger equation, $H\Psi=E\Psi$, we obtain the following equation for $\psi(0<z_i<L)$
 \begin{equation}
--\frac{\hbar^2}{2m}\sum_i\frac{\partial^2 \psi}{\partial z_i^2}-\frac{\hbar^2}{2M}\left(\sum_{i}\frac{\partial \psi}{\partial z_i}\right)^2
-+ i \frac{\hbar P}{M}\sum_{i}\frac{\partial \psi}{\partial z_i}+g\sum_{i>j}\delta(z_i-z_j)\psi=\left({\cal E}-\frac{P^2}{2M}\right)\psi,
+-\frac{\hbar^2}{2m}\sum_i\frac{\partial^2 \psi}{\partial z_i^2}-\frac{\hbar^2}{2M}\left(\sum_{i}\frac{\partial }{\partial z_i}\right)^2\psi
++ i \frac{\hbar {\cal P}}{M}\sum_{i}\frac{\partial \psi}{\partial z_i}+\lambda \sum_{i>j}\delta(z_i-z_j)\psi=\left(E-\frac{{\cal P}^2}{2M}\right)\psi,
 \end{equation}
@@
 \begin{equation}
-\psi(z_i=0)=\psi(z_i=L); \qquad \frac{\partial \psi}{\partial z_i}\bigg|^{z_i=0^+}_{z_i=L^-}= \frac{2 c \kappa}{\hbar^2} \psi(z_i=0),
+\psi(z_i=0)=\psi(z_i=L); \qquad \frac{\partial \psi}{\partial z_i}\bigg|^{z_i=0^+}_{z_i=L^-}= \frac{2 g \kappa}{\hbar^2} \psi(z_i=0),
 \end{equation}
@@
 
-By assumption the bosons are weakly-interacting, therefore we use the ansatz $\psi=\prod_i \Phi(z_i)$ to approximate the function. 
-To minimize the expectation value of the Hamiltonian the function $\Phi(z)$ must satisfy the following Gross-Pitaevski-type equation
+By assumption the bosons interact weakly, such that the ansatz $\psi=\prod_i \Phi(z_i)$ can be used to approximate the system. 
+To minimize the expectation value of the Hamiltonian the function $\Phi(z)$ must satisfy the following non-linear Schr{\"o}dinger equation
 \begin{equation}
--\frac{\hbar^2}{2\kappa}\frac{\partial^2\Phi}{\partial z^2}+i\frac{\hbar P}{M}\frac{\partial \Phi}{\partial z}
--i \frac{\hbar^2 (N-1) A}{M} \frac{\partial\Phi}{\partial z} + g(N-1)|\Phi|^2\Phi=\mu \Phi,
+-\frac{\hbar^2}{2\kappa}\frac{\partial^2\Phi}{\partial z^2}+i\frac{\hbar {\cal P}}{M}\frac{\partial \Phi}{\partial z}
+-i \frac{\hbar^2 (N-1) A}{M} \frac{\partial\Phi}{\partial z} + \lambda (N-1)|\Phi|^2\Phi=\mu \Phi,
 \end{equation}
-where $A=-i\int \Phi(x)^*\frac{\partial}{\partial x}\Phi(x)\mathrm{d}x$ defines the momentum of a boson, and $\mu$ is the chemical potential (it appears as the Lagrange multiplier). 
+where $A=-i\int \Phi(x)^*\frac{\partial}{\partial x}\Phi(x)\mathrm{d}x$ defines the momentum of a boson, and $\mu$ is the Lagrange multiplier. 
 We rewrite this equation as
 \begin{equation}
--\frac{\partial^2\Phi}{\partial z^2}+i v \frac{\partial \Phi}{\partial z} + \tilde g(N-1)|\Phi|^2\Phi+\tilde c\delta(z)\Phi=\tilde\mu\Phi,
+-\frac{\partial^2\Phi}{\partial z^2}+i v \frac{\partial \Phi}{\partial z} + \tilde \lambda (N-1)|\Phi|^2\Phi=\tilde\mu\Phi,
 \label{eq:GPE_resc}
 \end{equation}
-where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde g=\frac{2 \kappa g}{\hbar^2}$, $\tilde c=\frac{2 \kappa c}{\hbar^2}$ and 
-$v\equiv \frac{2 \kappa P_I}{M \hbar}$, where $P_I=P-\hbar A(N-1)$ defines the momentum of the impurity in the thermodynamic limit.
-Note the corresponding boundary conditions 
+where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde \lambda =\frac{2 \kappa \lambda}{\hbar^2}$, and 
+$v\equiv \frac{2 \kappa P}{M \hbar}$, where $P={\cal P}-\hbar A(N-1)$ defines the momentum of the impurity in the thermodynamic limit;
+note that because $A$ is determined by $P$, there is a unique value of ${\cal P}$ for a given $P_I$.
+The corresponding boundary conditions read
 \begin{equation}
-\Phi(z=0)=\Phi(z=L); \qquad \frac{\partial \Phi}{\partial z}\bigg|^{z=0^+}_{z=L^-}= \tilde c \Phi(0),
+\Phi(z=0)=\Phi(z=L); \qquad \frac{\partial \Phi}{\partial z}\bigg|^{z=0^+}_{z=L^-}= \tilde g \Phi(0),
 \end{equation}
-
-This non-linear equation~(\ref{eq:GPE_resc}) has an analytic solution for the soliton-like behavior~\cite{ishikawa1980,hakim1997}, which determines the properties 
-of the polaron in our problem. Let us first consider the case with $c=0$. In this case the solution for $v>0$ is
+where $\tilde g= \frac{2\kappa g}{\hbar^2}$. The non-linear equation~(\ref{eq:GPE_resc}) 
+has an analytic steady solution~\cite{hakim1997}, which determines the properties 
+of the polaron in our problem. Let us first consider the non-interacting case $\lambda=0$. In this case the solution for $v>0$ is~\cite{tsuzuki1971, ishikawa1980}
 \begin{equation}
-\Phi=\sqrt{\frac{\tilde \mu}{\tilde g(N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z+z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z+z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\label{eq:Phi_c0}
 \end{equation}
@@
 \phi(z)=-\pi\theta(z+z_0)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
+\label{eq:phi_c0}
 \end{equation}
-where  $\beta=1- v^2/(2\tilde \mu)$, and $z_0$ is some parameter that should be determined from the boundary conditions.
-It is worthwhile noting that the solution for $v<0$ is $\Phi^*$.
-We plot this solution in Figs.~\ref{fig:Fig1} and~\ref{fig:Fig2}; for simplicity we consider the region $-L/2<z<L/2$, the region $0<z<L$ easily follows.
-Note that the solution is not periodic (see $\phi$), however by combining two solution with $\pm z_0$
-we can construct a periodic solution with a singularity at $z=0$. Therefore, the polaron in this picture is a combination of two moving solitons: The impurity creates a topological defect, which 
-leads to a quasiparticle picture.
+where  $\beta=1- v^2/(2\tilde \mu)$, and $z_0$ is some parameter that determines the origin. It is worthwhile noting that the solution for $v<0$ is $\Phi^*$. 
+The solution from Eqs.~(\ref{eq:Phi_c0}) and~(\ref{eq:phi_c0}) is plotted in Fig.~\ref{fig:Fig1}; 
+for simplicity it is plotted in the interval $-L/2<z<L/2$, the region $0<z<L$ easily follows. By combining the solutions with $\pm z_0$ 
+one can construct a steady solution with a singularity at $z=0$~\cite{hakim1997}. Therefore, the `polaron' in this model is a superposition of two moving solitons. 
+In other words, the impurity creates a topological defect, which leads to a dissipationless propagation.
 
@@
 \begin{figure}
-\centerline{\includegraphics[scale=0.5]{density.pdf}}
-\caption{The density, $|\Phi|^2$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left curve), $z_0=-0.2$, assuming that $\tilde \mu=1.6, v=0.3$ (everything in arbitrary units). 
-Note that the minimum of the density is at $-z_0$.}
+\centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
+\caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
+assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
+Note that the minimum of the density is at $-z_0$.
+The shaded area is a combination of the two solutions with the singularity at $z=0$.
+Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
 \label{fig:Fig1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centerline{\includegraphics[scale=0.5]{phase.pdf}}
-\caption{The phase, $\phi$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left curve), $z_0=-0.2$, assuming that $\tilde \mu=1.6, v=0.3$ (everything in arbitrary units).}
-\label{fig:Fig2}
 \end{figure}
@@
 \begin{equation}
-\Phi=\sqrt{\frac{\tilde \mu}{\tilde g(N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z\pm z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z\pm z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
 \end{equation}
@@
 \phi(z)=\delta \phi \theta(-z)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z\pm z_0)\right]-2\beta+1}\right),
+\label{eq:phase_soliton}
 \end{equation}
-where the parameter $\delta \phi$ is not important for the further derivations, it reassures that the function is periodic  
-(in the thermodynamic limit it is written as $2\pi - \mathrm{arctan}\left[\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{1-2\beta}\right]$);
-the plus sign in $\pm$ corresponds to $z>0$ and the minus sign to $z<0$. The wave function can be easily visualised from Figs.~\ref{fig:Fig1} and~\ref{fig:Fig2}. 
-The density has a non-analytic derivative at $z=0$. The phase is discontinuous function at $z=0$ (the derivative is continuous).
+where $z_0>0$ is discussed below, the parameter $\delta \phi$ is not important for the further derivations, it reassures that the phase is a continuous function;
+the plus sign in $\pm$ corresponds to $z>0$ and the minus sign to $z<0$. This function is illustrated in Fig.~\ref{fig:Fig1}. 
+The density has a non-analytic derivative at $z=0$. The phase is a continuous function at $z=0$ (its derivative is also continuous).
+Note that the wave function is not periodic (see Eq.~(\ref{eq:phase_soliton})). This non-periodicity is not important 
+for our discussion, because we are interested in the behavior of the bosons close to the impurity. It suggests that a grey soliton
+must be formed upon a change of interaction parameters to take care of the phase slip.
 
-The corresponding chemical potential is found from the normalization condition $\int \Phi^2=1$, for large values of $N$ and $L$ it reads
+The parameter $\tilde \mu$ is found from the normalization condition $\int \Phi^2=1$. For $N\to\infty$, we obtain
 \begin{equation}
-\tilde \mu=\gamma \rho^2 \frac{N-1}{N}\left(1-2\sqrt{2\beta} \frac{ (\mathrm{tanh}(d)-1)}{\sqrt{\gamma}N}\right),
+\tilde \mu=\gamma \rho^2 \frac{N-1}{N}\left(1-2\sqrt{2\beta_0} \frac{ (\mathrm{tanh}(d)-1)}{\sqrt{\gamma}N}\right),
 \end{equation}
-where $\rho=N/L$, $\gamma=\tilde g/\rho$, and $d=\sqrt{\frac{\gamma \beta}{2}}\rho z_0$.
-The condition on $z_0$ is found by using the boundary conditions at $z=\{0,L\}$
+where $\gamma=\tilde \lambda /\rho$, $\rho=N/L$, $\beta_0=1-v^2/(2\gamma \rho^2)$, and $d=\sqrt{\frac{\gamma \beta_0}{2}}\rho z_0$.
+The equation to determine $z_0$ is found by using the boundary conditions at $z=\{0,L\}$
 \begin{equation}
-\frac{\tilde c}{\rho \sqrt{2\gamma}}=\frac{\beta^{\frac{3}{2}}\tanh(d)}{-\beta+\cosh^2(d)}.
+\frac{\tilde g}{\rho \sqrt{2\gamma}}=\frac{\beta_0^{\frac{3}{2}}\tanh(d)}{-\beta_0+\cosh^2(d)}.
+\label{eq:c_v}
 \end{equation}
 This equation is cubic (in $\tanh(d)$), hence, the solutions can be found in a closed form.
+There are three solutions. However, only two will lead to the acceptable values of $z_0$. 
+We will refer to these steady solutions as the `polaron' and the `polaron-soliton' pair, because in the limit $g\to 0$ the former 
+corresponds to the ground state, and the latter to a gray soliton. 
+The `polaron-soliton' pair is expected to be unstable (small perturbations will lead to 
+a decay of this steady solution~\cite{hakim1997}),
+therefore, we do not consider it. The solutions merge for $z_m$ 
+\begin{equation}
+\tanh^2\left(\sqrt{\frac{\gamma \beta_0}{2}}\rho z_m\right)=\frac{\sqrt{1+\frac{4v^2}{\gamma \rho^2}}-(1+\frac{v^2}{\gamma \rho^2})}{2\beta_0},
+\label{eq:z_m}
+\end{equation}
+which is derived by taking a derivative of Eq.~(\ref{eq:c_v}) with respect to $z_0$ and equating the resulting expression to zero -- this determines 
+the maximum value of $g$ for which (for a fixed $\beta_0$) there is a steady solution.
+Equations~(\ref{eq:c_v}) and (\ref{eq:z_m}) give the equation for the critical value of $v_c$:
+\begin{equation}
+\frac{\tilde g}{\rho\sqrt{\gamma}}=\frac{3-\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}{-1+\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}\sqrt{\sqrt{1+\frac{4v_c^2}{\gamma \rho}}-1-\frac{v_c^2}{\gamma\rho^2}}.
+\end{equation}
+For $v>v_c$ (see Fig. 1 of the main text) there is no steady solutions.
+
 Now we can calculate the energy of the polaron in the thermodynamic limit
 \begin{equation}
-E\equiv \lim_{N\to\infty, \frac{N}{L}\to \rho}\left[{\cal E}(c,P)-{\cal E}(c=0,P=0)\right],
+{\cal E}\equiv \lim_{N\to\infty, \frac{N}{L}\to \rho}\left[E(c,P)-E(c=0,P=0)\right],
 \end{equation}
@@
 \begin{equation}
-{\cal E}(c,P) = \frac{P^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-gN(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
+E(c,P) = \frac{P^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-gN(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
 \end{equation}
@@
 \begin{equation}
-E=\frac{P_I^2}{2M}+\frac{\hbar^2\rho}{2\kappa}\frac{\sqrt{2 \tilde g \rho \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P_I}{M}\lim_{N\to\infty} A N,
+{\cal E}=\frac{P_I^2}{2M}+\frac{\hbar^2\rho}{2\kappa}\frac{\sqrt{2 \tilde g \rho \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P_I}{M}\lim_{N\to\infty} A N,
 \end{equation}
@@
 \begin{equation}
-E\simeq \epsilon+ \frac{P_I^2}{2m_{\mathrm{\mathrm{eff}}}},
+{\cal E}\simeq \epsilon+ \frac{P_I^2}{2m_{\mathrm{\mathrm{eff}}}},
 \end{equation}
 where $\epsilon$ is the effective energy of the polaron, and $m_{\mathrm{eff}}$ is the effective mass.
-
-Further Discussions in the supplementary material and in the paper:
-
-Discuss the effective mass.
-
-Discuss the two different solutions.
-
-Discuss the critical momentum.
-
-Discuss the quench dynamics to the polaron.
-
-Discuss the literature.
 

### 2019-01-07 Paper/version2/paper.tex
Drafted text for methods section

--- 2018-10-18 Paper/version2/paper.tex
@@
 \usepackage{array}
+\usepackage{subcaption}
 \usepackage{graphicx}
@@
 
-Figure \ref{fig:method_examples} demonstrates the application of the procedure described above to three scenarios: the comb potential, evaporative cooling, and anti-evaporative cooling.
-Each figure shows the resulting link potential $V_0(x)$ along with the target and actual momentum-transmission profiles.
+\subsection{Single-comb transport profile}
+To illustrate the method described above we optimize for a single-comb transport profile sharply-peaked near $k=1$ ($\hbar=2m=1$).
+For our target transport profile, we use a Lorentz distribution peaked at $k=1$ and with a small HWHM (see Figure~\ref{fig:method_illustration}, top).
+For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.X$, $\sigma_{\mathrm{max}}=Y.Y$, $A_{\mathrm{min}}=0.X$, and $A_{\mathrm{max}}=Y.Y$.
+We simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
+The resulting optimization has three parameters.
+Despite the few parameters, the cost function for this optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$.
+So, while this is a very simple example, it still requires a method for globally searching the space of link potentials.
 
-{\it Figure 2: Examples of a few profiles that can be created: comb, evaporative, anti-evaporative etc. In the insets are the corresponding potentials.}
+Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the single-comb optimization.
+The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
+This additional resonance need not be a problem if the scattering atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$.
+The two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see inset).
+Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure}
+   \includegraphics[width=1\linewidth]{figures/plot_transport_profiles.pdf}
+   \includegraphics[width=1\linewidth]{figures/plot_link_potential.pdf}
+ \caption[Single comb link potential]{Two-Gaussian solution for the $k=1$ comb transport profile.
+The top figure shows the target profile (dot-dashed, red) used during optimization and the actual profile resulting from the optimization procedure.
+The inset is a zoomed-in view of the region around the peak near $k=1$.
+The bottom figure shows the optimal link potential $V(x)$.}
+ \label{fig:method_illustration}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+It may be experimentally problematic if the transport profile shown in Figure \ref{fig:method_illustration} were highly sensitive to the potential parameters.
+Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired potential.
+To test this sensitivity, we generate 200 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
+The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Figure \ref{fig:sensitivity}.
+Both the peak positions, $k_0$, and the peak heights, $T_0$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
+When optimizing with 3- or 4-Gaussian potentials, we found that solutions tended to be extremely sensitive to the potential parameters.
+If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
+
+Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as double-comb or step transport profiles for various experimental scenarios.
+We find that these more complicated transport profiles require more than two Gaussian potentials and that the solutions using the procedure we describe are highly-sensitive to the potential parameters.
+We leave the thorough exploration of these ideas to future work.
+In the next section, we discuss a possible experimental application of the single-comb solution.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
+\begin{figure}
+   \includegraphics[width=1\linewidth]{figures/plot_sensitivity.pdf}
+ \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.
+Shown are the distributions of the peak position $k_0$ (main graph) and peak height $T_0$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential shown in Fig.~\ref{fig:method_illustration}.
+}
+ \label{fig:sensitivity}
+\end{figure}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-02-04 Paper/version2/paper.tex
Halfway done working through Artem comments

@@
 \usepackage{array}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{graphicx}
@@
 \begin{abstract}
-We propose a scheme for engineering fluxes of cold atoms with given momentum profiles. 
-In our proposal, the flux is created using a link potential that selects desired momenta 
-from the bath. We discuss how to determine the link potential given the required profile 
-of a beam, and present a topical application, in which the beam is used 
-to study Bose polarons. 
+We propose a scheme for engineering fluxes of cold atoms with useful momentum profiles. 
+In our proposal, the flux is created by selecting particles from a trapped gas.
+The selection is achieved by connecting the gas to an external potential that enhances
+the tunnelling probablity for atoms with desired momenta. 
+We discuss how to find this potential given a requested profile 
+of a beam, and discuss a topical application, in which a beam narrow in momentum space 
+is used to create Bose polarons. Such a beam can give an access to the self-energy and the effective 
+mass of the polaron, as well as to the corresponding critical momentum.
 \end{abstract}
@@
 
-{\it Introduction. --} In systems of cold atoms the typical energies are so 
-low that usually only a few quantities (e.g., the scattering length and the three-body parameter) 
-determine physics~\cite{braaten2006, bloch2008}. 
-When these parameters are known the outcomes of measurements can be predicted. 
-Ultracold beams with a given momentum might be very useful for determining these parameters. 
-For example, the effective mass of a Fermi or Bose `polaron'~\cite{zwierlein2009,hu2016,arlt2016}
-can be obtained by studying a beam of particles with a given momentum inside a degenerate gas.
-Furthermore, ultracold beams can give new 
-insight into the systems where non-universal energy-dependent phenomena have been observed. For instance, it can help 
-to understand the temperature (energy) dependence of the three-body parameter~\cite{naidon2011, huang2015, wacker2018}.
+{\it Introduction. --} 
+A scattering off a target is
+universally used to study properties of particles and materials {\color{blue} more?}.  
+In this Letter we discuss how to create cold-atom beams
+of given momentum profiles, which is a prerequisite for scattering experiments
+with quantum gases. 
+Such beams can be useful for measuring parameters that define
+physics of cold-atoms systems. It can be few-body parameters such as
+the scattering length and the three-body parameter~\cite{braaten2006, bloch2008}.
+The parameters of interest can also incorporate many-body effects, such as the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
 
-In this Letter, we propose an approach for engineering beams of cold atoms. 
-Our proposal is illustrated in Fig.~\ref{fig:Figure1}: The particles in a reservoir scatter off the link potential with 
-some desired transmission coefficient, $T_0(k)$. The function $T_0(k)$ allows only particles with a given momentum to 
-tunnel through the barrier into the `flux region'. In spirit, our scheme is similar to a quantum switch device 
-(`transistor')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' is affected by changing the properties of the `gate'.
-However, the present proposal in addition to completely switching off the flux, allows one to engineer the momentum profile of the flux.
+Our proposal for engineering beams of cold atoms is summarized in Fig.~\ref{fig:Figure1}.
+For simplicity, we illustrate the method using a one-dimensional geometry 
+(a cylindrically symmetric three-dimensional case is identical to that
+within our formalism). The particles in a reservoir are non-interacting~\footnote{
+Strong interactions can lead to the transmission behavior that is not captured by the one-body Schr{\"o}dinger equation, e.g.,
+to a collective resonant transport~\cite{Schlagheck2005}.},
+so that their scattering properties are found by solving the one-body Schr{\"o}dinger equation
+\begin{equation}
+-\frac{\hbar^2}{2m}\frac{\partial^2}{\partial x^2}\psi+V_0(x)\psi=\frac{\hbar^2k^2}{2m}\psi,
+\label{eq:schr}
+\end{equation}
+where $m$ is the mass of a particle from the reservoir, $\frac{\hbar^2k^2}{2m}$ is its energy.
+The link potential $V_0(x)$ has the transmission coefficient, $T_0(k)$, that allows only particles with desired momenta to 
+tunnel through the barrier into the `flux region'. 
+The momentum profile of particles in the `flux region' can be measure using a single-atom momentum resolution (e.g.,~\cite{jochim2018}),
+which allows one to confirm that the desired beam has been produced.
 
-To confirm that the flux has been created one can use a single-atom momentum resolution to check the momentum profile of the flux~\cite{jochim2018}.
+In this Letter, we discuss how to 
+find $V_0(x)$ for a given function $T_0(k)$, and use the Bose polaron problem
+to illustrate a possible application of cold-atom beams. It is worthwhile noting that 
+our scheme is inspired by quantum switch devices 
+(`transistors')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' is affected by changing the properties of the `gate'.
+The benefit of the present set-up is that in addition to completely switching off the transmission, it allows one to design the momentum profile 
+of the flux.
 
@@
 \centerline{\includegraphics[scale=0.3]{figure1new.pdf}}
-\caption{An illustration of the proposal: The reservoir that contains particles of various momenta is connected to the external potential. The design of this potential
-allows only particles with desired momenta to tunnel into the flux region.
+\caption{An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external potential. 
+The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, 
+the distribution is non-zero only in the neighborhood of a chosen momentum.
   }
@@
 
-\section{Design}
-
-\subsection{Physical System}
-Describe the system.
-The system has three parts: Two reservoirs and a link between them; see Figure 1a.
-One reservoir is made of a non-interacting (for simplicity) gas of particles at temperature $T$.
-We call these particles probes or $A$.
-The reservoir is connected to the link.
-The link is a potential that acts only on particles $A$ (for simplicity).
-The second reservoir is made of interacting particles $B$.
-These particles make a system of interest, which we would like to analyze.
-
-\subsection{Procedure for Finding a Link Potential}\label{sec:procedure_link}
+{\it Procedure for Finding a Link Potential. --}
 We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the $k$-integrated squared error between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
@@
 \begin{equation}\label{eq:cost1}
-  J_{\bm{\theta}} = \sum_kw_k\left|T_0(k) - T_{\mathbf{\theta}}(k)\right|^2,
+  J_{\bm{\theta}} = \sum_kw_k\left|T_0(k) - T_{\bm{\theta}}(k)\right|^2,
 \end{equation}
@@
 The weights are chosen to emphasize regions of $k$ during the minimization.
-For instance, when trying to create a ``comb'' potential that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$, then it would be appropriate to increase the weights in the region of $k_0$.
-We find that results are sensitive to the choice of $w_k$, and some trial and error was required to get acceptable potentials.
+For instance, when trying to create a potential barrow band-pass filter that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$ (see Fig.~\ref{fig:Figure1} and Fig.~\ref{fig:method_illustration}, top), then it would be appropriate to increase the weights in the region of $k_0$.
+The convergence of our approach was somewhat sensitive to the choice of $w_k$.
+To arrive at acceptible solutions, we progressively increased $w_k$ in the region of $k_0$ until we found solutions that effectively balanced the need to allow flux near $k_0$ and forbid flux far from $k_0$.
 
-With the goal of discovering experimentally viable solutions, we parameterize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussian potentials each of the form
+With the goal of discovering experimentally viable solutions, we parameterize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussians, each of the form
 \begin{equation}\label{eq:V-param}
-V_i(x; A_i, \mu_i, \sigma_i) = \frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right],
+V_i(x; A_i, \mu_i, \sigma_i) = \frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right];
 \end{equation}
+the parameter $\bm{\theta}$ denotes the parameter space $\{A_1, \mu_1, \sigma_1,...,A_N, \mu_N, \sigma_N\}$.
 While minimizing Eq.~\eqref{eq:cost1}, we enforce the parameter constraints listed in Table \ref{tab:constraints}.
-In addition to these explicit constraints on the parameters, we enforce an implicit constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
+In addition to these constraints on the parameters, we enforce an constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
 To accomplish this, we minimize the augmented cost
@@
 The full form is given in the suppl.~material.
-
-For a choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating Schr{\"o}dinger's equation across the region of the potential and calculating the ratio of the transmitted to the incident flux.
-In order to do this efficiently, we approximate the integral as a banded linear system of equations solvable in $O(M)$ time where $M$ is the number of $x$-steps.
-Using these techniques we are able to evaluate the transmission coefficient x thousand times per second on a 7th generation Intel Core i7 processor under the conditions used in our tests.
-
- We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
-This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
-Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
-Emperically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
 
@@
 
-\subsection{Single-comb transport profile}
-To illustrate the method described above we optimize for a single-comb transport profile sharply-peaked near $k=1$ ($\hbar=2m=1$).
-For our target transport profile, we use a Lorentz distribution peaked at $k=1$ and with a small HWHM (see Figure~\ref{fig:method_illustration}, top).
-For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.X$, $\sigma_{\mathrm{max}}=Y.Y$, $A_{\mathrm{min}}=0.X$, and $A_{\mathrm{max}}=Y.Y$.
-We simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
-The resulting optimization has three parameters.
-Despite the few parameters, the cost function for this optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$.
-So, while this is a very simple example, it still requires a method for globally searching the space of link potentials.
-
-Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the single-comb optimization.
-The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
-This additional resonance need not be a problem if the scattering atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$.
-The two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see inset).
-Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials.
+For a choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating the Schr{\"o}dinger equation~(\ref{eq:schr}) across the region of the potential and calculating the ratio of the transmitted to the incident flux.
+In order to do this efficiently, we discretize the second derivative in Eq.~(\ref{eq:schr}), which transforms Eq.~(\ref{eq:schr}) into
+a banded linear system of equations solvable in $O(M)$ time where $M$ is the number of $x$-steps.
+Using these techniques we are able to evaluate the transmission coefficient {\color{red} x} thousand times per second on a 7th generation Intel Core i7 processor under the conditions used in our tests.
 
@@
    \includegraphics[width=1\linewidth]{figures/plot_link_potential.pdf}
- \caption[Single comb link potential]{Two-Gaussian solution for the $k=1$ comb transport profile.
+ \caption[Narrow band-pass filter link potential]{Two-Gaussian solution for the $k=1$ narrow band-pass filter transport profile.
 The top figure shows the target profile (dot-dashed, red) used during optimization and the actual profile resulting from the optimization procedure.
 The inset is a zoomed-in view of the region around the peak near $k=1$.
-The bottom figure shows the optimal link potential $V(x)$.}
+The bottom figure shows the optimal link potential $V(x, \bm{\theta^*})$.
+{\color{blue} bold font, $k>2$?}}
  \label{fig:method_illustration}
@@
 
-It may be experimentally problematic if the transport profile shown in Figure \ref{fig:method_illustration} were highly sensitive to the potential parameters.
+ We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
+This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
+Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
+Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
+
+{\it Narrow band-pass filter transport profile. --}
+To illustrate the method described above we optimize for a narrow band-pass filter transport profile sharply-peaked near $k=k_0$.
+{\color{green} For simplicity, in what follows we adopt the units in which $k_0=\hbar=2m=1$}.
+For our target transport profile, we use a Lorentz distribution peaked at $k=1$ and with a small {\color{red} HWHM} (see Figure~\ref{fig:method_illustration}, top).
+For the constraints shown in Table~\ref{tab:constraints}, {\color{red} we use $\sigma_{\mathrm{min}}=0.X$, $\sigma_{\mathrm{max}}=Y.Y$, $A_{\mathrm{min}}=0.X$, and $A_{\mathrm{max}}=Y.Y$}.
+We simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
+{\color{green} We anticipate that this potential might be the easiest to realize in the laboratory. In addition, it is straithforward to visualize the transfer using quasi-discrete levels 
+in the link potential. 
+Note also that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of link potential is still required, because
+the cost function for the optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$. }
+
+Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the band-pass filter optimization.
+The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
+This additional resonance need not be a problem if the scattering atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{In general, one needs to include the momentum distribution of the reservoir, $n(k)$,
+in the cost function. To this end, one might multiply in Eq.~(\ref{eq:cost1}) $T_{\bm{\theta}}(k)$ by $n(k)$; the rest of the discussion is untouched.
+The function $n(k)$ can be determined by the Bose-Einstein or Fermi-Dirac distributions. The illustration in the text practically corresponds to a Fermi gas 
+at zero temperature, i.e., $n(k<k_F)=1$ and zero otherwise, with the Fermi energy that satisfies $1\ll k_F^2 \ll A_\mathrm{min}$}.
+ {\color{green}  Note that the two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see the inset in Fig.~\ref{fig:method_illustration}), and the second resonance might be used instead in practical applications.
+Indeed, the width of the first resonance is quite narrow,
+which requires long experimental runtime; for example, a reasonable assumption $\hbar^2k_0^2/(2m)=k_B\times 100$nK, where $k_B$ is the Boltzmann constant leads to 
+a single-particle time scale for tunnelling $\tau\sim 0.2 s$. In case this time scale is not experimentally realistic, the second resonance 
+can be used.} Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials {\color{blue} explain better?}.
+
+It may be experimentally problematic if the transport profile shown in Fig.~\ref{fig:method_illustration} were highly sensitive to the potential parameters.
 Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired potential.
 To test this sensitivity, we generate 200 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
-The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Figure \ref{fig:sensitivity}.
+The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Fig.~\ref{fig:sensitivity}.
 Both the peak positions, $k_0$, and the peak heights, $T_0$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
-When optimizing with 3- or 4-Gaussian potentials, we found that solutions tended to be extremely sensitive to the potential parameters.
+When optimizing with 3- or 4-Gaussian potentials, we found that solutions tended to be more sensitive to the potential parameters.
 If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
 
-Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as double-comb or step transport profiles for various experimental scenarios.
+Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as double band-pass filter or step transport profiles for various experimental scenarios.
 We find that these more complicated transport profiles require more than two Gaussian potentials and that the solutions using the procedure we describe are highly-sensitive to the potential parameters.
 We leave the thorough exploration of these ideas to future work.
-In the next section, we discuss a possible experimental application of the single-comb solution.
+In the next section, we discuss a possible experimental application of the narrow band-pass filter solution.
 
@@
 
-{\it Application. --} Consider a flux through a degenerate 
-one-dimensional Bose gas. If the current is low then the system 
-can be described using the concept of the polaron -- an impurity dressed by low-energy excitations 
-of the environment~\cite{landau1948}. Let us briefly describe the properties of this quasiparticle
-within an extension to the mean-field theory developed in Ref.~\cite{volosniev2017}
-for a zero momentum of the impurity~\footnote{See the Supplementary Material}; see also~\cite{kain2016, parisi2017,grusdt2017, pastukhov2017}. 
-According to this theory the lowest energy state of a system with a fixed value of momentum, $P$, 
-is a combination of two solitons which makes a dissipationless defect in the Bose gas, which we call the polaron. The corresponding energy 
+{\it Application. --} If one places a Bose or Fermi gas in the `flux region' (see Fig.~\ref{fig:Figure1}) then the resulting 
+system models an impurity-gas problem provided that the flux is dilute (no interactions for particles that make the beam).
+Quantum simulations of problems with mobile impurities is an important domain of cold-atoms 
+experiments~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017},
+and our proposal allows for investigating the dynamics of impurities that initially have 
+a known momentum profile. We illustrate this statement below by considering a flux through a degenerate 
+one-dimensional Bose gas.
+
+We assume that the flux is non-zero only 
+in the neighborhood of a chosen value $k_0$ as in Fig.~\ref{fig:method_illustration}.
+Therefore, for simplicity, we assume that the impurity has momentum $k_0$.
+If $k_0$ is small then the propagation of the impurity can be described using the polaron quasiparticle 
+-- an impurity dressed by low-energy excitations of the environment~\cite{landau1948}. 
+To model this quasiparticle, we use a non-linear Schr{\"o}dinger equation
+for a Bose gas with an impurity atom~\footnote{See the Supplementary Material for the solution to 
+the impurity-(Bose gas) problem}. The employed equation has been solved analytically
+in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, 
+which allows us to work out all properties of the polaron; 
+note that this (or similar) non-linear equation is used in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018}
+to extract some properties of impurities in a Bose gas,
+see also~\cite{kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies. 
+The lowest energy state of a system with a fixed value of the impurity momentum, $P$, in this model
+is a combination of two solitons. They make a dissipationless defect in the Bose gas, which we call the polaron. The corresponding energy 
 is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, 
@@
 for $P<P_c$, where $P_c$ defines the momentum above which the propagation flux produces grey solitons. 
-Note that quantum fluctuations will lead to some finite dissipation~\cite{astrakharchik2004,sykes2009} even for $P<P_c$, however
+Note that quantum fluctuations will lead to some finite dissipation~\cite{astrakharchik2004,sykes2009,Cherny2012} even for $P<P_c$, however
 we do no consider this effect in the present study.
 
-Ultracold beams can be used to study the properties of Bose polarons. For example, to measure the effective 
-mass one can prepare the flux of particles $B$ in the hyperfine state that does not 
-interact with the Bose gas. Then the particles $B$ can be transferred into a hyperfine state that strongly interacts with the gas.
-This transfer is possible only if one deposits the energy that compensates for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
-There is a non-zero overlap between a free particle and the polaron state; see~\cite{volosniev2017} for $P=0$.
-Therefore, by looking at the radio-frequency responce (e.g., the transferred fraction) at different momenta, the effective mass of the polaron can be extracted. 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\begin{figure}
+\centerline{\includegraphics[scale=0.3]{figure3.pdf}}
+\caption{Panel {\bf a)} shows schematically the energies of a free particle and
+a particle in a degenerate Bose gas. The possibility to create atom with a given momenta 
+will allow one to establish the effective mass of the polaron
+and the limits of applicability of the polaron model by measuring the energy difference, $\Delta(p)$, using the radio-frequency spectroscopy.
+Note that quasiparticle properties should be absent for high momenta $P>P_c$. For one spatial dimension, a typical momentum scale, $P_c$, 
+can be estimated  by considering the existence of steady solutions 
+of a relevant non-linear Schr{\"o}dinger equation; see the text for details. Panel {\bf b)} 
+shows the results for a heavy impurity of mass $M$; $c$ is the speed of sound in the gas
+and $g$ is the boson-impurity interaction strength.
+  }
+\label{fig:Figure3}
+\end{figure}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+Ultracold beams can be used to measure properies of Bose polarons, in particular $\epsilon, m_{\mathrm{eff}}$ and $P_c$.
+For example, to measure the effective 
+mass one prepares a flux of particles in a hyperfine state that does not 
+interact with the Bose gas. Then the beam particles can be transferred into a hyperfine state that strongly interacts with the gas.
+This transfer is possible only if one deposits enough energy to compensate for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
+Therefore, by looking at the radio-frequency responce (e.g., the transferred fraction) at different momenta, the self-energy and effective mass 
+of the polaron can be extracted. 
 This idea is similar to a recent experiment in a three-dimensional Fermi polaron~\cite{zaccanti2017}. However,
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centerline{\includegraphics[scale=0.3]{figure3.pdf}}
-\caption{Panel {\bf a)} shows schematically the energies of a free particle and a Bose polaron --
-a particle in a degenerate Bose gas. The possibility to create particles of a given momenta 
-will allow one to establish the effective mass of the polaron
-and the limits of applicability of the polaron model by measuring the energy difference, $\Delta(p)$, using the radio-frequency spectroscopy.
-Note that quasiparticle properties should be absent for high momenta. For one spatial dimension, a typical momentum scale can be estimated  by considering the existence of steady solutions 
-of a suitable non-linear Schr{\"o}dinger equation; see the text for details. Panel {\bf b)} 
-shows the results for a heavy impurity of mass $M$; $c$ is the speed of sound
-and $g$ is the boson-impurity interaction strength.
-  }
-\label{fig:Figure3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 {\it Summary. --}  We have shown how to create beams of particles to probe systems of cold atoms. 
-As an application of our proposal we have used the one-dimensional Bose polaron problem. The same concept
-can be used to study two-, three- and mixed-dimensional systems. Other interesting applications.
+As an application of our proposal we have used the one-dimensional Bose polaron problem.
+We anticipate that the ideas discussed in this Letter can be used to study two-, three- and mixed-dimensional polaron systems {\color{blue} refrences}, temperature (energy) dependence of Efimov trimers~\cite{naidon2011, huang2015, wacker2018}, thermalization in systems with a hole in the momentum space (similar to that in a coordinate space {\color{blue} references}), etc {\color{blue} more details?}).
 
 \begin{acknowledgments}
-We thank Georg Bruun for referring to~\cite{zaccanti2017}.
-A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation.
+We thank Georg Bruun and Peter Schlagheck for referring to~\cite{zaccanti2017} and~\cite{Schlagheck2005}
+correspondingly, and Joachim Brand and Volodymyr Pastukhov for useful discussions.
+A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation and the Deutsche Forschungsgemeinschaft
+(VO 2437/1-1).
 \end{acknowledgments}
@@
 \section{Polaron}
+
+{\color{blue} Discuss the residue} 
+There is a non-zero overlap between a free particle and the polaron state; see~\cite{volosniev2017} for $P=0$.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
-\caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
-assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
-Note that the minimum of the density is at $-z_0$.
+% \begin{figure}
+% \centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
+% \caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
+% assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
+% Note that the minimum of the density is at $-z_0$.
 The shaded area is a combination of the two solutions with the singularity at $z=0$.
 Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
-\label{fig:Fig1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% \label{fig:Fig1}
+% \end{figure}
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-02-13 Paper/version2/paper.tex
New draft...

@@
 \DeclareMathOperator*{\argmin}{argmin}
+\DeclareMathOperator\erf{erf}
+\DeclareMathOperator\erfc{erfc}
 
@@
 The convergence of our approach was somewhat sensitive to the choice of $w_k$.
-To arrive at acceptible solutions, we progressively increased $w_k$ in the region of $k_0$ until we found solutions that effectively balanced the need to allow flux near $k_0$ and forbid flux far from $k_0$.
+
+We developed a strategy for choosing the weights that takes into account the following considerations: 1) the transport coefficient is constrained to be zero for $k=0$ so the weight can be smaller for small $k$, 2) the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to supress flux at large $k$, and 3) to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
+Follwing these principles, we arrive at the following formula for the weight function:
+\begin{equation}\label{eq:weight-of-k}
+  w(k;r) = w_{\mathrm{bg}}(k) + rT_0(k)
+\end{equation}
+where $w_{\mathrm{bg}}(k)$ is chosen to account for considerations 1 and 2 above, and the term proportional to the positive constant $r$ accounts for consideration 3.
+For $w_{\mathrm{bg}}(k)$, we use the {\color{blue} transport profile resulting from a morse potential WITH WHAT PARAMS?}:
+\begin{equation}\label{eq:weight-of-k}
+  w_{\mathrm{bg}}(k) = \left[\frac{\sinh^2(\sqrt{2}\pi k)}{\sinh^2(\sqrt{2}\pi k) + \cosh^2(\sqrt{7}\pi/2)}\right]^{1/2}.
+\end{equation}
+The parameter $r$ was chosen by trial and error for each target profile $T_0(k)$.
 
@@
 In addition to these constraints on the parameters, we enforce an constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
-To accomplish this, we minimize the augmented cost
+To accomplish this, we minimize the boundary-augmented cost function
 \begin{equation}\label{eq:cost2}
@@
 The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
-The full form is given in the suppl.~material.
+The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in the suppl.~material.
 
@@
 a banded linear system of equations solvable in $O(M)$ time where $M$ is the number of $x$-steps.
-Using these techniques we are able to evaluate the transmission coefficient {\color{red} x} thousand times per second on a 7th generation Intel Core i7 processor under the conditions used in our tests.
+Using these techniques we are able to evaluate the transmission coefficient 3.7 thousand times per second on a 7th generation Intel Core i7 processor for a test involving 1,000 randomly generated two-Gaussian potentials and 100 different scattering momenta.
 
@@
 \begin{figure}
-   \includegraphics[width=1\linewidth]{figures/plot_transport_profiles.pdf}
-   \includegraphics[width=1\linewidth]{figures/plot_link_potential.pdf}
+   \includegraphics[width=1\linewidth]{figures/plot_transport_profiles_with_inset.pdf}
  \caption[Narrow band-pass filter link potential]{Two-Gaussian solution for the $k=1$ narrow band-pass filter transport profile.
-The top figure shows the target profile (dot-dashed, red) used during optimization and the actual profile resulting from the optimization procedure.
-The inset is a zoomed-in view of the region around the peak near $k=1$.
-The bottom figure shows the optimal link potential $V(x, \bm{\theta^*})$.
+The main figure shows the target profile (dot-dashed, red) used during optimization and the actual transport profile resulting from the optimization procedure (solid, blue).
+The inset figure shows the optimal link potential $V(x, \bm{\theta^*})$.
 {\color{blue} bold font, $k>2$?}}
@@
 
- We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{original DE paper}.
+We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{storn1997differential}.
 This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
 Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
-Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing \cite{Tests performed using mathematica}.
+Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing for this particular optimization problem.
 
@@
 To illustrate the method described above we optimize for a narrow band-pass filter transport profile sharply-peaked near $k=k_0$.
-{\color{green} For simplicity, in what follows we adopt the units in which $k_0=\hbar=2m=1$}.
-For our target transport profile, we use a Lorentz distribution peaked at $k=1$ and with a small {\color{red} HWHM} (see Figure~\ref{fig:method_illustration}, top).
-For the constraints shown in Table~\ref{tab:constraints}, {\color{red} we use $\sigma_{\mathrm{min}}=0.X$, $\sigma_{\mathrm{max}}=Y.Y$, $A_{\mathrm{min}}=0.X$, and $A_{\mathrm{max}}=Y.Y$}.
-We simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
-{\color{green} We anticipate that this potential might be the easiest to realize in the laboratory. In addition, it is straithforward to visualize the transfer using quasi-discrete levels 
-in the link potential. 
-Note also that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of link potential is still required, because
-the cost function for the optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$. }
+For simplicity, we adopt the units in which $k_0=\hbar=2m=1$.
+For our target transport profile, we use a Lorentz profile
+\begin{equation}\label{eq:Ttarget}
+  T(k; k_0,b) = \left[1 + \frac{(k-k_0)^2}{b^2}\right]^{-1}
+\end{equation}
+with $k_0=1$ and $b=0.03$ (see Figure~\ref{fig:method_illustration}).
+For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.2$, $\sigma_{\mathrm{max}}=3$, $A_{\mathrm{min}}=5$, and $A_{\mathrm{max}}=30$.
+We further simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
+We anticipate that this potential might be the easiest to realize in the laboratory.
+In addition, it is straithforward to visualize the transfer using quasi-discrete levels in the link potential.
+Note also that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of link potential is still required, because the cost function for the optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$.
 
@@
 at zero temperature, i.e., $n(k<k_F)=1$ and zero otherwise, with the Fermi energy that satisfies $1\ll k_F^2 \ll A_\mathrm{min}$}.
- {\color{green}  Note that the two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see the inset in Fig.~\ref{fig:method_illustration}), and the second resonance might be used instead in practical applications.
+ {\color{red}  Note that the two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see the inset in Fig.~\ref{fig:method_illustration}), and the second resonance might be used instead in practical applications.
 Indeed, the width of the first resonance is quite narrow,
@@
 a single-particle time scale for tunnelling $\tau\sim 0.2 s$. In case this time scale is not experimentally realistic, the second resonance 
-can be used.} Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials {\color{blue} explain better?}.
+can be used.
+Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials.
+}
 
@@
 
-Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as double band-pass filter or step transport profiles for various experimental scenarios.
+Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles for various experimental scenarios.
 We find that these more complicated transport profiles require more than two Gaussian potentials and that the solutions using the procedure we describe are highly-sensitive to the potential parameters.
@@
 
-\subsection{Cost Function}\label{sec:cost_function}
-
+\subsection{Boundary-Augmented Cost Function}\label{sec:Jaug}
+Equation \eqref{eq:cost2} shows the boundary-augmented cost function which includes a term that increases the cost for link-potential solutions that extend beyond the support region $x\in[-x_0,x_0]$.
+This added terms is
 \begin{equation}
-  J'_{\mathbf{\theta}} = J_{\mathbf{\theta}} + \alpha J_{\mathrm{boundary}},
+  J_{\mathrm{boundary}} = \alpha \sum_i^N J_{\mathrm{boundary}}^i,
 \end{equation}
-where $\alpha>0$ is the weight given to cost incurred for having the potential extend outside the support region of the potential.
+where 
+\begin{equation}\label{eq:Jboundaryi}
+  J_{\mathrm{boundary}}^i = \int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2.
+\end{equation}
+Assuming the Gaussian potential form in Eq.~\eqref{eq:V-param}, this evaluates to
+\begin{equation}\label{eq:JboundaryIGaussian}
+  J_{\mathrm{boundary}}^i = \frac{\sqrt{\pi}}{2}A_i^2\sigma_i\left[
+    \erfc\left(\frac{x_0+\mu_i}{\sigma_i}\right) +
+    \erfc\left(\frac{x_0-\mu_i}{\sigma_i}\right)
+  \right],
+\end{equation}
+where $\erfc$ is the complementary error function.
 

### 2019-02-25 Paper/version2/paper.tex
Polished Version

@@
 
-\title{Engineering momentum profiles of cold-atom beams}
+\title{Engineering momentum profiles of cold-atom {\color{blue} streams}}
 
@@
 \begin{abstract}
-We propose a scheme for engineering fluxes of cold atoms with useful momentum profiles. 
-In our proposal, the flux is created by selecting particles from a trapped gas.
-The selection is achieved by connecting the gas to an external potential that enhances
-the tunnelling probablity for atoms with desired momenta. 
-We discuss how to find this potential given a requested profile 
-of a beam, and discuss a topical application, in which a beam narrow in momentum space 
-is used to create Bose polarons. Such a beam can give an access to the self-energy and the effective 
-mass of the polaron, as well as to the corresponding critical momentum.
+We propose to engineer beams of cold atoms by selecting particles from a trapped gas.
+The gas is spatially connected to an external potential whose transmission coefficient allows only
+atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the required 
+beam profile and output is a filter potential.
+A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
+Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons;
+it allows one to study the self-energy and the effective mass of polarons, as well as the corresponding 
+Landau criterion.
 \end{abstract}
@@
 {\it Introduction. --}   
-A scattering off a target is
-universally used to study properties of particles and materials {\color{blue} more?}.  
-In this Letter we discuss how to create cold-atom beams
-of given momentum profiles, which is a prerequisite for scattering experiments
-with quantum gases. 
-Such beams can be useful for measuring parameters that define
-physics of cold-atoms systems. It can be few-body parameters such as
-the scattering length and the three-body parameter~\cite{braaten2006, bloch2008}.
-The parameters of interest can also incorporate many-body effects, such as the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
+In this Letter we discuss how to create cold-atom streams whose momentum profile
+is adjusted to the needs of the matter in hand.   
+Such streams are a prerequisite for scattering experiments with quantum gases, in particular, 
+they can be useful for measuring parameters that define
+physics of cold-atoms systems. It can be parameters related to few-body correlations such as
+the scattering length and the three-body parameter~\cite{braaten2006, bloch2008}, or
+many-body effects, such as the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
 
-Our proposal for engineering beams of cold atoms is summarized in Fig.~\ref{fig:Figure1}.
-For simplicity, we illustrate the method using a one-dimensional geometry 
+Our proposal is summarized in Fig.~\ref{fig:Figure1}.
+Superficially, it reminds a quantum switch device
+(`transistor')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' (reservoir) 
+is determined by the `gate' (link potential).
+However, our proposal allows one to design the momentum profile 
+of the flux in addition to completely switching off the transmission.
+For simplicity, we illustrate our idea using a one-dimensional geometry (1D) 
 (a cylindrically symmetric three-dimensional case is identical to that
@@
 to a collective resonant transport~\cite{Schlagheck2005}.},
-so that their scattering properties are found by solving the one-body Schr{\"o}dinger equation
+so that their scattering properties may be calculated using the one-body Schr{\"o}dinger equation:
 \begin{equation}
@@
 The link potential $V_0(x)$ has the transmission coefficient, $T_0(k)$, that allows only particles with desired momenta to 
-tunnel through the barrier into the `flux region'. 
-The momentum profile of particles in the `flux region' can be measure using a single-atom momentum resolution (e.g.,~\cite{jochim2018}),
-which allows one to confirm that the desired beam has been produced.
+tunnel through the barrier into the `flux region'. By changing $V_0(x)$ one tunes $T_0(x)$ to the needs of the experiment.
+Note that the momentum profile of particles in the `flux region' can be measured using 
+a single-atom momentum resolution (e.g.,~\cite{jochim2018}),
+which allows one to confirm that the requested beam has been produced.
 
 In this Letter,  we discuss how to 
-find $V_0(x)$ for a given function $T_0(k)$, and use the Bose polaron problem
-to illustrate a possible application of cold-atom beams. It is worthwhile noting that 
-our scheme is inspired by quantum switch devices 
-(`transistors')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' is affected by changing the properties of the `gate'.
-The benefit of the present set-up is that in addition to completely switching off the transmission, it allows one to design the momentum profile 
-of the flux.
+calculate $V_0(x)$ for a given function $T_0(k)$. Furthermore, we briefly discuss the one-dimensional 
+Bose polaron problem as a possible application of cold-atom beams.
 
@@
 The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, 
-the distribution is non-zero only in the neighborhood of a chosen momentum.
+the distribution is non-zero only in the neighborhood of a chosen momentum. The link potential is a narrow-band filter.
   }
@@
 The weights are chosen to emphasize regions of $k$ during the minimization.
-For instance, when trying to create a potential barrow band-pass filter that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$ (see Fig.~\ref{fig:Figure1} and Fig.~\ref{fig:method_illustration}, top), then it would be appropriate to increase the weights in the region of $k_0$.
-The convergence of our approach was somewhat sensitive to the choice of $w_k$.
+For instance, for a narrow band-pass filter that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$ (see Figs.~\ref{fig:Figure1} and~\ref{fig:method_illustration}), it is appropriate to increase the weights in the region of $k_0$.
+The convergence of our approach is somewhat sensitive to the choice of $w_k$.
 
-We developed a strategy for choosing the weights that takes into account the following considerations: 1) the transport coefficient is constrained to be zero for $k=0$ so the weight can be smaller for small $k$, 2) the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to supress flux at large $k$, and 3) to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
-Follwing these principles, we arrive at the following formula for the weight function:
+We developed a strategy for choosing the weights that takes into account the following considerations: {\it i)} the transport coefficient is zero for $k=0$ 
+(there can be no transmission for $k=0$ and $V\neq 0$ in 1D) so the weight can be smaller for small $k$, {\it ii)} the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to supress flux at large $k$, and {\it iii)} to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
+Following these principles, we arrive at the following formula for the weight function:
 \begin{equation}\label{eq:weight-of-k}
@@
 \end{equation}
-where $w_{\mathrm{bg}}(k)$ is chosen to account for considerations 1 and 2 above, and the term proportional to the positive constant $r$ accounts for consideration 3.
-For $w_{\mathrm{bg}}(k)$, we use the {\color{blue} transport profile resulting from a morse potential WITH WHAT PARAMS?}:
+where $w_{\mathrm{bg}}(k)$ is chosen to account for considerations {\it i)} and {\it ii)} above, and the term proportional to the positive constant $r$ accounts for consideration {\it iii)}.
+{\color{blue} The form  of $w_{\mathrm{bg}}(k)$ can be inferred from typical transmission coefficients.
+We use the one for
+the Morse potential $\hbar^2k_0^2/[2m \cosh^2(k_0x/\sqrt{2})]$ (cf.~\cite{landau1977}):
 \begin{equation}\label{eq:weight-of-k}
-  w_{\mathrm{bg}}(k) = \left[\frac{\sinh^2(\sqrt{2}\pi k)}{\sinh^2(\sqrt{2}\pi k) + \cosh^2(\sqrt{7}\pi/2)}\right]^{1/2}.
+  w_{\mathrm{bg}}(k) = \left[\frac{\sinh^2(\sqrt{2}\pi k/k_0)}{\sinh^2(\sqrt{2}\pi k/k_0) + \cosh^2(\sqrt{7}\pi/2)}\right]^{1/2},
 \end{equation}
+where the parameter $k_0$ determines a typical energy scale (for an example see our illustration below).}
 The parameter $r$ was chosen by trial and error for each target profile $T_0(k)$.
@@
 While minimizing Eq.~\eqref{eq:cost1}, we enforce the parameter constraints listed in Table \ref{tab:constraints}.
-In addition to these constraints on the parameters, we enforce an constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
+In addition to these constraints on the parameters, we enforce a constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
 To accomplish this, we minimize the boundary-augmented cost function
@@
 The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
-The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in the suppl.~material.
+The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Ref.~\footnote{See the Supplementary Material for the full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ and
+for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem.}.
 
@@
    \includegraphics[width=1\linewidth]{figures/plot_transport_profiles_with_inset.pdf}
- \caption[Narrow band-pass filter link potential]{Two-Gaussian solution for the $k=1$ narrow band-pass filter transport profile.
-The main figure shows the target profile (dot-dashed, red) used during optimization and the actual transport profile resulting from the optimization procedure (solid, blue).
+ \caption[Narrow band-pass filter link potential]{A two-Gaussian solution for the narrow band-pass filter transport profile.
+The main figure shows the target profile (dot-dashed, red) used during optimization (see Eq.~(\ref{eq:Ttarget})) and the actual transport profile resulting from the optimization procedure (solid, blue).
 The inset figure shows the optimal link potential $V(x, \bm{\theta^*})$.
-{\color{blue} bold font, $k>2$?}}
+{\color{red} bold font in the inset}}
  \label{fig:method_illustration}
@@
 
-{\it Narrow band-pass filter transport profile. --}
-To illustrate the method described above we optimize for a narrow band-pass filter transport profile sharply-peaked near $k=k_0$.
-For simplicity, we adopt the units in which $k_0=\hbar=2m=1$.
-For our target transport profile, we use a Lorentz profile
+{\it Narrow band-pass filter (NBP) transport profile. --}
+To illustrate the method described above we optimize for a NBP filter transport profile sharply-peaked near $k=k_0$. 
+{\color{blue} For our target transport profile, we use a Lorentz profile~(see Figure~\ref{fig:method_illustration})
 \begin{equation}\label{eq:Ttarget}
@@
 \end{equation}
-with $k_0=1$ and $b=0.03$ (see Figure~\ref{fig:method_illustration}).
+where $k_0$ determines the peak position and $b$ determines the width. 
+For simplicity, in this subsection we adopt the units $k_0=\hbar=2m=1$, which scales $k_0$
+out of the problem. The value of $b$ must be much smaller than $k_0$ 
+to have a well-defined peak, but not too small to have realistic time scales
+for a one-body tunnelling. We set $b=0.03 k_0$, which for a reasonable assumption 
+$\hbar^2k_0^2/(2m)=k_B\times \mu$K, where $k_B$ is the Boltzmann constant leads to 
+the time scale associated with the resonance width $\frac{2m}{\hbar b^2}\sim 10$ms.}
+
  For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.2$, $\sigma_{\mathrm{max}}=3$, $A_{\mathrm{min}}=5$, and $A_{\mathrm{max}}=30$.
@@
 We anticipate that this potential might be the easiest to realize in the laboratory.
-In addition, it is straithforward to visualize the transfer using quasi-discrete levels in the link potential.
-Note also that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of link potential is still required, because the cost function for the optimization has many local minima corresponding to the many ways that a resonance state can be placed near the scattering energy $k^2$.
+Moreover, it allows us to give a physical interpretation in terms of quasi-discrete energy levels supported by the link.
+It is worthwhile noting, that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of possible link potentials is still required, because the cost function for the optimization has many local minima corresponding to the many ways to produce a resonance state near the scattering energy~$k_0^2$ {\color{red} Why do we need the sentence?}.
 
-Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the band-pass filter optimization.
+Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the NBP filter optimization.
 The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
-This additional resonance need not be a problem if the scattering atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{In general, one needs to include the momentum distribution of the reservoir, $n(k)$,
-in the cost function. To this end, one might multiply in Eq.~(\ref{eq:cost1}) $T_{\bm{\theta}}(k)$ by $n(k)$; the rest of the discussion is untouched.
-The function $n(k)$ can be determined by the Bose-Einstein or Fermi-Dirac distributions. The illustration in the text practically corresponds to a Fermi gas 
-at zero temperature, i.e., $n(k<k_F)=1$ and zero otherwise, with the Fermi energy that satisfies $1\ll k_F^2 \ll A_\mathrm{min}$}.
- {\color{red}  Note that the two-Gaussian solution struggles to reproduce the width of the Lorentz target profile (see the inset in Fig.~\ref{fig:method_illustration}), and the second resonance might be used instead in practical applications.
-Indeed, the width of the first resonance is quite narrow,
-which requires long experimental runtime; for example, a reasonable assumption $\hbar^2k_0^2/(2m)=k_B\times 100$nK, where $k_B$ is the Boltzmann constant leads to 
-a single-particle time scale for tunnelling $\tau\sim 0.2 s$. In case this time scale is not experimentally realistic, the second resonance 
-can be used.
-Though we have not demonstrated that the solution shown in Fig.~\ref{fig:method_illustration} corresponds to a global minimum, this failure to reproduce the width may result from insufficient freedom in the family of constrained two-Gaussian potentials.
-}
+This additional resonance need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{In general, one needs to include the distribution of particles over the energy in the reservoir, $n(k)$,
+in the cost function. To this end, one might simply multiply in Eq.~(\ref{eq:cost1}) $T_{\bm{\theta}}(k)$ by $n(k)$, leaving the rest as is.
+The function $n(k)$ is determined by the Bose-Einstein or Fermi-Dirac distributions, temperature and the shape of the trap. Current Eq.~(\ref{eq:cost1}) assumes a Fermi gas 
+at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
 
@@
 Both the peak positions, $k_0$, and the peak heights, $T_0$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
-When optimizing with 3- or 4-Gaussian potentials, we found that solutions tended to be more sensitive to the potential parameters.
+
+{\color{blue} Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
+We discovered empirically that these more complicated transport profiles require more than two Gaussian potentials.
+Link potentials made of 3- or 4-Gaussian potentials tend to be more sensitive to random variations of potential parameters.
 If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
-
-Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles for various experimental scenarios.
-We find that these more complicated transport profiles require more than two Gaussian potentials and that the solutions using the procedure we describe are highly-sensitive to the potential parameters.
-We leave the thorough exploration of these ideas to future work.
-In the next section, we discuss a possible experimental application of the narrow band-pass filter solution.
+We leave the thorough exploration of these ideas to future work. In the next section, we discuss a possible experimental application of the NBP filter. }
 
@@
  \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.
-Shown are the distributions of the peak position $k_0$ (main graph) and peak height $T_0$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential shown in Fig.~\ref{fig:method_illustration}.
-}
+Shown are the distributions of the peak position $k_0$ (main graph) and peak height $T_0$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.
+{\color{red} bold font in the inset.
+Should we use $T_{max}$ and $k_{max}$ because $k_0$ and $T_0$ have been already introduced?} }
  \label{fig:sensitivity}
@@
 
-{\it Application. --} If one places a Bose or Fermi gas in the `flux region' (see Fig.~\ref{fig:Figure1}) then the resulting 
-system models an impurity-gas problem provided that the flux is dilute (no interactions for particles that make the beam).
-Quantum simulations of problems with mobile impurities is an important domain of cold-atoms 
-experiments~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017},
-and our proposal allows for investigating the dynamics of impurities that initially have 
-a known momentum profile. We illustrate this statement below by considering a flux through a degenerate 
-one-dimensional Bose gas.
+{\it Application. --} A Bose or Fermi gas (see Fig.~\ref{fig:Figure1}) can be placed in the `flux region'
+to study quantum environments with mobile neutral impurities -- an important research venue promoted by cold-atom 
+simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017}.
+With our proposal it is possible to investigate dynamics of impurities that initially have 
+a known momentum profile, thus allowing for a direct measurement of the effective mass and 
+the critical momentum. A detailed discussion of these concepts is beyond the scope 
+of the Letter. Still, we find it useful to briefly explain them in connection to our proposal. 
+To this end, we consider a degenerate one-dimensional Bose gas with an impurity of momentum $P$.
+To model this system, we employ a non-linear Schr{\"o}dinger equation
+for a Bose gas with an impurity atom~[10]. This equation was solved analytically
+in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, 
+which allows us to work out all properties of the dressed particle in a simple manner; 
+note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018},
+see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
 
-We assume that the flux is non-zero only 
-in the neighborhood of a chosen value $k_0$ as in Fig.~\ref{fig:method_illustration}.
-Therefore, for simplicity, we assume that the impurity has momentum $k_0$.
-If $k_0$ is small then the propagation of the impurity can be described using the polaron quasiparticle 
--- an impurity dressed by low-energy excitations of the environment~\cite{landau1948}. 
-To model this quasiparticle, we use a non-linear Schr{\"o}dinger equation
-for a Bose gas with an impurity atom~\footnote{See the Supplementary Material for the solution to 
-the impurity-(Bose gas) problem}. The employed equation has been solved analytically
-in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, 
-which allows us to work out all properties of the polaron; 
-note that this (or similar) non-linear equation is used in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018}
-to extract some properties of impurities in a Bose gas,
-see also~\cite{kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies. 
-The lowest energy state of a system with a fixed value of the impurity momentum, $P$, in this model
-is a combination of two solitons. They make a dissipationless defect in the Bose gas, which we call the polaron. The corresponding energy 
+The lowest energy state of the non-linear Schr{\"o}dinger equation with a given $P$ is a combination of two solitons. 
+They make a dissipationless defect in the Bose gas, which accompanies the impurity. The corresponding energy 
 is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, 
-$\epsilon$ is the self-energy of the polaron, and $m_{\mathrm{eff}}$ is its effective mass. The polaron solution is steady only 
-for $P<P_c$, where $P_c$ defines the momentum above which the propagation flux produces grey solitons. 
-Note that quantum fluctuations will lead to some finite dissipation~\cite{astrakharchik2004,sykes2009,Cherny2012} even for $P<P_c$, however
-we do no consider this effect in the present study.
+$\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass. The solution is steady only 
+for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}). 
+Note that quantum fluctuations lead to a finite dissipation (cf.~\cite{astrakharchik2004,sykes2009,Cherny2012})
+even for $P<P_c$. We do not consider this effect as it does not change our qualitative presentation.
 
@@
 \centerline{\includegraphics[scale=0.3]{figure3.pdf}}
-\caption{Panel {\bf a)} shows schematically the energies of a free particle and
-a particle in a degenerate Bose gas. The possibility to create atom with a given momenta 
-will allow one to establish the effective mass of the polaron
-and the limits of applicability of the polaron model by measuring the energy difference, $\Delta(p)$, using the radio-frequency spectroscopy.
-Note that quasiparticle properties should be absent for high momenta $P>P_c$. For one spatial dimension, a typical momentum scale, $P_c$, 
-can be estimated  by considering the existence of steady solutions 
-of a relevant non-linear Schr{\"o}dinger equation; see the text for details. Panel {\bf b)} 
-shows the results for a heavy impurity of mass $M$; $c$ is the speed of sound in the gas
-and $g$ is the boson-impurity interaction strength.
+\caption{Panel {\bf a)} shows schematically the energies of a free and dressed particles. 
+The effective mass and the self-energy 
+can be obtained from the energy difference, $\Delta(p)$.
+Panel {\bf b)} shows $P_c$ for an impurity of mass $M\gg m$; 
+$c$ is the speed of sound in the gas and $g$ is the boson-impurity interaction strength.
   }
@@
 
-Ultracold beams can be used to measure properies of Bose polarons, in particular $\epsilon, m_{\mathrm{eff}}$ and $P_c$.
-For example, to measure the effective 
-mass one prepares a flux of particles in a hyperfine state that does not 
-interact with the Bose gas. Then the beam particles can be transferred into a hyperfine state that strongly interacts with the gas.
-This transfer is possible only if one deposits enough energy to compensate for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
-Therefore, by looking at the radio-frequency responce (e.g., the transferred fraction) at different momenta, the self-energy and effective mass 
-of the polaron can be extracted. 
-This idea is similar to a recent experiment in a three-dimensional Fermi polaron~\cite{zaccanti2017}. However,
-in our case the initial momentum is known, and therefore not only the effective mass but also the limits of applicability 
-of the polaron model can be determined, in particular, the critical momentum above which there are no steady solutions.
-In Fig.~\ref{fig:Figure3}{\bf b)} we present this momentum for heavy impurities (for which our theory works best), relevant 
-for mixtures of cold atoms with large mass imbalance, e.g., Li-Yb~\cite{takahashi2018}.
+To measure $\epsilon, m_{\mathrm{eff}}$ and $P_c$, one shall use a NBP filter to create a flux of particles 
+with momenta close to $P$. The value of $b$ must be chosen such that the current is weak, i.e., 
+there is a negligible probability to find two flux particles at distances smaller than the healing 
+length of the Bose gas. Then the impurity-in-a-gas picture is applicable by construction. 
+For the sake of argument, we assume that initially the impurity is in a hyperfine state 
+that does not interact with the Bose gas. To transfer to a strongly interacting hyperfine state 
+one has to deposit enough energy to compensate for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
+Therefore, the radio-frequency responce (e.g., the transferred fraction) at different momenta directly measures 
+the self-energy and effective mass of the polaron;
+such a measurement would be similar to the one in a recent experiment with a three-dimensional Fermi polaron~\cite{zaccanti2017}, but 
+with a superior control over the impurity momentum. 
+Moreover, the overlap between the non-interacting and interacting states, i.e., the residue, can
+be measured, allowing one to test recent theoretical calculations~\cite{volosniev2017, pastukhov2017,grusdt2017,pastukhov2018}
+that, while qualitatively agreeing on $m_{\mathrm{eff}}$ and $\epsilon$, contradict each other on the residue.
+Since the momentum of the impurity is known, not only the effective parameters but also the limits of applicability 
+of the polaron model will be seen in the radio-frequency responce, in particular, $P_c$.
+In Fig.~\ref{fig:Figure3}{\bf b)} we present $P_c$ for impurities whose mass $M$ is much larger than $m$~\cite{hakim1997}.
 For weak interactions ($g\to 0$) the critical momentum is determined by the speed of sound, $c$, in accordance with the Landau criterion.
-For strong interactions ($g\to \infty$) the critical momentum goes to zero as $1/g$.  
-In this limit the critical momentum is determined by the time needed to exchange two strongly interacting particles.
+In the opposite limit, $g\to \infty$, the critical momentum goes to zero as $1/g$:   
+$P_c$ is limited by the timescale for a two-body exchange.
 
-{\it Summary. --}  We have shown how to create beams of particles to probe systems of cold atoms. 
-As an application of our proposal we have used the one-dimensional Bose polaron problem.
-We anticipate that the ideas discussed in this Letter can be used to study two-, three- and mixed-dimensional polaron systems {\color{blue} refrences}, temperature (energy) dependence of Efimov trimers~\cite{naidon2011, huang2015, wacker2018}, thermalization in systems with a hole in the momentum space (similar to that in a coordinate space {\color{blue} references}), etc {\color{blue} more details?}).
+{\it Summary. --}  We proposed to engineer streams of particles with desired momenta profiles
+using a filter potential connected to a reservoir; see Fig.~\ref{fig:Figure1}.
+A stream can be used to probe cold-atom systems. It can also be used for quantum simulations, as we illustrated 
+with a narrow band-pass filter and a one-dimensional Bose gas in the `flux' region. 
+Polarons in two-, three- and mixed-dimensional geometries can be created similarly. 
+{\color{red} Time-dependent driving?}
 
 \begin{acknowledgments}
-We thank Georg Bruun and Peter Schlagheck for referring to~\cite{zaccanti2017} and~\cite{Schlagheck2005}
-correspondingly, and Joachim Brand and Volodymyr Pastukhov for useful discussions.
+We thank Peter Schlagheck for referring to~\cite{Schlagheck2005},
+and Joachim Brand and Volodymyr Pastukhov for useful discussions.
 A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation and the Deutsche Forschungsgemeinschaft
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% \begin{figure}
-% \centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
-% \caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
-% assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
-% Note that the minimum of the density is at $-z_0$.
+ \begin{figure}
+ \centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
+ \caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
+ assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
+ Note that the minimum of the density is at $-z_0$.
 The shaded area is a combination of the two solutions with the singularity at $z=0$.
 Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
-% \label{fig:Fig1}
-% \end{figure}
-% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \label{fig:Fig1}
+ \end{figure}
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2019-03-19 Paper/version2/paper.tex
polished abstract

@@
 \begin{abstract}
-We propose to engineer beams of cold atoms by selecting particles from a trapped gas.
-The gas is spatially connected to an external potential whose transmission coefficient allows only
-atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the required 
-beam profile and output is a filter potential.
+We describe a procedure for engineering beams of cold atoms by selectively filtering particles from a trapped gas based on momenta.
+A gas is spatially connected to an external potential whose transmission coefficient only allows atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the desired
+transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired profile.
 A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
-Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons;
-it allows one to study the self-energy and the effective mass of polarons, as well as the corresponding 
-Landau criterion.
+Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons, allowing one to study the self-energy and the effective mass of polarons, as well as the corresponding Landau criterion.
 \end{abstract}

### 2019-03-19 Paper/version2/paper.tex
polished up to polaron section. still need to update figs 2 and 3.

@@
 A gas is spatially connected to an external potential whose transmission coefficient only allows atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the desired
-transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired profile.
-A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
+transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired beam profile.
+We illustrate this procedure by finding a filter potential that approximately produces a narrow band-pass (NBP) filter transport profile.
 Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons, allowing one to study the self-energy and the effective mass of polarons, as well as the corresponding Landau criterion.
@@
 {\it Introduction. --}   
-In this Letter we discuss how to create cold-atom streams whose momentum profile
-is adjusted to the needs of the matter in hand.   
-Such streams are a prerequisite for scattering experiments with quantum gases, in particular, 
-they can be useful for measuring parameters that define
-physics of cold-atoms systems. It can be parameters related to few-body correlations such as
-the scattering length and the three-body parameter~\cite{braaten2006, bloch2008}, or
-many-body effects, such as the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
+In this Letter we discuss a procedure for creating cold-atom streams with momentum transport profiles that can be selected for the matter at hand.
+Such streams would enable novel scattering experiments with quantum gases. In particular, 
+they could be used to measure parameters that define
+physics of cold-atoms systems such as such few-body parameters like the
+scattering length or three-body parameter~\cite{braaten2006, bloch2008} or
+many-body effects like the self-energy or the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
 
-Our proposal is summarized in Fig.~\ref{fig:Figure1}.
-Superficially, it reminds a quantum switch device
-(`transistor')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' (reservoir) 
-is determined by the `gate' (link potential).
-However, our proposal allows one to design the momentum profile 
-of the flux in addition to completely switching off the transmission.
-For simplicity, we illustrate our idea using a one-dimensional geometry (1D) 
-(a cylindrically symmetric three-dimensional case is identical to that
-within our formalism). The particles in a reservoir are non-interacting~\footnote{
-Strong interactions can lead to the transmission behavior that is not captured by the one-body Schr{\"o}dinger equation, e.g.,
-to a collective resonant transport~\cite{Schlagheck2005}.},
-so that their scattering properties may be calculated using the one-body Schr{\"o}dinger equation:
+Figure ~\ref{fig:Figure1} summarizes our proposal.
+Analogous to a quantum switch device (`transistor')~\cite{zoller2004, marchukov2016}, the flux of particles from the `source' (reservoir) is determined by the `gate' (link potential).
+However, rather than simply controlling the overall transmission rate, our proposal allows one to design the momentum profile of the outgoing flux.
+For simplicity, we illustrate our idea using a one-dimensional geometry (1D) (though our formalism also applies directly to a cylindrically symmetric three-dimensional geometry).
+We assume that the particles in the reservoir are non-interacting~\footnote{Strong interactions can lead to the transmission behavior that is not captured by the one-body Schr{\"o}dinger equation, e.g.,to a collective resonant transport~\cite{Schlagheck2005}.}, so that their scattering properties may be calculated using the one-body Schr{\"o}dinger equation:
 \begin{equation}
@@
 where $m$ is the mass of a particle from the reservoir, $\frac{\hbar^2k^2}{2m}$ is its energy.
-The link potential $V_0(x)$ has the transmission coefficient, $T_0(k)$, that allows only particles with desired momenta to 
-tunnel through the barrier into the `flux region'. By changing $V_0(x)$ one tunes $T_0(x)$ to the needs of the experiment.
-Note that the momentum profile of particles in the `flux region' can be measured using 
-a single-atom momentum resolution (e.g.,~\cite{jochim2018}),
-which allows one to confirm that the requested beam has been produced.
+The link potential $V_0(x)$ produces the transmission coefficient, $T_0(k)$.
+By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the `flux region' as required by the experimental application.
+Note that the momentum profile of the outgoing beam can be measured using a single-atom momentum resolution (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
 
-In this Letter,  we discuss how to 
-calculate $V_0(x)$ for a given function $T_0(k)$. Furthermore, we briefly discuss the one-dimensional 
-Bose polaron problem as a possible application of cold-atom beams.
+In this Letter,  we discuss how to determine an appropriate $V_0(x)$ for a given desired flux profile $T_0(k)$.
+Furthermore, we briefly discuss the 1D Bose polaron problem as a possible application of cold-atom beams.
 
@@
 \centerline{\includegraphics[scale=0.3]{figure1new.pdf}}
-\caption{An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external potential. 
-The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, 
-the distribution is non-zero only in the neighborhood of a chosen momentum. The link potential is a narrow-band filter.
+\caption{ \textcolor{red}{The link potential looks a bit unnatural to me.
+The odd part is the kinks where the middle potential joins its neighbors.
+Can we make this smooth?
+Summing three gaussians and adding an intercept should work, yes?} An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external link potential.
+The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, the distribution is non-zero only in the neighborhood of a chosen momentum.
+The link potential is a narrow-band filter.
 }
@@
 {\it Procedure for Finding a Link Potential. --} 
-We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the $k$-integrated squared error between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
+We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the $k$-integrated squared error between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ produced by a sample potential $V(x, \bm{\theta})$.
 Concretely, we minimize the cost
@@
 where the $k$-integral has been approximated (up to a constant factor) by a sum over a discrete set of momentum values, and $w_k$ is the weight given to momentum $k$.
-The weights are chosen to emphasize regions of $k$ during the minimization.
+The weights are chosen to emphasize or de-emphasize special regions of $k$ during the minimization.
 For instance, for a narrow band-pass filter that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$ (see Figs.~\ref{fig:Figure1} and~\ref{fig:method_illustration}), it is appropriate to increase the weights in the region of $k_0$.
@@
 We developed a strategy for choosing the weights that takes into account the following considerations: {\it i)} the transport coefficient is zero for $k=0$ 
-(there can be no transmission for $k=0$ and $V\neq 0$ in 1D) so the weight can be smaller for small $k$, {\it ii)} the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to supress flux at large $k$, and {\it iii)} to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
+(there can be no transmission for $k=0$ and $V\neq 0$ in 1D), so the weight can be smaller for small $k$, {\it ii)} the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to suppress flux at large $k$, and {\it iii)} to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
 Following these principles, we arrive at the following formula for the weight function:
@@
 where $w_{\mathrm{bg}}(k)$ is chosen to account for considerations {\it i)} and {\it ii)} above, and the term proportional to the positive constant $r$ accounts for consideration {\it iii)}.
-{\color{blue} The form  of $w_{\mathrm{bg}}(k)$ can be inferred from typical transmission coefficients.
-We use the one for
+The form  of $w_{\mathrm{bg}}(k)$ can be inferred from typical transmission coefficients.
+For convenience, we use the analytic form for the transmission coefficient produced by
 the Morse potential $\hbar^2k_0^2/[2m \cosh^2(k_0x/\sqrt{2})]$ (cf.~\cite{landau1977}):
@@
 \end{equation}
-where the parameter $k_0$ determines a typical energy scale (for an example see our illustration below).}
+where the parameter $k_0$ determines a typical energy scale (for an example see our illustration below).
 The parameter $r$ was chosen by trial and error for each target profile $T_0(k)$.
@@
 While minimizing Eq.~\eqref{eq:cost1}, we enforce the parameter constraints listed in Table \ref{tab:constraints}.
-In addition to these constraints on the parameters, we enforce a constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
+In addition to these constraints on the parameters, we enforce a constraint requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
 To accomplish this, we minimize the boundary-augmented cost function
 \begin{equation}\label{eq:cost2}
-  J_{\bm{\theta}}^{\mathrm{aug}} = J_{\bm{\theta}} + \alpha \sum_i^N\int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2,
+  J_{\bm{\theta}}^{\mathrm{aug}} = J_{\bm{\theta}} + \alpha \sum_{i=1}^N\int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2,
 \end{equation}
-where $\alpha$ is a tuning parameter chosen to make the added term of a similar order to $J_{\mathbf{\theta}}$ in the scenario that the potential extends outside the support region.
-Beyond this, we find that results are not very sensitive to the choice of $\alpha$ probably due to the very short tails of the Gaussian potentials.
+where $\alpha$ is a tuning parameter chosen empirically to aid in convergence.
+We find that results are not very sensitive to the choice of $\alpha$ probably due to the very short tails of the Gaussian potentials.
 The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
@@
 
-For a choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating the Schr{\"o}dinger equation~(\ref{eq:schr}) across the region of the potential and calculating the ratio of the transmitted to the incident flux.
+For a particular choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating the Schr{\"o}dinger equation~(\ref{eq:schr}) across the region of the potential and calculating the ratio of the transmitted to the incident flux.
 In order to do this efficiently, we discretize the second derivative in Eq.~(\ref{eq:schr}), which transforms Eq.~(\ref{eq:schr}) into
@@
 To illustrate the method described above we optimize for a NBP filter transport profile sharply-peaked near $k=k_0$. 
-{\color{blue} For our target transport profile, we use a Lorentz profile~(see Figure~\ref{fig:method_illustration})
+For our target transport profile, we use a Lorentz profile~(see Figure~\ref{fig:method_illustration})
 \begin{equation}\label{eq:Ttarget}
@@
 to have a well-defined peak, but not too small to have realistic time scales
-for a one-body tunnelling. We set $b=0.03 k_0$, which for a reasonable assumption 
+for a one-body tunneling. We set $b=0.03 k_0$, which for a reasonable assumption 
 $\hbar^2k_0^2/(2m)=k_B\times \mu$K, where $k_B$ is the Boltzmann constant leads to 
-the time scale associated with the resonance width $\frac{2m}{\hbar b^2}\sim 10$ms.}
+the time scale associated with the resonance width $\frac{2m}{\hbar b^2}\sim 10$ms.
 
@@
 Moreover, it allows us to give a physical interpretation in terms of quasi-discrete energy levels supported by the link.
-It is worthwhile noting, that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of possible link potentials is still required, because the cost function for the optimization has many local minima corresponding to the many ways to produce a resonance state near the scattering energy~$k_0^2$ {\color{red} Why do we need the sentence?}.
+Even though we work here with a very simple example with only three unknown parameters, a method for globally searching the space of possible link potentials is still required, because the cost function for the optimization has many local minima corresponding to the many ways to produce a resonance state near the scattering energy~$k_0^2$.
+Moreover this global search technique extends to more complicated transport profiles which necessitate more complicated families of link potentials.
 
@@
 It may be experimentally problematic if the transport profile shown in Fig.~\ref{fig:method_illustration} were highly sensitive to the potential parameters.
-Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired potential.
+Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired transport profile.
 To test this sensitivity, we generate 200 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
 The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Fig.~\ref{fig:sensitivity}.
-Both the peak positions, $k_0$, and the peak heights, $T_0$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
+Both the peak positions, $k_{\mathrm{max}}$, and the peak heights, $T_{\mathrm{max}}$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
 
-{\color{blue} Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
+Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
 We discovered empirically that these more complicated transport profiles require more than two Gaussian potentials.
-Link potentials made of 3- or 4-Gaussian potentials tend to be more sensitive to random variations of potential parameters.
+In our explorations, we found that link potentials made of 3- or 4-Gaussian potentials tended to be more sensitive to random variations of potential parameters.
 If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
-We leave the thorough exploration of these ideas to future work. In the next section, we discuss a possible experimental application of the NBP filter. }
+We leave the thorough exploration of these ideas to future work.
+In the next section, we discuss a possible experimental application of the NBP filter.
 
@@
  \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.
-Shown are the distributions of the peak position $k_0$ (main graph) and peak height $T_0$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.
-{\color{red} bold font in the inset.
-Should we use $T_{max}$ and $k_{max}$ because $k_0$ and $T_0$ have been already introduced?} }
+Shown are the distributions of the peak position $k_{\mathrm{max}}$ (main graph) and peak height $T_{\mathrm{max}}$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.}
  \label{fig:sensitivity}

### 2019-03-20 Paper/version2/paper.tex
Light polish on application section

@@
 The link potential $V_0(x)$ produces the transmission coefficient, $T_0(k)$.
-By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the `flux region' as required by the experimental application.
+By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the flux region as required by the experimental application.
 Note that the momentum profile of the outgoing beam can be measured using a single-atom momentum resolution (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
@@
 Summing three gaussians and adding an intercept should work, yes?} An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external link potential.
-The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, the distribution is non-zero only in the neighborhood of a chosen momentum.
+The potential filters out the desired momenta, and the particles in the flux region have a known momentum distribution -- here, the distribution is non-zero only in the neighborhood of a chosen momentum.
 The link potential is a narrow-band filter.
@@
 
-{\it Application. --} A Bose or Fermi gas (see Fig.~\ref{fig:Figure1}) can be placed in the `flux region'
-to study quantum environments with mobile neutral impurities -- an important research venue promoted by cold-atom 
-simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017}.
-With our proposal it is possible to investigate dynamics of impurities that initially have 
-a known momentum profile, thus allowing for a direct measurement of the effective mass and 
-the critical momentum. A detailed discussion of these concepts is beyond the scope 
-of the Letter. Still, we find it useful to briefly explain them in connection to our proposal. 
+{\it Application.
+--} A Bose or Fermi gas can be placed in the flux region  (see Fig.~\ref{fig:Figure1}) to study quantum environments with neutral, mobile impurities -- an important research venue promoted by cold-atom simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017}.
+With our proposal it is possible to investigate dynamics of impurities that initially have a known momentum profile, thus allowing for a direct measurement of the effective mass and the critical momentum.
+A detailed discussion of these concepts is beyond the scope of the Letter.
+Still, we find it useful to briefly explain them in connection to our proposal.
 To this end, we consider a degenerate one-dimensional Bose gas with an impurity of momentum $P$.
-To model this system, we employ a non-linear Schr{\"o}dinger equation
-for a Bose gas with an impurity atom~[10]. This equation was solved analytically
-in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, 
-which allows us to work out all properties of the dressed particle in a simple manner; 
-note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018},
-see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
+To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom~[10].
+This equation was solved analytically in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, which allows us to work out all properties of the dressed particle in a simple manner; note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018}, see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
 
 The lowest energy state of the non-linear Schr{\"o}dinger equation with a given $P$ is a combination of two solitons.
-They make a dissipationless defect in the Bose gas, which accompanies the impurity. The corresponding energy 
-is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, 
-$\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass. The solution is steady only 
-for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}). 
-Note that quantum fluctuations lead to a finite dissipation (cf.~\cite{astrakharchik2004,sykes2009,Cherny2012})
-even for $P<P_c$. We do not consider this effect as it does not change our qualitative presentation.
+They make a dissipationless defect in the Bose gas, which accompanies the impurity.
+The corresponding energy is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, $\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass.
+The solution is steady only for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}).
+Note that quantum fluctuations lead to a finite dissipation (cf.~\cite{astrakharchik2004,sykes2009,Cherny2012}) even for $P<P_c$.
+We do not consider this effect as it does not change our qualitative presentation.
 
@@
 
-To measure $\epsilon, m_{\mathrm{eff}}$ and $P_c$, one shall use a NBP filter to create a flux of particles 
-with momenta close to $P$. The value of $b$ must be chosen such that the current is weak, i.e., 
-there is a negligible probability to find two flux particles at distances smaller than the healing 
-length of the Bose gas. Then the impurity-in-a-gas picture is applicable by construction. 
-For the sake of argument, we assume that initially the impurity is in a hyperfine state 
+To measure $\epsilon, m_{\mathrm{eff}}$ and $P_c$, one can use a narrow band-pass filter as shown in Fig.~\ref{fig:method_illustration} to create a flux of particles with momenta close to $P$.
+The value of $b$ must be chosen such that the current is weak, i.e., there is a negligible probability to find two flux particles at distances smaller than the healing
+length of the Bose gas.
+\textcolor{red}{It might be good to state here how this be accomplished using the above framework.
+For example, using a target profile with very narrow width.} Then the impurity-in-a-gas picture is applicable by construction.
+For simplicity, we assume that initially the impurity is in a hyperfine state 
 that does not interact with the Bose gas. To transfer to a strongly interacting hyperfine state 
@@
 Therefore, the radio-frequency responce (e.g., the transferred fraction) at different momenta directly measures 
-the self-energy and effective mass of the polaron;
-such a measurement would be similar to the one in a recent experiment with a three-dimensional Fermi polaron~\cite{zaccanti2017}, but 
+the self-energy and effective mass of the polaron.
+
+A measurement such as this would be similar to the measurement in a recent experiment with a three-dimensional Fermi polaron~\cite{zaccanti2017} but 
 with a superior control over the impurity momentum. 
@@
 
-{\it Summary. --}  We proposed to engineer streams of particles with desired momenta profiles
-using a filter potential connected to a reservoir; see Fig.~\ref{fig:Figure1}.
-A stream can be used to probe cold-atom systems. It can also be used for quantum simulations, as we illustrated 
-with a narrow band-pass filter and a one-dimensional Bose gas in the `flux' region. 
-Polarons in two-, three- and mixed-dimensional geometries can be created similarly. 
+{\it Summary.
+--}  We outline a proceeder for engineering beams of particles with desired momentum profiles using a filter potential connected to a reservoir (see Fig.~\ref{fig:Figure1}).
+Such a beam can be used to probe cold-atom systems.
+It can also be used for quantum simulations, as we illustrated with a narrow band-pass filter and a one-dimensional Bose gas in the flux region.
+Polarons in two-, three- and mixed-dimensional geometries can similarly be created.
 {\color{red} Time-dependent driving?}

### 2019-03-27 Paper/version2/SM.tex
Arxiv submission

--- 2019-03-19 Paper/version2/paper.tex
@@
-\documentclass[twocolumn,amsmath,amssymb,showpacs,prl,superscriptaddress,aps]{revtex4-1}
+\documentclass[onecolumn,amsmath,amssymb,showpacs,prl,superscriptaddress,aps]{revtex4-1}
 
@@
 
-\title{Engineering momentum profiles of cold-atom {\color{blue} streams}}
+\title{Supplementary Material for ``Engineering momentum profiles of cold-atom beams"}
 
@@
 
-\begin{abstract}
-We describe a procedure for engineering beams of cold atoms by selectively filtering particles from a trapped gas based on momenta.
-A gas is spatially connected to an external potential whose transmission coefficient only allows atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the desired
-transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired profile.
-A narrow band-pass (NBP) filter transport profile is used as a clear-cut example. 
-Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons, allowing one to study the self-energy and the effective mass of polarons, as well as the corresponding Landau criterion.
-\end{abstract}
-
 \maketitle
 
-{\it Introduction. --}   
-In this Letter we discuss how to create cold-atom streams whose momentum profile
-is adjusted to the needs of the matter in hand.   
-Such streams are a prerequisite for scattering experiments with quantum gases, in particular, 
-they can be useful for measuring parameters that define
-physics of cold-atoms systems. It can be parameters related to few-body correlations such as
-the scattering length and the three-body parameter~\cite{braaten2006, bloch2008}, or
-many-body effects, such as the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
-
-Our proposal is summarized in Fig.~\ref{fig:Figure1}.
-Superficially, it reminds a quantum switch device
-(`transistor')~\cite{zoller2004, marchukov2016}, where the flux of particles from the `source' (reservoir) 
-is determined by the `gate' (link potential).
-However, our proposal allows one to design the momentum profile 
-of the flux in addition to completely switching off the transmission.
-For simplicity, we illustrate our idea using a one-dimensional geometry (1D) 
-(a cylindrically symmetric three-dimensional case is identical to that
-within our formalism). The particles in a reservoir are non-interacting~\footnote{
-Strong interactions can lead to the transmission behavior that is not captured by the one-body Schr{\"o}dinger equation, e.g.,
-to a collective resonant transport~\cite{Schlagheck2005}.},
-so that their scattering properties may be calculated using the one-body Schr{\"o}dinger equation:
-\begin{equation}
--\frac{\hbar^2}{2m}\frac{\partial^2}{\partial x^2}\psi+V_0(x)\psi=\frac{\hbar^2k^2}{2m}\psi,
-\label{eq:schr}
-\end{equation}
-where $m$ is the mass of a particle from the reservoir, $\frac{\hbar^2k^2}{2m}$ is its energy.
-The link potential $V_0(x)$ has the transmission coefficient, $T_0(k)$, that allows only particles with desired momenta to 
-tunnel through the barrier into the `flux region'. By changing $V_0(x)$ one tunes $T_0(x)$ to the needs of the experiment.
-Note that the momentum profile of particles in the `flux region' can be measured using 
-a single-atom momentum resolution (e.g.,~\cite{jochim2018}),
-which allows one to confirm that the requested beam has been produced.
-
-In this Letter,  we discuss how to 
-calculate $V_0(x)$ for a given function $T_0(k)$. Furthermore, we briefly discuss the one-dimensional 
-Bose polaron problem as a possible application of cold-atom beams.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centerline{\includegraphics[scale=0.3]{figure1new.pdf}}
-\caption{An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external potential. 
-The potential filters out the desired momenta, and the particles in the `flux region' have a known momentum distribution -- here, 
-the distribution is non-zero only in the neighborhood of a chosen momentum. The link potential is a narrow-band filter.
-  }
-\label{fig:Figure1}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-{\it Procedure for Finding a Link Potential. --} 
-We find an appropriate link potential $V_0(x) \equiv V(x,\bm{\theta}^*)$ by performing a global search over a family of possible potentials $V(x,\bm{\theta})$ for the parameters $\bm{\theta}^*$ that reduce the $k$-integrated squared error between the desired transmission-momentum profile $T_0(k)$ and the actual profile $T_{\bm\theta}(k)$ determined by a sample potential $V(x, \bm{\theta})$.
-Concretely, we minimize the cost
-\begin{equation}\label{eq:cost1}
-  J_{\bm{\theta}} = \sum_kw_k\left|T_0(k) - T_{\bm{\theta}}(k)\right|^2,
-\end{equation}
-where the $k$-integral has been approximated (up to a constant factor) by a sum over a discrete set of momentum values, and $w_k$ is the weight given to momentum $k$.
-The weights are chosen to emphasize regions of $k$ during the minimization.
-For instance, for a narrow band-pass filter that forbids transmission for all $k$ except in the neighborhood of a chosen value $k_0$ (see Figs.~\ref{fig:Figure1} and~\ref{fig:method_illustration}), it is appropriate to increase the weights in the region of $k_0$.
-The convergence of our approach is somewhat sensitive to the choice of $w_k$.
-
-We developed a strategy for choosing the weights that takes into account the following considerations: {\it i)} the transport coefficient is zero for $k=0$ 
-(there can be no transmission for $k=0$ and $V\neq 0$ in 1D) so the weight can be smaller for small $k$, {\it ii)} the transport coefficient approaches 1 for large $k$ so higher weights are required in the large-$k$ region if one wishes to supress flux at large $k$, and {\it iii)} to reproduce narrow features in the target transport profile, it may be helpful to increase the weight in the $k$-region of these features.
-Following these principles, we arrive at the following formula for the weight function:
-\begin{equation}\label{eq:weight-of-k}
-  w(k;r) = w_{\mathrm{bg}}(k) + rT_0(k)
-\end{equation}
-where $w_{\mathrm{bg}}(k)$ is chosen to account for considerations {\it i)} and {\it ii)} above, and the term proportional to the positive constant $r$ accounts for consideration {\it iii)}.
-{\color{blue} The form  of $w_{\mathrm{bg}}(k)$ can be inferred from typical transmission coefficients.
-We use the one for
-the Morse potential $\hbar^2k_0^2/[2m \cosh^2(k_0x/\sqrt{2})]$ (cf.~\cite{landau1977}):
-\begin{equation}\label{eq:weight-of-k}
-  w_{\mathrm{bg}}(k) = \left[\frac{\sinh^2(\sqrt{2}\pi k/k_0)}{\sinh^2(\sqrt{2}\pi k/k_0) + \cosh^2(\sqrt{7}\pi/2)}\right]^{1/2},
-\end{equation}
-where the parameter $k_0$ determines a typical energy scale (for an example see our illustration below).}
-The parameter $r$ was chosen by trial and error for each target profile $T_0(k)$.
-
-With the goal of discovering experimentally viable solutions, we parameterize the family of link potentials $V(x, \bm{\theta})$, as a sum of $N$ Gaussians, each of the form
-\begin{equation}\label{eq:V-param}
-V_i(x; A_i, \mu_i, \sigma_i) = \frac{A_i}{\sqrt{2\pi\sigma_i^2}}\exp\left[{-\frac{(x-\mu_i)^2}{2\sigma_i^2}}\right];
-\end{equation}
-the parameter $\bm{\theta}$ denotes the parameter space $\{A_1, \mu_1, \sigma_1,...,A_N, \mu_N, \sigma_N\}$.
-While minimizing Eq.~\eqref{eq:cost1}, we enforce the parameter constraints listed in Table \ref{tab:constraints}.
-In addition to these constraints on the parameters, we enforce a constraint by requiring that the link potential should not extend beyond the region of potential support $x\in[-x_0,x_0]$.
-To accomplish this, we minimize the boundary-augmented cost function
-\begin{equation}\label{eq:cost2}
-  J_{\bm{\theta}}^{\mathrm{aug}} = J_{\bm{\theta}} + \alpha \sum_i^N\int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2,
-\end{equation}
-where $\alpha$ is a tuning parameter chosen to make the added term of a similar order to $J_{\mathbf{\theta}}$ in the scenario that the potential extends outside the support region.
-Beyond this, we find that results are not very sensitive to the choice of $\alpha$ probably due to the very short tails of the Gaussian potentials.
-The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
-The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Ref.~\footnote{See the Supplementary Material for the full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ and
-for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem.}.
-
-\begin{table}[t]
-  \renewcommand*{\arraystretch}{1.4}
-  \begin{tabular}{m{3cm}|m{5.5cm}}
-    Constraints & Experimental Rationale \\
-    \hline\hline
-    $\sum_{i=1}^{N}\mu_i = 0$ & The cost function has a continuous degeneracy associated with overall translations of the link potential. \\
-    \hline
-    $\sigma_{\mathrm{min}} \leq \sigma_j \leq \sigma_{\mathrm{max}} $ & Laser beam widths fall between a minimum and maximum value.\\
-    \hline
-    $A_{\mathrm{min}} \leq |A_j| \leq A_{\mathrm{max}}$ & Laser amplitudes fall between a minimum and maximum value.
-  \end{tabular}
-  \caption{The explicit constraints on the potential parameters and the rationale for each constraint.
-The values of $\sigma_{\mathrm{min}}$, $\sigma_{\mathrm{max}}$, $A_{\mathrm{min}}$, and $A_{\mathrm{max}}$ must be determined from the experimental context.}
-  \label{tab:constraints}
-\end{table}
-
-For a choice of $\bm{\theta}$ (and hence $V(x;\bm{\theta})$), we solve for $T_{\bm{\theta}}(k)$ by integrating the Schr{\"o}dinger equation~(\ref{eq:schr}) across the region of the potential and calculating the ratio of the transmitted to the incident flux.
-In order to do this efficiently, we discretize the second derivative in Eq.~(\ref{eq:schr}), which transforms Eq.~(\ref{eq:schr}) into
-a banded linear system of equations solvable in $O(M)$ time where $M$ is the number of $x$-steps.
-Using these techniques we are able to evaluate the transmission coefficient 3.7 thousand times per second on a 7th generation Intel Core i7 processor for a test involving 1,000 randomly generated two-Gaussian potentials and 100 different scattering momenta.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{figure}
-   \includegraphics[width=1\linewidth]{figures/plot_transport_profiles_with_inset.pdf}
- \caption[Narrow band-pass filter link potential]{A two-Gaussian solution for the narrow band-pass filter transport profile.
-The main figure shows the target profile (dot-dashed, red) used during optimization (see Eq.~(\ref{eq:Ttarget})) and the actual transport profile resulting from the optimization procedure (solid, blue).
-The inset figure shows the optimal link potential $V(x, \bm{\theta^*})$.
-{\color{red} bold font in the inset}}
- \label{fig:method_illustration}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{storn1997differential}.
-This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
-Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
-Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing for this particular optimization problem.
-
-{\it Narrow band-pass filter (NBP) transport profile. --}
-To illustrate the method described above we optimize for a NBP filter transport profile sharply-peaked near $k=k_0$. 
-{\color{blue} For our target transport profile, we use a Lorentz profile~(see Figure~\ref{fig:method_illustration})
-\begin{equation}\label{eq:Ttarget}
-  T(k; k_0,b) = \left[1 + \frac{(k-k_0)^2}{b^2}\right]^{-1}
-\end{equation}
-where $k_0$ determines the peak position and $b$ determines the width. 
-For simplicity, in this subsection we adopt the units $k_0=\hbar=2m=1$, which scales $k_0$
-out of the problem. The value of $b$ must be much smaller than $k_0$ 
-to have a well-defined peak, but not too small to have realistic time scales
-for a one-body tunnelling. We set $b=0.03 k_0$, which for a reasonable assumption 
-$\hbar^2k_0^2/(2m)=k_B\times \mu$K, where $k_B$ is the Boltzmann constant leads to 
-the time scale associated with the resonance width $\frac{2m}{\hbar b^2}\sim 10$ms.}
-
- For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.2$, $\sigma_{\mathrm{max}}=3$, $A_{\mathrm{min}}=5$, and $A_{\mathrm{max}}=30$.
-We further simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
-We anticipate that this potential might be the easiest to realize in the laboratory.
-Moreover, it allows us to give a physical interpretation in terms of quasi-discrete energy levels supported by the link.
-It is worthwhile noting, that even though we work here with a very simple example that has only three unknown parameters, a method for globally searching the space of possible link potentials is still required, because the cost function for the optimization has many local minima corresponding to the many ways to produce a resonance state near the scattering energy~$k_0^2$ {\color{red} Why do we need the sentence?}.
-
-Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the NBP filter optimization.
-The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
-This additional resonance need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{In general, one needs to include the distribution of particles over the energy in the reservoir, $n(k)$,
-in the cost function. To this end, one might simply multiply in Eq.~(\ref{eq:cost1}) $T_{\bm{\theta}}(k)$ by $n(k)$, leaving the rest as is.
-The function $n(k)$ is determined by the Bose-Einstein or Fermi-Dirac distributions, temperature and the shape of the trap. Current Eq.~(\ref{eq:cost1}) assumes a Fermi gas 
-at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
-
-It may be experimentally problematic if the transport profile shown in Fig.~\ref{fig:method_illustration} were highly sensitive to the potential parameters.
-Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired potential.
-To test this sensitivity, we generate 200 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
-The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Fig.~\ref{fig:sensitivity}.
-Both the peak positions, $k_0$, and the peak heights, $T_0$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
-
-{\color{blue} Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
-We discovered empirically that these more complicated transport profiles require more than two Gaussian potentials.
-Link potentials made of 3- or 4-Gaussian potentials tend to be more sensitive to random variations of potential parameters.
-If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
-We leave the thorough exploration of these ideas to future work. In the next section, we discuss a possible experimental application of the NBP filter. }
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
-\begin{figure}
-   \includegraphics[width=1\linewidth]{figures/plot_sensitivity.pdf}
- \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.
-Shown are the distributions of the peak position $k_0$ (main graph) and peak height $T_0$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.
-{\color{red} bold font in the inset.
-Should we use $T_{max}$ and $k_{max}$ because $k_0$ and $T_0$ have been already introduced?} }
- \label{fig:sensitivity}
-\end{figure}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-{\it Application. --} A Bose or Fermi gas (see Fig.~\ref{fig:Figure1}) can be placed in the `flux region'
-to study quantum environments with mobile neutral impurities -- an important research venue promoted by cold-atom 
-simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017}.
-With our proposal it is possible to investigate dynamics of impurities that initially have 
-a known momentum profile, thus allowing for a direct measurement of the effective mass and 
-the critical momentum. A detailed discussion of these concepts is beyond the scope 
-of the Letter. Still, we find it useful to briefly explain them in connection to our proposal. 
-To this end, we consider a degenerate one-dimensional Bose gas with an impurity of momentum $P$.
-To model this system, we employ a non-linear Schr{\"o}dinger equation
-for a Bose gas with an impurity atom~[10]. This equation was solved analytically
-in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, 
-which allows us to work out all properties of the dressed particle in a simple manner; 
-note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018},
-see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
-
-The lowest energy state of the non-linear Schr{\"o}dinger equation with a given $P$ is a combination of two solitons. 
-They make a dissipationless defect in the Bose gas, which accompanies the impurity. The corresponding energy 
-is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, 
-$\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass. The solution is steady only 
-for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}). 
-Note that quantum fluctuations lead to a finite dissipation (cf.~\cite{astrakharchik2004,sykes2009,Cherny2012})
-even for $P<P_c$. We do not consider this effect as it does not change our qualitative presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\begin{figure}
-\centerline{\includegraphics[scale=0.3]{figure3.pdf}}
-\caption{Panel {\bf a)} shows schematically the energies of a free and dressed particles. 
-The effective mass and the self-energy 
-can be obtained from the energy difference, $\Delta(p)$.
-Panel {\bf b)} shows $P_c$ for an impurity of mass $M\gg m$; 
-$c$ is the speed of sound in the gas and $g$ is the boson-impurity interaction strength.
-  }
-\label{fig:Figure3}
-\end{figure}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-To measure $\epsilon, m_{\mathrm{eff}}$ and $P_c$, one shall use a NBP filter to create a flux of particles 
-with momenta close to $P$. The value of $b$ must be chosen such that the current is weak, i.e., 
-there is a negligible probability to find two flux particles at distances smaller than the healing 
-length of the Bose gas. Then the impurity-in-a-gas picture is applicable by construction. 
-For the sake of argument, we assume that initially the impurity is in a hyperfine state 
-that does not interact with the Bose gas. To transfer to a strongly interacting hyperfine state 
-one has to deposit enough energy to compensate for the interaction effects; see Fig.~\ref{fig:Figure3}{\bf a)}. 
-Therefore, the radio-frequency responce (e.g., the transferred fraction) at different momenta directly measures 
-the self-energy and effective mass of the polaron;
-such a measurement would be similar to the one in a recent experiment with a three-dimensional Fermi polaron~\cite{zaccanti2017}, but 
-with a superior control over the impurity momentum. 
-Moreover, the overlap between the non-interacting and interacting states, i.e., the residue, can
-be measured, allowing one to test recent theoretical calculations~\cite{volosniev2017, pastukhov2017,grusdt2017,pastukhov2018}
-that, while qualitatively agreeing on $m_{\mathrm{eff}}$ and $\epsilon$, contradict each other on the residue.
-Since the momentum of the impurity is known, not only the effective parameters but also the limits of applicability 
-of the polaron model will be seen in the radio-frequency responce, in particular, $P_c$.
-In Fig.~\ref{fig:Figure3}{\bf b)} we present $P_c$ for impurities whose mass $M$ is much larger than $m$~\cite{hakim1997}.
-For weak interactions ($g\to 0$) the critical momentum is determined by the speed of sound, $c$, in accordance with the Landau criterion.
-In the opposite limit, $g\to \infty$, the critical momentum goes to zero as $1/g$:   
-$P_c$ is limited by the timescale for a two-body exchange.
-
-{\it Summary. --}  We proposed to engineer streams of particles with desired momenta profiles
-using a filter potential connected to a reservoir; see Fig.~\ref{fig:Figure1}.
-A stream can be used to probe cold-atom systems. It can also be used for quantum simulations, as we illustrated 
-with a narrow band-pass filter and a one-dimensional Bose gas in the `flux' region. 
-Polarons in two-, three- and mixed-dimensional geometries can be created similarly. 
-{\color{red} Time-dependent driving?}
-
-\begin{acknowledgments}
-We thank Peter Schlagheck for referring to~\cite{Schlagheck2005},
-and Joachim Brand and Volodymyr Pastukhov for useful discussions.
-A.~G.~V. gratefully acknowledges the support of the Humboldt Foundation and the Deutsche Forschungsgemeinschaft
-(VO 2437/1-1).
-\end{acknowledgments}
-
-\widetext
-
-\section{Supplementary Material}
-
-\section{Polaron}
-
-{\color{blue} Discuss the residue} 
-There is a non-zero overlap between a free particle and the polaron state; see~\cite{volosniev2017} for $P=0$.
+\section{Impurity in a Bose gas}
 
@@
 We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$ respectively. 
-The reservoir by assumption is large, such that the dynamics can be described by the thermodynamic limit $N\to \infty$ with a given density $\rho$.
-To approach this limit, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
-We are interested in the limit $N(L)\to \infty$ with $\rho=\frac{N}{L}$.
+The environment is large by assumption. To describe it, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
+We are interested in the thermodynamic limit: $N, L\to \infty$ with a fixed value of the density $\rho=\frac{N}{L}$.
 
-For $c=0$ the eigenstates can be written as $e^{2\pi i \frac{n_1x_1+\ldots+n_N x_N+my}{L}}$, where $n_1,\ldots,n_N$ and $m$ are arbitrary integrers. 
-For $c>0$ this basis set can be used to expand an eigenfunction of the Hamiltonian, $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. 
+If the system is non-interacting ($\lambda=g=0$), the eigenstates are written as $e^{2\pi i \frac{n_1x_1+\ldots+n_N x_N+my}{L}}$, where $n_1,\ldots,n_N$ and $m$ are arbitrary integers. 
+For non-vanishing interactions we use these functions to write an eigenfunction of the Hamiltonian as $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. 
 Because all interactions are pairwise, 
@@
 where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde \lambda =\frac{2 \kappa \lambda}{\hbar^2}$, and 
-$v\equiv \frac{2 \kappa P}{M \hbar}$, where $P={\cal P}-\hbar A(N-1)$ defines the momentum of the impurity in the thermodynamic limit;
+$v= \frac{2 \kappa P}{M \hbar}$ with $P={\cal P}-\hbar A(N-1)$. $P$ defines the momentum of the impurity in the thermodynamic limit;
 note that because $A$ is determined by $P$, there is a unique value of ${\cal P}$ for a given $P_I$.
-The corresponding boundary conditions read
+The boundary conditions for Eq.~(\ref{eq:GPE_resc}) read
 \begin{equation}
@@
 has an analytic steady solution~\cite{hakim1997}, which determines the properties 
-of the polaron in our problem. Let us first consider the non-interacting case $\lambda=0$. In this case the solution for $v>0$ is~\cite{tsuzuki1971, ishikawa1980}
+of the dressed impurity in our problem. Let us first consider the non-interacting impurity $g=0$. 
+In this case the solution for $v>0$ is~\cite{tsuzuki1971, ishikawa1980}
 \begin{equation}
@@
 \begin{equation}
-\phi(z)=-\pi\theta(z+z_0)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
+\phi(z)=-\pi\theta(z+z_d)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
 \label{eq:phi_c0}
 \end{equation}
-where  $\beta=1- v^2/(2\tilde \mu)$, and $z_0$ is some parameter that determines the origin. It is worthwhile noting that the solution for $v<0$ is $\Phi^*$. 
+where  $\beta=1- v^2/(2\tilde \mu)$, $z_0$ is some parameter that determines the origin and $z_d$ is the point where $\mathrm{arctan}$ reaches $\pi/2$.
+ It is worthwhile noting that the solution for $v<0$ is $\Phi^*$. 
 The solution from Eqs.~(\ref{eq:Phi_c0}) and~(\ref{eq:phi_c0}) is plotted in Fig.~\ref{fig:Fig1}; 
-for simplicity it is plotted in the interval $-L/2<z<L/2$, the region $0<z<L$ easily follows. By combining the solutions with $\pm z_0$ 
-one can construct a steady solution with a singularity at $z=0$~\cite{hakim1997}. Therefore, the `polaron' in this model is a superposition of two moving solitons. 
-In other words, the impurity creates a topological defect, which leads to a dissipationless propagation.
+for simplicity it is plotted in the interval $-L/2<z<L/2$, the region $0<z<L$ easily follows.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{figure}
- \centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
- \caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
- assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
- Note that the minimum of the density is at $-z_0$.
+ \centerline{\includegraphics[scale=0.45]{figure1appendix_new.pdf}}
+\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) ($a>0$). 
+ Note that the minimum of the density is at $-a$. 
 The shaded area is a combination of the two solutions with the singularity at $z=0$. 
@@
 
-We write the wave function for the polaron as
+To describe an interacting impurity, we combine two moving solitons with $\pm z_0$, which creates a singularity at $z=0$~\cite{hakim1997,kamenev2016}.
+Therefore, a dressed impurity in our model is a topological defect with a dissipationless propagation. 
+We write the corresponding `wave function' as
 \begin{equation}
@@
 
-Now we can calculate the energy of the polaron in the thermodynamic limit
+Now we can calculate the energy of the dressed impurity in the thermodynamic limit
 \begin{equation}
@@
 \end{equation}
-where $\epsilon$ is the effective energy of the polaron, and $m_{\mathrm{eff}}$ is the effective mass.
+where $\epsilon$ is the effective energy of the dressed impurity, and $m_{\mathrm{eff}}$ is the effective mass.
 
-\subsection{Boundary-Augmented Cost Function}\label{sec:Jaug}
-Equation \eqref{eq:cost2} shows the boundary-augmented cost function which includes a term that increases the cost for link-potential solutions that extend beyond the support region $x\in[-x_0,x_0]$.
+The parameters $m_{\mathrm{eff}}$ and $\epsilon$ calculated using the non-linear Schr{\"o}dinger equation 
+agree well with the results in the literature~\cite{mistakidis2018}. This agreement supports methods for our discussion.
+Still, further work is required to understand properties of a dressed impurity in our formalism.
+First of all, it will be interesting to investigate the critical momentum,
+which is supersonic in the employed model for $g\to 0$ and for not heavy impurities.
+Indeed, the model we solve may have a different speed of sound, because it is equivalent 
+to a heavy impurity in a gas of bosons with a mass $\kappa$. 
+It will also be interesting to calculate the residue -- the overlap between wave functions that describe 
+a state with $g=0$ and an interacting state. In the present model, the impurity changes the order parameter
+only locally, which means a non-zero residue; see~\cite{volosniev2017} for $P=0$.
+It will be interesting to calculate the overlap using an exactly solvable model, e.g., 
+a heavy impenetrable impurity in a Bose gas (solvable by Bethe ansatz) to check this result.
+
+\section{Boundary-Augmented Cost Function}\label{sec:Jaug}
+Equation~(6) shows the boundary-augmented cost function which includes a term that increases the cost for link-potential solutions that extend beyond the support region $x\in[-x_0,x_0]$.
 This added terms is
@@
 \end{equation}
-Assuming the Gaussian potential form in Eq.~\eqref{eq:V-param}, this evaluates to
+Assuming the Gaussian potential form as in Eq.~(5), this evaluates to
 \begin{equation}\label{eq:JboundaryIGaussian}

### 2019-03-27 Paper/version2/paper.tex
Arxiv submission

@@
 
+%\usepackage[a4paper, total={6in, 8in}]{geometry}
+
+%\renewcommand{\baselinestretch}{2.2}
+
 \begin{document}
 
-\title{Engineering momentum profiles of cold-atom {\color{blue} streams}}
+\title{Engineering momentum profiles of cold-atom beams}
 
@@
 {\it Introduction. --}   
-In this Letter we discuss a procedure for creating cold-atom streams with momentum transport profiles that can be selected for the matter at hand.
-Such streams would enable novel scattering experiments with quantum gases. In particular, 
+In this Letter we discuss a procedure for creating cold-atom beams with momentum transport profiles that can be selected for the matter at hand.
+Such beams would enable novel scattering experiments with quantum gases. In particular, 
 they could be used to measure parameters that define
-physics of cold-atoms systems such as such few-body parameters like the
-scattering length or three-body parameter~\cite{braaten2006, bloch2008} or
-many-body effects like the self-energy or the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
+few- and many-body physics of cold-atoms systems, e.g., the
+scattering length, three-body parameter~\cite{braaten2006, bloch2008} or
+the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
 
@@
 By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the flux region as required by the experimental application.
-Note that the momentum profile of the outgoing beam can be measured using a single-atom momentum resolution (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
+Note that the momentum profile of the outgoing beam can be measured using single-atom momentum resolution techniques (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
 
@@
 \begin{figure}
-\centerline{\includegraphics[scale=0.3]{figure1new.pdf}}
-\caption{ \textcolor{red}{The link potential looks a bit unnatural to me.
-The odd part is the kinks where the middle potential joins its neighbors.
-Can we make this smooth?
-Summing three gaussians and adding an intercept should work, yes?} An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external link potential.
+\centerline{\includegraphics[scale=0.4]{figure1new.pdf}}
+\caption{An illustration of the proposal: A reservoir that contains particles of various momenta is connected to an external link potential.
 The potential filters out the desired momenta, and the particles in the flux region have a known momentum distribution -- here, the distribution is non-zero only in the neighborhood of a chosen momentum.
-The link potential is a narrow-band filter.
+The link potential is a narrow band-pass filter.
 }
@@
 \begin{equation}\label{eq:cost1}
-  J_{\bm{\theta}} = \sum_kw_k\left|T_0(k) - T_{\bm{\theta}}(k)\right|^2,
+  J_{\bm{\theta}} = \sum_{0<k<k_F} w_k\left|T_0(k) - T_{\bm{\theta}}(k)\right|^2,
 \end{equation}
-where the $k$-integral has been approximated (up to a constant factor) by a sum over a discrete set of momentum values, and $w_k$ is the weight given to momentum $k$.
+where the $k$-integral has been approximated (up to a constant factor) by a sum over a discrete set of momentum values, the interval of integration is $[0,k_F]$, and $w_k$ is the weight given to momentum $k$.
 The weights are chosen to emphasize or de-emphasize special regions of $k$ during the minimization.
@@
 The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Ref.~\footnote{See the Supplementary Material for the full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ and
-for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem.}.
+for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem. The Supplementary Material includes Refs.~[39,40]}.
 
@@
 The main figure shows the target profile (dot-dashed, red) used during optimization (see Eq.~(\ref{eq:Ttarget})) and the actual transport profile resulting from the optimization procedure (solid, blue).
-The inset figure shows the optimal link potential $V(x, \bm{\theta^*})$.
-{\color{red} bold font in the inset}}
+The inset figure shows the optimal link potential $V(x, \bm{\theta^*})$.}
  \label{fig:method_illustration}
@@
 
-{\it Narrow band-pass filter (NBP) transport profile. --}
+{\it Narrow band-pass (NBP) filter transport profile. --}
 To illustrate the method described above we optimize for a NBP filter transport profile sharply-peaked near $k=k_0$. 
@@
  For the constraints shown in Table~\ref{tab:constraints}, we use $\sigma_{\mathrm{min}}=0.2$, $\sigma_{\mathrm{max}}=3$, $A_{\mathrm{min}}=5$, and $A_{\mathrm{max}}=30$.
+We set $k_F=2$.
 We further simplify the optimization by searching over two-Gaussian link-potentials with equal amplitudes and widths.
@@
 The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
-This additional resonance need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{In general, one needs to include the distribution of particles over the energy in the reservoir, $n(k)$,
-in the cost function. To this end, one might simply multiply in Eq.~(\ref{eq:cost1}) $T_{\bm{\theta}}(k)$ by $n(k)$, leaving the rest as is.
-The function $n(k)$ is determined by the Bose-Einstein or Fermi-Dirac distributions, temperature and the shape of the trap. Current Eq.~(\ref{eq:cost1}) assumes a Fermi gas 
-at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
+This additional resonance need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{For a reservoir at a finite temperature it is beneficial to include the energy distribution, $n(k)$,
+in the cost function. To this end, one should simply convolute $T_{\bm{\theta}}(k)$ in Eq.~(\ref{eq:cost1}) with $n(k)$. 
+The function $n(k)$ is determined by the Bose-Einstein or Fermi-Dirac distributions, temperature and the shape of the trap. For simplicity, 
+we assume in current Eq.~(\ref{eq:cost1}) a one-dimensional Fermi gas at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
 
@@
 Such sensitivity would require extremely fine control over the laser amplitudes, positions, and widths in order to produce the desired transport profile.
-To test this sensitivity, we generate 200 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
-The distributions of the peak positions and heights for the 200 perturbed potentials are shown in Fig.~\ref{fig:sensitivity}.
+To test this sensitivity, we generate 2000 perturbed potentials by varying the six parameters of the two-Gaussian solution shown in Fig.~\ref{fig:method_illustration} by a random-normal multiplicative factor with mean 1 and standard deviation 0.05.
+The distributions of the peak positions and heights for the 2000 perturbed potentials are shown in Fig.~\ref{fig:sensitivity}.
 Both the peak positions, $k_{\mathrm{max}}$, and the peak heights, $T_{\mathrm{max}}$, undergo perturbations on the scale of the $5\%$  potential perturbations suggesting that transport properties are relatively insensitive to slight errors in the potential parameters.
@@
  \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.
-Shown are the distributions of the peak position $k_{\mathrm{max}}$ (main graph) and peak height $T_{\mathrm{max}}$ (inset) for 200 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.}
+Shown are the distributions of the peak position $k_{\mathrm{max}}$ (main graph) and peak height $T_{\mathrm{max}}$ (inset) for 2000 potentials with parameters randomly perturbed on the order of $5\%$ from the optimized potential presented in Fig.~\ref{fig:method_illustration}.}
  \label{fig:sensitivity}
@@
 To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom~[10].
-This equation was solved analytically in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, which allows us to work out all properties of the dressed particle in a simple manner; note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018}, see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
+This equation was solved analytically in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, which allows us to work out all properties of the dressed particle in a simple manner; note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018,pastukhov2019}, see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
 
@@
 They make a dissipationless defect in the Bose gas, which accompanies the impurity.
-The corresponding energy is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, $\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass.
-The solution is steady only for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}).
+The corresponding lowest energy is given by $E\simeq E_B+\epsilon+P^2/(2m_{\mathrm{eff}})$, where $E_B$ is the energy of the gas without an impurity, $\epsilon$ is the self-energy of the dressed particle, and $m_{\mathrm{eff}}$ is its effective mass.
+The solution is stable only for $P<P_c$; impurities with $P>P_c$ generate grey solitons (cf.~\cite{hakim1997}).
 Note that quantum fluctuations lead to a finite dissipation (cf.~\cite{astrakharchik2004,sykes2009,Cherny2012}) even for $P<P_c$.
@@
 To measure $\epsilon, m_{\mathrm{eff}}$ and $P_c$, one can use a narrow band-pass filter as shown in Fig.~\ref{fig:method_illustration} to create a flux of particles with momenta close to $P$. 
-The value of $b$ must be chosen such that the current is weak, i.e., there is a negligible probability to find two flux particles at distances smaller than the healing
-length of the Bose gas.
-\textcolor{red}{It might be good to state here how this be accomplished using the above framework.
-For example, using a target profile with very narrow width.} Then the impurity-in-a-gas picture is applicable by construction.
+The width (value of $b$) of the target profile must be chosen such that the current is weak, i.e., there is a negligible probability to find two flux particles at distances smaller than the healing 
+length of the Bose gas. Then the impurity-in-a-gas picture is applicable by construction. 
 For simplicity, we assume that initially the impurity is in a hyperfine state 
@@
 Moreover, the overlap between the non-interacting and interacting states, i.e., the residue, can
-be measured, allowing one to test recent theoretical calculations~\cite{volosniev2017, pastukhov2017,grusdt2017,pastukhov2018}
+be measured, allowing one to test different theoretical methods~\cite{volosniev2017, pastukhov2017,grusdt2017,pastukhov2018}
 that, while qualitatively agreeing on $m_{\mathrm{eff}}$ and $\epsilon$, contradict each other on the residue.
@@
 For weak interactions ($g\to 0$) the critical momentum is determined by the speed of sound, $c$, in accordance with the Landau criterion.
-In the opposite limit, $g\to \infty$, the critical momentum goes to zero as $1/g$:   
+In the opposite limit, $g\to \infty$, the critical momentum goes to zero as $1/g$ (cf.~\cite{kamenev2016}):   
 $P_c$ is limited by the timescale for a two-body exchange.
@@
 {\it Summary.
---}  We outline a proceeder for engineering beams of particles with desired momentum profiles using a filter potential connected to a reservoir (see Fig.~\ref{fig:Figure1}).
+--}  We outline a procedure for engineering beams of particles with desired momentum profiles using a filter potential connected to a reservoir (see Fig.~\ref{fig:Figure1}).
 Such a beam can be used to probe cold-atom systems.
@@
 Polarons in two-, three- and mixed-dimensional geometries can similarly be created.
-{\color{red} Time-dependent driving?}
+
+\vspace*{1em}
 
@@
 (VO 2437/1-1).
+
+\vspace*{1em}
+
+The authors contributed equally to this work.
 \end{acknowledgments}
-
-\widetext
-
-\section{Supplementary Material}
-
-\section{Polaron}
-
-{\color{blue} Discuss the residue} 
-There is a non-zero overlap between a free particle and the polaron state; see~\cite{volosniev2017} for $P=0$.
-
-To model one impurity atom that moves through a one-dimensional environment made of $N$ cold bosonic atoms, we employ the following Hamiltonian
-\begin{equation}
-H=-\frac{\hbar^2}{2m}\sum_{i=1}^N\frac{\partial^2}{\partial x_i^2}-\frac{\hbar^2}{2M}\frac{\partial^2}{\partial y^2}+\lambda \sum_{i>j=1}^N\delta(x_i-x_j)+g \sum_{i=1}^N \delta(x_i-y),
-\end{equation}
-where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are at the coordinates $\{x_i\}$. 
-We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$ respectively. 
-The reservoir by assumption is large, such that the dynamics can be described by the thermodynamic limit $N\to \infty$ with a given density $\rho$.
-To approach this limit, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
-We are interested in the limit $N(L)\to \infty$ with $\rho=\frac{N}{L}$.
-
-For $c=0$ the eigenstates can be written as $e^{2\pi i \frac{n_1x_1+\ldots+n_N x_N+my}{L}}$, where $n_1,\ldots,n_N$ and $m$ are arbitrary integrers. 
-For $c>0$ this basis set can be used to expand an eigenfunction of the Hamiltonian, $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. 
-Because all interactions are pairwise, 
-the total (angular) momentum of the system must be conserved, and we write it as ${\cal P}=\frac{2\pi\hbar}{L}\left(\sum_{j} n_j+m\right)$.
-A conserved quantity (${\cal P}$) allows us to exclude one variable from the consideration. 
-We write the function $\Psi$ as $\Psi=e^{i \frac{{\cal P} y}{\hbar}}\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jz_j}{L}}\equiv e^{i \frac{{\cal P} y}{\hbar}} \psi(z_1,...,z_N)$ 
-with $z_i=L\theta(y-x_i)+x_i-y$, where $\theta(x)$ is the Heaviside step function, i.e., 
-$\theta(x>0) = 1$ and zero otherwise. The variables $z_i$ are defined such that $0\leq z_i \leq L$ and the impurity is placed at $z=0$ ($z=L$). Now if we insert this 
-function into the Schr{\"o}dinger equation, $H\Psi=E\Psi$, we obtain the following equation for $\psi(0<z_i<L)$
-\begin{equation}
--\frac{\hbar^2}{2m}\sum_i\frac{\partial^2 \psi}{\partial z_i^2}-\frac{\hbar^2}{2M}\left(\sum_{i}\frac{\partial }{\partial z_i}\right)^2\psi
-+ i \frac{\hbar {\cal P}}{M}\sum_{i}\frac{\partial \psi}{\partial z_i}+\lambda \sum_{i>j}\delta(z_i-z_j)\psi=\left(E-\frac{{\cal P}^2}{2M}\right)\psi,
-\end{equation}
-which must be supplemented with the boundary conditions:
-\begin{equation}
-\psi(z_i=0)=\psi(z_i=L); \qquad \frac{\partial \psi}{\partial z_i}\bigg|^{z_i=0^+}_{z_i=L^-}= \frac{2 g \kappa}{\hbar^2} \psi(z_i=0),
-\end{equation}
-where $\kappa=mM/(m+M)$ is the reduced mass.
-
-By assumption the bosons interact weakly, such that the ansatz $\psi=\prod_i \Phi(z_i)$ can be used to approximate the system. 
-To minimize the expectation value of the Hamiltonian the function $\Phi(z)$ must satisfy the following non-linear Schr{\"o}dinger equation
-\begin{equation}
--\frac{\hbar^2}{2\kappa}\frac{\partial^2\Phi}{\partial z^2}+i\frac{\hbar {\cal P}}{M}\frac{\partial \Phi}{\partial z}
--i \frac{\hbar^2 (N-1) A}{M} \frac{\partial\Phi}{\partial z} + \lambda (N-1)|\Phi|^2\Phi=\mu \Phi,
-\end{equation}
-where $A=-i\int \Phi(x)^*\frac{\partial}{\partial x}\Phi(x)\mathrm{d}x$ defines the momentum of a boson, and $\mu$ is the Lagrange multiplier. 
-We rewrite this equation as
-\begin{equation}
--\frac{\partial^2\Phi}{\partial z^2}+i v \frac{\partial \Phi}{\partial z} + \tilde \lambda (N-1)|\Phi|^2\Phi=\tilde\mu\Phi,
-\label{eq:GPE_resc}
-\end{equation}
-where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde \lambda =\frac{2 \kappa \lambda}{\hbar^2}$, and 
-$v\equiv \frac{2 \kappa P}{M \hbar}$, where $P={\cal P}-\hbar A(N-1)$ defines the momentum of the impurity in the thermodynamic limit;
-note that because $A$ is determined by $P$, there is a unique value of ${\cal P}$ for a given $P_I$.
-The corresponding boundary conditions read
-\begin{equation}
-\Phi(z=0)=\Phi(z=L); \qquad \frac{\partial \Phi}{\partial z}\bigg|^{z=0^+}_{z=L^-}= \tilde g \Phi(0),
-\end{equation}
-where $\tilde g= \frac{2\kappa g}{\hbar^2}$. The non-linear equation~(\ref{eq:GPE_resc}) 
-has an analytic steady solution~\cite{hakim1997}, which determines the properties 
-of the polaron in our problem. Let us first consider the non-interacting case $\lambda=0$. In this case the solution for $v>0$ is~\cite{tsuzuki1971, ishikawa1980}
-\begin{equation}
-\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z+z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
-\label{eq:Phi_c0}
-\end{equation}
-\begin{equation}
-\phi(z)=-\pi\theta(z+z_0)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
-\label{eq:phi_c0}
-\end{equation}
-where  $\beta=1- v^2/(2\tilde \mu)$, and $z_0$ is some parameter that determines the origin. It is worthwhile noting that the solution for $v<0$ is $\Phi^*$. 
-The solution from Eqs.~(\ref{eq:Phi_c0}) and~(\ref{eq:phi_c0}) is plotted in Fig.~\ref{fig:Fig1}; 
-for simplicity it is plotted in the interval $-L/2<z<L/2$, the region $0<z<L$ easily follows. By combining the solutions with $\pm z_0$ 
-one can construct a steady solution with a singularity at $z=0$~\cite{hakim1997}. Therefore, the `polaron' in this model is a superposition of two moving solitons. 
-In other words, the impurity creates a topological defect, which leads to a dissipationless propagation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
- \begin{figure}
- \centerline{\includegraphics[scale=0.45]{figure1appendix.pdf}}
- \caption{Panel {\bf a)}: The density, $|\Phi|^2 \tilde \lambda (N-1)$, of the Bose gas for two different parameters $z_0$: $z_0=0.2$ (left red curve), $z_0=-0.2$ (right blue curve), 
- assuming that $\tilde \mu=1.6, v=0.3$ (everything is in units where $\rho=1$). 
- Note that the minimum of the density is at $-z_0$.
-The shaded area is a combination of the two solutions with the singularity at $z=0$.
-Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
- \label{fig:Fig1}
- \end{figure}
- %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-We write the wave function for the polaron as
-\begin{equation}
-\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z\pm z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
-\end{equation}
-with 
-\begin{equation}
-\phi(z)=\delta \phi \theta(-z)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z\pm z_0)\right]-2\beta+1}\right),
-\label{eq:phase_soliton}
-\end{equation}
-where $z_0>0$ is discussed below, the parameter $\delta \phi$ is not important for the further derivations, it reassures that the phase is a continuous function;
-the plus sign in $\pm$ corresponds to $z>0$ and the minus sign to $z<0$. This function is illustrated in Fig.~\ref{fig:Fig1}. 
-The density has a non-analytic derivative at $z=0$. The phase is a continuous function at $z=0$ (its derivative is also continuous).
-Note that the wave function is not periodic (see Eq.~(\ref{eq:phase_soliton})). This non-periodicity is not important 
-for our discussion, because we are interested in the behavior of the bosons close to the impurity. It suggests that a grey soliton
-must be formed upon a change of interaction parameters to take care of the phase slip.
-
-The parameter $\tilde \mu$ is found from the normalization condition $\int \Phi^2=1$. For $N\to\infty$, we obtain
-\begin{equation}
-\tilde \mu=\gamma \rho^2 \frac{N-1}{N}\left(1-2\sqrt{2\beta_0} \frac{ (\mathrm{tanh}(d)-1)}{\sqrt{\gamma}N}\right),
-\end{equation}
-where $\gamma=\tilde \lambda /\rho$, $\rho=N/L$, $\beta_0=1-v^2/(2\gamma \rho^2)$, and $d=\sqrt{\frac{\gamma \beta_0}{2}}\rho z_0$.
-The equation to determine $z_0$ is found by using the boundary conditions at $z=\{0,L\}$
-\begin{equation}
-\frac{\tilde g}{\rho \sqrt{2\gamma}}=\frac{\beta_0^{\frac{3}{2}}\tanh(d)}{-\beta_0+\cosh^2(d)}.
-\label{eq:c_v}
-\end{equation}
-This equation is cubic (in $\tanh(d)$), hence, the solutions can be found in a closed form.
-There are three solutions. However, only two will lead to the acceptable values of $z_0$. 
-We will refer to these steady solutions as the `polaron' and the `polaron-soliton' pair, because in the limit $g\to 0$ the former 
-corresponds to the ground state, and the latter to a gray soliton. 
-The `polaron-soliton' pair is expected to be unstable (small perturbations will lead to 
-a decay of this steady solution~\cite{hakim1997}),
-therefore, we do not consider it. The solutions merge for $z_m$ 
-\begin{equation}
-\tanh^2\left(\sqrt{\frac{\gamma \beta_0}{2}}\rho z_m\right)=\frac{\sqrt{1+\frac{4v^2}{\gamma \rho^2}}-(1+\frac{v^2}{\gamma \rho^2})}{2\beta_0},
-\label{eq:z_m}
-\end{equation}
-which is derived by taking a derivative of Eq.~(\ref{eq:c_v}) with respect to $z_0$ and equating the resulting expression to zero -- this determines 
-the maximum value of $g$ for which (for a fixed $\beta_0$) there is a steady solution.
-Equations~(\ref{eq:c_v}) and (\ref{eq:z_m}) give the equation for the critical value of $v_c$:
-\begin{equation}
-\frac{\tilde g}{\rho\sqrt{\gamma}}=\frac{3-\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}{-1+\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}\sqrt{\sqrt{1+\frac{4v_c^2}{\gamma \rho}}-1-\frac{v_c^2}{\gamma\rho^2}}.
-\end{equation}
-For $v>v_c$ (see Fig. 1 of the main text) there is no steady solutions.
-
-Now we can calculate the energy of the polaron in the thermodynamic limit
-\begin{equation}
-{\cal E}\equiv \lim_{N\to\infty, \frac{N}{L}\to \rho}\left[E(c,P)-E(c=0,P=0)\right],
-\end{equation}
-where
-\begin{equation}
-E(c,P) = \frac{P^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-gN(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
-\end{equation}
-Using these expressions we derive 
-\begin{equation}
-{\cal E}=\frac{P_I^2}{2M}+\frac{\hbar^2\rho}{2\kappa}\frac{\sqrt{2 \tilde g \rho \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P_I}{M}\lim_{N\to\infty} A N,
-\end{equation}
-where $b=1+\frac{v^2}{4\tilde g\rho}=1+\frac{\kappa P_I^2}{2M^2 g\rho}$. This energy for $v\to 0$ can be written as 
-\begin{equation}
-{\cal E}\simeq \epsilon+ \frac{P_I^2}{2m_{\mathrm{\mathrm{eff}}}},
-\end{equation}
-where $\epsilon$ is the effective energy of the polaron, and $m_{\mathrm{eff}}$ is the effective mass.
-
-\subsection{Boundary-Augmented Cost Function}\label{sec:Jaug}
-Equation \eqref{eq:cost2} shows the boundary-augmented cost function which includes a term that increases the cost for link-potential solutions that extend beyond the support region $x\in[-x_0,x_0]$.
-This added terms is
-\begin{equation}
-  J_{\mathrm{boundary}} = \alpha \sum_i^N J_{\mathrm{boundary}}^i,
-\end{equation}
-where 
-\begin{equation}\label{eq:Jboundaryi}
-  J_{\mathrm{boundary}}^i = \int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2.
-\end{equation}
-Assuming the Gaussian potential form in Eq.~\eqref{eq:V-param}, this evaluates to
-\begin{equation}\label{eq:JboundaryIGaussian}
-  J_{\mathrm{boundary}}^i = \frac{\sqrt{\pi}}{2}A_i^2\sigma_i\left[
-    \erfc\left(\frac{x_0+\mu_i}{\sigma_i}\right) +
-    \erfc\left(\frac{x_0-\mu_i}{\sigma_i}\right)
-  \right],
-\end{equation}
-where $\erfc$ is the complementary error function.
 

### 2019-04-03 Paper/version2/SM.tex
Version for submisson to PRL

@@
 where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are at the coordinates $\{x_i\}$. 
-We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$ respectively. 
+We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$, respectively. 
 The environment is large by assumption. To describe it, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
@@
 $v= \frac{2 \kappa P}{M \hbar}$ with $P={\cal P}-\hbar A(N-1)$. $P$ defines the momentum of the impurity in the thermodynamic limit;
-note that because $A$ is determined by $P$, there is a unique value of ${\cal P}$ for a given $P_I$.
+note that $A$ is determined by $P$, and there is a unique value of ${\cal P}$ for a given $P$.
 The boundary conditions for Eq.~(\ref{eq:GPE_resc}) read
@@
  \centerline{\includegraphics[scale=0.45]{figure1appendix_new.pdf}}
-\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) ($a>0$). 
+\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) 
+($a>0$, the exact value of $a$ is not important for our discussion). 
  Note that the minimum of the density is at $-a$. 
@@
 corresponds to the ground state, and the latter to a gray soliton. 
-The `polaron-soliton' pair is expected to be unstable (small perturbations will lead to 
+The `polaron-soliton' pair is expected to be unstable (small perturbations lead to 
 a decay of this steady solution~\cite{hakim1997}),
@@
 \end{equation}
-For $v>v_c$ (see Fig. 1 of the main text) there is no steady solutions.
+For $v>v_c$ (see Fig. 4 of the main text) there is no steady solutions.
 
@@
 \begin{equation}
-E(c,P) = \frac{P^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-gN(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
+E(c,P) = \frac{{\mathcal P}^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-\lambda N(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
 \end{equation}
@@
 \begin{equation}
-{\cal E}=\frac{P_I^2}{2M}+\frac{\hbar^2\rho}{2\kappa}\frac{\sqrt{2 \tilde g \rho \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P_I}{M}\lim_{N\to\infty} A N,
+{\cal E}=\frac{P^2}{2M}+\frac{\hbar^2\rho^2}{2\kappa}\frac{\sqrt{2  \gamma \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P}{M}\lim_{N\to\infty} A N,
 \end{equation}
-where $b=1+\frac{v^2}{4\tilde g\rho}=1+\frac{\kappa P_I^2}{2M^2 g\rho}$. This energy for $v\to 0$ can be written as 
+where $b=1+\frac{v^2}{4\tilde \lambda \rho}=1+\frac{\kappa P^2}{2M^2 \lambda \rho}$. This energy for $v\to 0$ can be written as 
 \begin{equation}
-{\cal E}\simeq \epsilon+ \frac{P_I^2}{2m_{\mathrm{\mathrm{eff}}}},
+{\cal E}\simeq \epsilon+ \frac{P^2}{2m_{\mathrm{\mathrm{eff}}}},
+\label{eq:18}
 \end{equation}
@@
 
-The parameters $m_{\mathrm{eff}}$ and $\epsilon$ calculated using the non-linear Schr{\"o}dinger equation 
-agree well with the results in the literature~\cite{mistakidis2018}. This agreement supports methods for our discussion.
-Still, further work is required to understand properties of a dressed impurity in our formalism.
+The parameters $m_{\mathrm{eff}}$ and $\epsilon$ calculated using Eq.~(\ref{eq:18})  
+agree well with the results in the literature~\cite{mistakidis2018}, supporting 
+the use of the non-linear Schr{\"o}dinger equation for solving the problem. 
+However, further work is required to understand other properties of a dressed impurity in this formalism.
 First of all, it will be interesting to investigate the critical momentum,
 which is supersonic in the employed model for $g\to 0$ and for not heavy impurities.
-Indeed, the model we solve may have a different speed of sound, because it is equivalent 
-to a heavy impurity in a gas of bosons with a mass $\kappa$. 
-It will also be interesting to calculate the residue -- the overlap between wave functions that describe 
-a state with $g=0$ and an interacting state. In the present model, the impurity changes the order parameter
-only locally, which means a non-zero residue; see~\cite{volosniev2017} for $P=0$.
-It will be interesting to calculate the overlap using an exactly solvable model, e.g., 
-a heavy impenetrable impurity in a Bose gas (solvable by Bethe ansatz) to check this result.
+Indeed, the model we solve is equivalent to a heavy impurity moving in a gas of bosons with mass $\kappa$,  
+which has a different speed of sound. 
+Note that Fig.~4 of the main text reports on a heavy impurity ($M/m\gg 1$) for which this problem does not occur.
+It will be also interesting to investigate the residue -- the overlap between the wave function that describes 
+a state with $g=0$ and the wave function that decribes an interacting state. In the present model, the impurity changes the order parameter
+only locally, which means a non-zero residue (see~\cite{volosniev2017} for $P=0$), contradicting other 
+studies on the topic~\cite{pastukhov2017,grusdt2017}. To understand this disagreement, one could calculate the overlap using an exactly solvable model, e.g., 
+a heavy impenetrable impurity in a Bose gas (solvable by Bethe ansatz).
 

### 2019-04-03 Paper/version2/paper.tex
Version for submisson to PRL

@@
 the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
+{\color{green} The beams can also be used as the initial state for atom interferometry~\cite{Impens2006,Cronin2009}}.
 
 Figure ~\ref{fig:Figure1} summarizes our proposal.
-Analogous to a quantum switch device (`transistor')~\cite{zoller2004, marchukov2016}, the flux of particles from the `source' (reservoir) is determined by the `gate' (link potential).
+Analogous to a quantum switch device (`transistor')~\cite{zoller2004, marchukov2016,thuberg2017}, the flux of particles from the `source' (reservoir) is determined by the `gate' (link potential).
 However, rather than simply controlling the overall transmission rate, our proposal allows one to design the momentum profile of the outgoing flux.
@@
 By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the flux region as required by the experimental application.
+{\color{green} The tunability of $V_0(x)$ in cold-atom set-ups has been recently demonstrated~\cite{esslinger2015,esslinger2018,esslinger2019}, 
+meaning that our proposal relies only on the toolbox readily available in laboratories.}
 Note that the momentum profile of the outgoing beam can be measured using single-atom momentum resolution techniques (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
@@
 The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Ref.~\footnote{See the Supplementary Material for the full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ and
-for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem. The Supplementary Material includes Refs.~[39,40]}.
+for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem. The Supplementary Material includes Refs.~\cite{tsuzuki1971,ishikawa1980}}.
 
@@
 {\it Application.
---} A Bose or Fermi gas can be placed in the flux region  (see Fig.~\ref{fig:Figure1}) to study quantum environments with neutral, mobile impurities -- an important research venue promoted by cold-atom simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017}.
+--} A Bose or Fermi gas can be placed in the flux region  (see Fig.~\ref{fig:Figure1}) to study quantum environments with neutral, mobile impurities -- an important research venue promoted by cold-atom simulators~\cite{zwierlein2009,salomon2009,grimm2012, widera2012, catani2012, fukuhara2013, hu2016,arlt2016,zaccanti2017,ardila2018}.
 With our proposal it is possible to investigate dynamics of impurities that initially have a known momentum profile, thus allowing for a direct measurement of the effective mass and the critical momentum.

### 2019-04-03 Paper/prl_sub/paper.tex
added folder with only neccessary files for prl submission

--- 2019-04-03 Paper/version2/paper.tex
@@
 \begin{abstract}
-We describe a procedure for engineering beams of cold atoms by selectively filtering particles from a trapped gas based on momenta.
-A gas is spatially connected to an external potential whose transmission coefficient only allows atoms with desired momenta to escape from the trap. We outline an algorithm whose input is the desired
-transmission profile of the outgoing beam and whose output is a filter potential that approximately produces the desired beam profile.
-We illustrate this procedure by finding a filter potential that approximately produces a narrow band-pass (NBP) filter transport profile.
-Further, we discuss a topical application, in which a NBP filter is integrated to produce Bose polarons, allowing one to study the self-energy and the effective mass of polarons, as well as the corresponding Landau criterion.
+We describe a procedure for engineering beams of cold atoms by selectively draining particles from a trapped gas based on momenta.
+Atoms escape through a filter potential that only transmits atoms with the desired momenta.
+We outline an algorithm that outputs a filter potential that produces a pre-specified beam momentum profile.
+We illustrate this procedure for the case of a narrow band-pass (NBP) quantum filter.
+Lastly, we discuss the application of the NBP filter for probing the self-energy and effective mass of Bose polarons, as well as the corresponding Landau criterion.
 \end{abstract}
@@
 the self-energy and the effective mass of a polaron~\cite{massignan2014, schmidt2018}.
-{\color{green} The beams can also be used as the initial state for atom interferometry~\cite{Impens2006,Cronin2009}}.
+The beams can also be used as the initial state for atom interferometry~\cite{Impens2006,Cronin2009}.
 
@@
 By carefully tuning $V_0(x)$ one produces a $T_0(k)$ that allows only particles with desired momenta to tunnel through the barrier into the flux region as required by the experimental application.
-{\color{green} The tunability of $V_0(x)$ in cold-atom set-ups has been recently demonstrated~\cite{esslinger2015,esslinger2018,esslinger2019}, 
-meaning that our proposal relies only on the toolbox readily available in laboratories.}
+The tunability of $V_0(x)$ in cold-atom set-ups has been recently demonstrated~\cite{esslinger2015,esslinger2018,esslinger2019},
+suggesting that our proposal relies only on the toolbox available in current cold-atom laboratories.
 Note that the momentum profile of the outgoing beam can be measured using single-atom momentum resolution techniques (e.g.,~\cite{jochim2018}), allowing one to confirm that the beam has the desired flux profile.
@@
 \begin{figure}
-   \includegraphics[width=1\linewidth]{figures/plot_transport_profiles_with_inset.pdf}
+   \includegraphics[width=1\linewidth]{plot_transport_profiles_with_inset.pdf}
  \caption[Narrow band-pass filter link potential]{A two-Gaussian solution for the narrow band-pass filter transport profile.
@@
 \begin{figure}
-   \includegraphics[width=1\linewidth]{figures/plot_sensitivity.pdf}
+   \includegraphics[width=1\linewidth]{plot_sensitivity.pdf}
  \caption[Sensitivity Plot]{Sensitivity of the transport profile to perturbations of the potential parameters.

### 2019-05-10 Paper/pra_resub/paper.tex
PRA Resub

--- 2019-04-03 Paper/prl_sub/paper.tex
@@
-\documentclass[twocolumn,amsmath,amssymb,showpacs,prl,superscriptaddress,aps]{revtex4-1}
+\documentclass[twocolumn,amsmath,amssymb,showpacs,pra,superscriptaddress,aps]{revtex4-1}
 
@@
 {\it Introduction. --}   
-In this Letter we discuss a procedure for creating cold-atom beams with momentum transport profiles that can be selected for the matter at hand.
+In this Rapid Communication we discuss a procedure for creating cold-atom beams with momentum transport profiles that can be selected for the matter at hand.
 Such beams would enable novel scattering experiments with quantum gases. In particular, 
@@
 
-In this Letter,  we discuss how to determine an appropriate $V_0(x)$ for a given desired flux profile $T_0(k)$.
+In this Rapid Communication,  we discuss how to determine an appropriate $V_0(x)$ for a given desired flux profile $T_0(k)$.
 Furthermore, we briefly discuss the 1D Bose polaron problem as a possible application of cold-atom beams.
@@
 where $\alpha$ is a tuning parameter chosen empirically to aid in convergence. 
-We find that results are not very sensitive to the choice of $\alpha$ probably due to the very short tails of the Gaussian potentials.
+{\color{blue} If the potential $V_i$ is outside $[-x_0,x_0]$ then the boundary-augmented 
+cost function evaluates to $J_{\bm{\theta}}\simeq J_{\bm{\theta}} +\alpha A_i$, which means that $\alpha$
+should be chosen of the order $J_{\bm{\theta}}/A_{\mathrm{min}}$ to dictate the constraint.}
  The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
@@
 Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing for this particular optimization problem.
+{\color{green} Here we can discuss why it is suprising or not.
+Althuogh such a discussion is not really
+necessarily, in my opinion.}
 
@@
 Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the NBP filter optimization.
-The solution does a good job of suppressing transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
-This additional resonance need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population near $k=2$~\footnote{For a reservoir at a finite temperature it is beneficial to include the energy distribution, $n(k)$,
+{\color{blue} The solution suppresses transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
+In general, the transmission coefficient will always be non-zero to the right of the target profile. 
+This, however, need not be a problem if the atoms are sourced from a thermal reservoir with sufficiently low population to the right of the target profile~\footnote{For a reservoir at a finite temperature it is beneficial to include the energy distribution, $n(k)$,
 in the cost function. To this end, one should simply convolute $T_{\bm{\theta}}(k)$ in Eq.~(\ref{eq:cost1}) with $n(k)$. 
@@
 we assume in current Eq.~(\ref{eq:cost1}) a one-dimensional Fermi gas at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
+Moreover, the transmission coefficient can be furher shaped by using a second NBP filter.}
 
@@
 Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
-We discovered empirically that these more complicated transport profiles require more than two Gaussian potentials.
-In our explorations, we found that link potentials made of 3- or 4-Gaussian potentials tended to be more sensitive to random variations of potential parameters.
+{\color{blue} These more complicated transport profiles require more than two Gaussian potentials,
+because they rely on multipath interference that must supress tunelling for certain values of momenta.} In our explorations, we found that link potentials made of 3- or 4-Gaussian potentials tended to be more sensitive to random variations of potential parameters.
 If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.
@@
 With our proposal it is possible to investigate dynamics of impurities that initially have a known momentum profile, thus allowing for a direct measurement of the effective mass and the critical momentum.
-A detailed discussion of these concepts is beyond the scope of the Letter.
+A detailed discussion of these concepts is beyond the scope of the Rapid Communication.
 Still, we find it useful to briefly explain them in connection to our proposal.
 To this end, we consider a degenerate one-dimensional Bose gas with an impurity of momentum $P$.
-To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom~[10].
+To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom~[16].
 This equation was solved analytically in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, which allows us to work out all properties of the dressed particle in a simple manner; note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018,pastukhov2019}, see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.

### 2019-06-05 Paper/pra_resub/paper.tex
accepted red comments and started drafting green comment

@@
 where $\alpha$ is a tuning parameter chosen empirically to aid in convergence. 
-{\color{blue} If the potential $V_i$ is outside $[-x_0,x_0]$ then the boundary-augmented 
+ If the potential $V_i$ is outside $[-x_0,x_0]$ then the boundary-augmented 
 cost function evaluates to $J_{\bm{\theta}}\simeq J_{\bm{\theta}} +\alpha A_i$, which means that $\alpha$
-should be chosen of the order $J_{\bm{\theta}}/A_{\mathrm{min}}$ to dictate the constraint.}
+should be chosen of the order $J_{\bm{\theta}}/A_{\mathrm{min}}$ to dictate the constraint.
  The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
@@
 Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing for this particular optimization problem.
-{\color{green} Here we can discuss why it is suprising or not.
-Althuogh such a discussion is not really
-necessarily, in my opinion.}
 
@@
 Figure \ref{fig:method_illustration} shows the link potential and transport profile resulting for the NBP filter optimization.
-{\color{blue} The solution suppresses transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
+The solution suppresses transport except near $k=1$ as set by our Lorentz target profile and near $k=2$ resulting from a second resonance in the scattering potential.
 In general, the transmission coefficient will always be non-zero to the right of the target profile. 
@@
 we assume in current Eq.~(\ref{eq:cost1}) a one-dimensional Fermi gas at zero temperature in a harmonic trap, i.e., $n(k<k_F)=1$ and zero otherwise.}.
-Moreover, the transmission coefficient can be furher shaped by using a second NBP filter.}
+Moreover, the transmission coefficient can be furher shaped by using a second NBP filter.
 
@@
 Though we have demonstrated our optimization method in a very simple scenario, it is possible to apply this technique to more complicated scenarios such as a double band-pass filter or step transport profiles.
-{\color{blue} These more complicated transport profiles require more than two Gaussian potentials,
-because they rely on multipath interference that must supress tunelling for certain values of momenta.} In our explorations, we found that link potentials made of 3- or 4-Gaussian potentials tended to be more sensitive to random variations of potential parameters.
+These more complicated transport profiles require more than two Gaussian potentials,
+because they rely on multipath interference that must supress tunelling for certain values of momenta.
+In our explorations, we found that link potentials made of 3- or 4-Gaussian potentials tended to be more sensitive to random variations of potential parameters.
 If such potentials are needed to produce the desired transport profile, it may be possible to further augment the cost function in order to preference solutions that are less sensitive to potential perturbations.

### 2019-07-08 Paper/prarc_resub/paper.tex
Added new folder for pra resub and renamed old folder

--- 2019-06-05 Paper/pra_resub/paper.tex
@@
 We minimize $J_{\bm{\theta}}^{\mathrm{aug}}$ for $\bm{\theta}^*$ using the global optimization routine called Differential Evolution (DE) \cite{storn1997differential}.
-This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem.
+This evolutionary-based search algorithm is suitable given the non-convex (multiple local minima) nature of the optimization problem and the continuity of the parameter space.
 Despite its simplicity, DE does a good job of balancing exploration of the space of link potentials against the need to efficiently learn from each sample with little tuning of the model settings.
-Empirically, we found DE to perform much better than several other approaches including random search, Nelder-Mead, and Simulated Annealing for this particular optimization problem.
+Empirically, we found DE to converge to good solutions much more quickly than random search perhaps due to DE's ability to incorporate information from the previous iteration of the optimization algorithm.
 

### 2019-07-09 Paper/pra_resub/paper.tex
finalized pra resub

@@
-\documentclass[twocolumn,amsmath,amssymb,showpacs,pra,superscriptaddress,aps]{revtex4-1}
+\documentclass[reprint, twocolumn,amsmath,amssymb,showpacs,pra,superscriptaddress,aps]{revtex4-1}
 
@@
 {\it Introduction. --}   
-In this Rapid Communication we discuss a procedure for creating cold-atom beams with momentum transport profiles that can be selected for the matter at hand.
+In this article we discuss a procedure for creating cold-atom beams with momentum transport profiles that can be selected for the matter at hand.
 Such beams would enable novel scattering experiments with quantum gases. In particular, 
@@
 
-In this Rapid Communication,  we discuss how to determine an appropriate $V_0(x)$ for a given desired flux profile $T_0(k)$.
+In this article, we discuss how to determine an appropriate $V_0(x)$ for a given desired flux profile $T_0(k)$.
 Furthermore, we briefly discuss the 1D Bose polaron problem as a possible application of cold-atom beams.
+
+Other studies related to the engineering of atomic beams have focused on the  outcoupling of atoms in an atomic wave guide to a Bose-Einstein condensate using rf fields \cite{PhysRevLett.97.200402, PhysRevA.80.041605, buning2010slow} or on controlling the transmission of atoms with careful manipulation of an optical lattice \cite{PhysRevLett.84.399, PhysRevLett.107.230401, PhysRevA.92.033614}.
+In contrast, the current article proposes a method for engineering atomic beams by coupling a trapped gas of atoms to a combination of individually tuned lasers.
+Moreover, the proposed scheme is generic in the sense that one can approximately produce arbitrary desired momentum profiles of the transmitted atom beam.
 
@@
 should be chosen of the order $J_{\bm{\theta}}/A_{\mathrm{min}}$ to dictate the constraint.
- The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function.
-The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Ref.~\footnote{See the Supplementary Material for the full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ and
-for the solution to the non-linear Schr{\"o}dinger equation for the impurity-(Bose gas) problem. The Supplementary Material includes Refs.~\cite{tsuzuki1971,ishikawa1980}}.
+ The integral in Eq.~\eqref{eq:cost2} evaluates to the complementary error function. The full form of $J_{\bm{\theta}}^{\mathrm{aug}}$ is given in Appendix \ref{app:J}.
 
@@
 With our proposal it is possible to investigate dynamics of impurities that initially have a known momentum profile, thus allowing for a direct measurement of the effective mass and the critical momentum.
-A detailed discussion of these concepts is beyond the scope of the Rapid Communication.
+A detailed discussion of these concepts is beyond the scope of this article.
 Still, we find it useful to briefly explain them in connection to our proposal.
 To this end, we consider a degenerate one-dimensional Bose gas with an impurity of momentum $P$.
-To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom~[16].
+To model this system, we employ a non-linear Schr{\"o}dinger equation for a Bose gas with an impurity atom (See Appendix \ref{app:impurity_bose_gas}).
 This equation was solved analytically in the context of a nonlinear flow past an obstacle~\cite{hakim1997}, which allows us to work out all properties of the dressed particle in a simple manner; note that this (or a similar) non-linear equation has been discussed in Refs.~\cite{kamenev2016, volosniev2017, mistakidis2018, dehkharghani2018, pastukhov2018,pastukhov2019}, see also~\cite{sacha2006, catani2012, kain2016, parisi2017,grusdt2017, pastukhov2017, kain2018} for other relevant studies.
@@
 
+\onecolumngrid
+\appendix
+
+\section{Boundary-Augmented Cost Function}\label{app:J}
+Equation~(6) shows the boundary-augmented cost function which includes a term that increases the cost for link-potential solutions that extend beyond the support region $x\in[-x_0,x_0]$.
+This added terms is
+\begin{equation}
+  J_{\mathrm{boundary}} = \alpha \sum_i^N J_{\mathrm{boundary}}^i,
+\end{equation}
+where 
+\begin{equation}\label{eq:Jboundaryi}
+  J_{\mathrm{boundary}}^i = \int\limits_{|x|>x_0}dx\,|V_i(x; A_i,\mu_i,\sigma_i)|^2.
+\end{equation}
+Assuming the Gaussian potential form as in Eq.~(5), this evaluates to
+\begin{equation}\label{eq:JboundaryIGaussian}
+  J_{\mathrm{boundary}}^i = \frac{\sqrt{\pi}}{2}A_i^2\sigma_i\left[
+    \erfc\left(\frac{x_0+\mu_i}{\sigma_i}\right) +
+    \erfc\left(\frac{x_0-\mu_i}{\sigma_i}\right)
+  \right],
+\end{equation}
+where $\erfc$ is the complementary error function.
+
+\section{Impurity in a Bose gas}\label{app:impurity_bose_gas}
+
+To model one impurity atom that moves through a one-dimensional environment made of $N$ cold bosonic atoms, we employ the following Hamiltonian
+\begin{equation}
+H=-\frac{\hbar^2}{2m}\sum_{i=1}^N\frac{\partial^2}{\partial x_i^2}-\frac{\hbar^2}{2M}\frac{\partial^2}{\partial y^2}+\lambda \sum_{i>j=1}^N\delta(x_i-x_j)+g \sum_{i=1}^N \delta(x_i-y),
+\end{equation}
+where $M$ is the mass of the impurity atom, and $m$ is the mass of a bosonic particle. The position of the impurity is $y$, bosons are at the coordinates $\{x_i\}$. 
+We assume that the realistic boson-boson and boson-impurity interactions are well-described by the zero-range potentials of strengths $\lambda$ and $g$, respectively. 
+The environment is large by assumption. To describe it, the periodic boundary conditions are used: The particles move in a ring of the circumference $L$, such that $0<x_i<L$ and $0<y<L$.
+We are interested in the thermodynamic limit: $N, L\to \infty$ with a fixed value of the density $\rho=\frac{N}{L}$.
+
+If the system is non-interacting ($\lambda=g=0$), the eigenstates are written as $e^{2\pi i \frac{n_1x_1+\ldots+n_N x_N+my}{L}}$, where $n_1,\ldots,n_N$ and $m$ are arbitrary integers. 
+For non-vanishing interactions we use these functions to write an eigenfunction of the Hamiltonian as $\Psi=\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jx_j+my}{L}}$. 
+Because all interactions are pairwise, 
+the total (angular) momentum of the system must be conserved, and we write it as ${\cal P}=\frac{2\pi\hbar}{L}\left(\sum_{j} n_j+m\right)$.
+A conserved quantity (${\cal P}$) allows us to exclude one variable from the consideration. 
+We write the function $\Psi$ as $\Psi=e^{i \frac{{\cal P} y}{\hbar}}\sum_{\{n_j\},m} a_{\{n_j\},m}e^{2\pi i \frac{\sum n_jz_j}{L}}\equiv e^{i \frac{{\cal P} y}{\hbar}} \psi(z_1,...,z_N)$ 
+with $z_i=L\theta(y-x_i)+x_i-y$, where $\theta(x)$ is the Heaviside step function, i.e., 
+$\theta(x>0) = 1$ and zero otherwise. The variables $z_i$ are defined such that $0\leq z_i \leq L$ and the impurity is placed at $z=0$ ($z=L$). Now if we insert this 
+function into the Schr{\"o}dinger equation, $H\Psi=E\Psi$, we obtain the following equation for $\psi(0<z_i<L)$
+\begin{equation}
+-\frac{\hbar^2}{2m}\sum_i\frac{\partial^2 \psi}{\partial z_i^2}-\frac{\hbar^2}{2M}\left(\sum_{i}\frac{\partial }{\partial z_i}\right)^2\psi
++ i \frac{\hbar {\cal P}}{M}\sum_{i}\frac{\partial \psi}{\partial z_i}+\lambda \sum_{i>j}\delta(z_i-z_j)\psi=\left(E-\frac{{\cal P}^2}{2M}\right)\psi,
+\end{equation}
+which must be supplemented with the boundary conditions:
+\begin{equation}
+\psi(z_i=0)=\psi(z_i=L); \qquad \frac{\partial \psi}{\partial z_i}\bigg|^{z_i=0^+}_{z_i=L^-}= \frac{2 g \kappa}{\hbar^2} \psi(z_i=0),
+\end{equation}
+where $\kappa=mM/(m+M)$ is the reduced mass.
+
+By assumption the bosons interact weakly, such that the ansatz $\psi=\prod_i \Phi(z_i)$ can be used to approximate the system. 
+To minimize the expectation value of the Hamiltonian the function $\Phi(z)$ must satisfy the following non-linear Schr{\"o}dinger equation
+\begin{equation}
+-\frac{\hbar^2}{2\kappa}\frac{\partial^2\Phi}{\partial z^2}+i\frac{\hbar {\cal P}}{M}\frac{\partial \Phi}{\partial z}
+-i \frac{\hbar^2 (N-1) A}{M} \frac{\partial\Phi}{\partial z} + \lambda (N-1)|\Phi|^2\Phi=\mu \Phi,
+\end{equation}
+where $A=-i\int \Phi(x)^*\frac{\partial}{\partial x}\Phi(x)\mathrm{d}x$ defines the momentum of a boson, and $\mu$ is the Lagrange multiplier. 
+We rewrite this equation as
+\begin{equation}
+-\frac{\partial^2\Phi}{\partial z^2}+i v \frac{\partial \Phi}{\partial z} + \tilde \lambda (N-1)|\Phi|^2\Phi=\tilde\mu\Phi,
+\label{eq:GPE_resc}
+\end{equation}
+where $\tilde\mu=\frac{2 \kappa \mu}{\hbar^2}$, $\tilde \lambda =\frac{2 \kappa \lambda}{\hbar^2}$, and 
+$v= \frac{2 \kappa P}{M \hbar}$ with $P={\cal P}-\hbar A(N-1)$. $P$ defines the momentum of the impurity in the thermodynamic limit;
+note that $A$ is determined by $P$, and there is a unique value of ${\cal P}$ for a given $P$.
+The boundary conditions for Eq.~(\ref{eq:GPE_resc}) read
+\begin{equation}
+\Phi(z=0)=\Phi(z=L); \qquad \frac{\partial \Phi}{\partial z}\bigg|^{z=0^+}_{z=L^-}= \tilde g \Phi(0),
+\end{equation}
+where $\tilde g= \frac{2\kappa g}{\hbar^2}$. The non-linear equation~(\ref{eq:GPE_resc}) 
+has an analytic steady solution~\cite{hakim1997}, which determines the properties 
+of the dressed impurity in our problem. Let us first consider the non-interacting impurity $g=0$. 
+In this case the solution for $v>0$ is~\cite{tsuzuki1971, ishikawa1980}
+\begin{equation}
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z+z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\label{eq:Phi_c0}
+\end{equation}
+\begin{equation}
+\phi(z)=-\pi\theta(z+z_d)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z+z_0)\right]-2\beta+1}\right),
+\label{eq:phi_c0}
+\end{equation}
+where  $\beta=1- v^2/(2\tilde \mu)$, $z_0$ is some parameter that determines the origin and $z_d$ is the point where $\mathrm{arctan}$ reaches $\pi/2$.
+ It is worthwhile noting that the solution for $v<0$ is $\Phi^*$. 
+The solution from Eqs.~(\ref{eq:Phi_c0}) and~(\ref{eq:phi_c0}) is plotted in Fig.~\ref{fig:Fig1}; 
+for simplicity it is plotted in the interval $-L/2<z<L/2$, the region $0<z<L$ easily follows.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+ \begin{figure}
+ \centerline{\includegraphics[scale=0.45]{figure1appendix_new.pdf}}
+\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) 
+($a>0$, the exact value of $a$ is not important for our discussion). 
+ Note that the minimum of the density is at $-a$. 
+The shaded area is a combination of the two solutions with the singularity at $z=0$. 
+Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
+ \label{fig:Fig1}
+ \end{figure}
+ %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+To describe an interacting impurity, we combine two moving solitons with $\pm z_0$, which creates a singularity at $z=0$~\cite{hakim1997,kamenev2016}.
+Therefore, a dressed impurity in our model is a topological defect with a dissipationless propagation. 
+We write the corresponding `wave function' as
+\begin{equation}
+\Phi=\sqrt{\frac{\tilde \mu}{\tilde \lambda (N-1)}}\left(1-\beta \mathrm{sech}^2\left[\sqrt{\frac{\tilde\mu\beta}{2}}(z\pm z_0)\right]\right)^{\frac{1}{2}}e^{i\phi(z)},
+\end{equation}
+with 
+\begin{equation}
+\phi(z)=\delta \phi \theta(-z)+\mathrm{arctan}\left(\frac{\sqrt{\frac{2 v^2}{\tilde \mu}\beta}}{\mathrm{exp}\left[\sqrt{2\tilde \mu\beta}(z\pm z_0)\right]-2\beta+1}\right),
+\label{eq:phase_soliton}
+\end{equation}
+where $z_0>0$ is discussed below, the parameter $\delta \phi$ is not important for the further derivations, it reassures that the phase is a continuous function;
+the plus sign in $\pm$ corresponds to $z>0$ and the minus sign to $z<0$. This function is illustrated in Fig.~\ref{fig:Fig1}. 
+The density has a non-analytic derivative at $z=0$. The phase is a continuous function at $z=0$ (its derivative is also continuous).
+Note that the wave function is not periodic (see Eq.~(\ref{eq:phase_soliton})). This non-periodicity is not important 
+for our discussion, because we are interested in the behavior of the bosons close to the impurity. It suggests that a grey soliton
+must be formed upon a change of interaction parameters to take care of the phase slip.
+
+The parameter $\tilde \mu$ is found from the normalization condition $\int \Phi^2=1$. For $N\to\infty$, we obtain
+\begin{equation}
+\tilde \mu=\gamma \rho^2 \frac{N-1}{N}\left(1-2\sqrt{2\beta_0} \frac{ (\mathrm{tanh}(d)-1)}{\sqrt{\gamma}N}\right),
+\end{equation}
+where $\gamma=\tilde \lambda /\rho$, $\rho=N/L$, $\beta_0=1-v^2/(2\gamma \rho^2)$, and $d=\sqrt{\frac{\gamma \beta_0}{2}}\rho z_0$.
+The equation to determine $z_0$ is found by using the boundary conditions at $z=\{0,L\}$
+\begin{equation}
+\frac{\tilde g}{\rho \sqrt{2\gamma}}=\frac{\beta_0^{\frac{3}{2}}\tanh(d)}{-\beta_0+\cosh^2(d)}.
+\label{eq:c_v}
+\end{equation}
+This equation is cubic (in $\tanh(d)$), hence, the solutions can be found in a closed form.
+There are three solutions. However, only two will lead to the acceptable values of $z_0$. 
+We will refer to these steady solutions as the `polaron' and the `polaron-soliton' pair, because in the limit $g\to 0$ the former 
+corresponds to the ground state, and the latter to a gray soliton. 
+The `polaron-soliton' pair is expected to be unstable (small perturbations lead to 
+a decay of this steady solution~\cite{hakim1997}),
+therefore, we do not consider it. The solutions merge for $z_m$ 
+\begin{equation}
+\tanh^2\left(\sqrt{\frac{\gamma \beta_0}{2}}\rho z_m\right)=\frac{\sqrt{1+\frac{4v^2}{\gamma \rho^2}}-(1+\frac{v^2}{\gamma \rho^2})}{2\beta_0},
+\label{eq:z_m}
+\end{equation}
+which is derived by taking a derivative of Eq.~(\ref{eq:c_v}) with respect to $z_0$ and equating the resulting expression to zero -- this determines 
+the maximum value of $g$ for which (for a fixed $\beta_0$) there is a steady solution.
+Equations~(\ref{eq:c_v}) and (\ref{eq:z_m}) give the equation for the critical value of $v_c$:
+\begin{equation}
+\frac{\tilde g}{\rho\sqrt{\gamma}}=\frac{3-\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}{-1+\sqrt{1+\frac{4v_c^2}{\gamma \rho^2}}}\sqrt{\sqrt{1+\frac{4v_c^2}{\gamma \rho}}-1-\frac{v_c^2}{\gamma\rho^2}}.
+\end{equation}
+For $v>v_c$ (see Fig. 4 of the main text) there is no steady solutions.
+
+Now we can calculate the energy of the dressed impurity in the thermodynamic limit
+\begin{equation}
+{\cal E}\equiv \lim_{N\to\infty, \frac{N}{L}\to \rho}\left[E(c,P)-E(c=0,P=0)\right],
+\end{equation}
+where
+\begin{equation}
+E(c,P) = \frac{{\mathcal P}^2}{2M} + \mu N-\frac{\hbar^2 A^2 N(N-1)}{2M}-\lambda N(N-1)\int_{0}^{L/2}|\Phi|^4\mathrm{d}z.
+\end{equation}
+Using these expressions we derive 
+\begin{equation}
+{\cal E}=\frac{P^2}{2M}+\frac{\hbar^2\rho^2}{2\kappa}\frac{\sqrt{2  \gamma \beta}}{3}\left[4 b + (-4b+\beta\mathrm{sech}^2(d))\tanh(d)\right]+\frac{\hbar P}{M}\lim_{N\to\infty} A N,
+\end{equation}
+where $b=1+\frac{v^2}{4\tilde \lambda \rho}=1+\frac{\kappa P^2}{2M^2 \lambda \rho}$. This energy for $v\to 0$ can be written as 
+\begin{equation}
+{\cal E}\simeq \epsilon+ \frac{P^2}{2m_{\mathrm{\mathrm{eff}}}},
+\label{eq:18}
+\end{equation}
+where $\epsilon$ is the effective energy of the dressed impurity, and $m_{\mathrm{eff}}$ is the effective mass.
+
+The parameters $m_{\mathrm{eff}}$ and $\epsilon$ calculated using Eq.~(\ref{eq:18})  
+agree well with the results in the literature~\cite{mistakidis2018}, supporting 
+the use of the non-linear Schr{\"o}dinger equation for solving the problem. 
+However, further work is required to understand other properties of a dressed impurity in this formalism.
+First of all, it will be interesting to investigate the critical momentum,
+which is supersonic in the employed model for $g\to 0$ and for not heavy impurities.
+Indeed, the model we solve is equivalent to a heavy impurity moving in a gas of bosons with mass $\kappa$,  
+which has a different speed of sound. 
+Note that Fig.~4 of the main text reports on a heavy impurity ($M/m\gg 1$) for which this problem does not occur.
+It will be also interesting to investigate the residue -- the overlap between the wave function that describes 
+a state with $g=0$ and the wave function that decribes an interacting state. In the present model, the impurity changes the order parameter
+only locally, which means a non-zero residue (see~\cite{volosniev2017} for $P=0$), contradicting other 
+studies on the topic~\cite{pastukhov2017,grusdt2017}. To understand this disagreement, one could calculate the overlap using an exactly solvable model, e.g., 
+a heavy impenetrable impurity in a Bose gas (solvable by Bethe ansatz).
+
 \end{document}

### 2019-07-11 Paper/pra_resub/paper.tex
added in artems change to new intro paragraph

@@
 
-Other studies related to the engineering of atomic beams have focused on the  outcoupling of atoms in an atomic wave guide to a Bose-Einstein condensate using rf fields \cite{PhysRevLett.97.200402, PhysRevA.80.041605, buning2010slow} or on controlling the transmission of atoms with careful manipulation of an optical lattice \cite{PhysRevLett.84.399, PhysRevLett.107.230401, PhysRevA.92.033614}.
+Other studies related to the engineering of atomic beams have focused on  the  outcoupling  of  atoms  from a Bose-Einstein condensate \cite{PhysRevLett.97.200402, PhysRevA.80.041605, buning2010slow} or on controlling the transmission of atoms with careful manipulation of an optical lattice \cite{PhysRevLett.84.399, PhysRevLett.107.230401, PhysRevA.92.033614}.
 In contrast, the current article proposes a method for engineering atomic beams by coupling a trapped gas of atoms to a combination of individually tuned lasers.

### 2019-07-23 Paper/pra_resub/paper.tex
figure 5 revision

@@
  \begin{figure}
- \centerline{\includegraphics[scale=0.45]{figure1appendix_new.pdf}}
-\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas for $z_0=a$ (red curve), $z_0=-a$ (blue curve) 
+ \centerline{\includegraphics[scale=0.45]{figure5_corrected.pdf}}
+\caption{Panel {\bf a)}: The density, $|\Phi|^2 N$, of the Bose gas  
+for $z_0=a$ (solid red curve), $z_0=-a$ (dot-dashed blue curve)
 ($a>0$, the exact value of $a$ is not important for our discussion).
   Note that the minimum of the density is at $-a$.
-The shaded area is a combination of the two solutions with the singularity at $z=0$. 
-Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities from {\bf a)}.}
+The shaded area is a combination of the two solutions with the  
+singularity at $z=0$.
+Panel {\bf b)}: The phase, $\phi$, of the Bose gas for the densities  
+from {\bf a)}.}
  \label{fig:Fig1}
